### 2014-03-28 R/Neutral_Model_BCI.Rmd
1st srsdq.md copied from naturalCommunities

# Multifractal patterns for spatial neutral simulacions based on BCI

I add the BCI 1995 Coccoli & Sherman plot data. One option is to standarize the abundaces using total no. of individuals, but I finally used the raw data added as metacommunity.

I also fit a logseries and compare different metacomunities generated with different parameters.

"Because common local species are likely to be
widespread metacommunity species, a better estimate can
often be obtained from fitting only the common species in
the local community." Hubell pag 300

```{r addCoccoliShermanBCI}
# BCI folder data
#
BCIwd <- "~/Dropbox/BCI"

getwd(oldcd)
# "~/Dropbox/Multifractals/NaturalCommunities"

setwd(BCIwd)
source('Fun_logseries.r')
library(vegan)

load('bci.full4.rdata')

bci4 <- get.AbundVec_BCI(bci.full4)
N <- sum(bci4$Freq)

rm(bci.full4)

load('cocoli.full1.rdata')
tcoc <- get.AbundVec_BCI(cocoli.full1)

rm(cocoli.full1)
tot <- rbind(tcoc,bci4[,1:3])

load('sherman.full1.rdata')
tshe <- get.AbundVec_BCI(sherman.full1)
tot <- rbind(tot,tshe)
rm(sherman.full1)
rm(tcoc,tshe)

require(plyr)

tot1 <-ddply(tot,.(sp),summarise,FreqT=sum(Freq))
tot <- tot[order(tot$sp),]
tot1$prob <- tot1$FreqT/sum(tot1$FreqT)
tot1 <- tot1[rev(order(tot1$prob)),]
#plot(log(tot1$prob))

setwd(oldcd)

N <- sum(tot1$FreqT)
lsf <- fit.logser(tot1$FreqT)
a <-  data.frame(t(unlist(lsf$summary)))$alfa
require(vegan)
require(untb)
fisherfit(tot1$FreqT)
# el alpha obtenido por fisherfit es diferente
tot1$Type <-"BCI"
tot1$Ord <- 1:nrow(tot1)

rm(lsf)

# generate some communities using untb to graph comparisons
#
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Neutral")
tot1 <-rbind(tot1,ff)
S=nrow(tot1[tot1$Type=="BCI",])

ff<-fisher.ecosystem(N=N,S=S,alpha=a,nmax=N)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff),Type="Fisher fit 1")
tot1 <-rbind(tot1[tot1$Type!="Fisher",],ff)

ff <-fisherfit(tot1[tot1$Type=="BCI",]$Freq)
ff$estimate
ff<-fisher.ecosystem(N=N,S=S,alpha=ff$estimate,nmax=N)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff),Type="Fisher fit 2")
tot1 <-rbind(tot1,ff)

# Parametro theta de Etienne 2007 
N=500*500
a=260
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
tot1 <-rbind(tot1,ff)

require(ggplot2)
g <- ggplot(data=tot1,aes(x=Ord,y=log(FreqT),col=Type)) + geom_line()

g
#lsf <- function(x) log(rad.logserf(tot1[tot1$Type=="BCI",]$Freq,a)(x))
#g + stat_function(fun=lsf)
#g

# Select only the raw data
#
tot1 <-tot1[tot1$Type=="BCI",]

rm(lsf,ff,tot)
```

Now generate parameter files to simulate neutral models.

```{r genParms, echo=F}
# Parameters from Etienne 2007
eti <- read.table("Etienne2007_I.dat", header=T)
# calculate m (migration from metacommunity) with the number of individuals for the simulation
N=500*500
mean(eti$I)/(mean(eti$I)+N-1)
# m =  0.0001596079
max(eti$I)/(max(eti$I)+N-1)
# m = 0.0001769294
min(eti$I)/(min(eti$I)+N-1)
# m = 0.0001452595

ana <- read.table("Anand2010_DD.dat", header=T)
m_DD <-mean(ana$DD)
mean_power <-function(alfa,x=1) abs(((alfa-1)/(alfa-2)*x)-m_DD)
mean_exp <- function(beta) abs(1/beta -m_DD)

optimize(mean_power,c(2,4))
# alfa=2.038974
mean_power(2.038974)+m_DD

# Range for exponential kernel 
optimize(mean_exp,c(0,1))
# beta=0.037495
mean_exp(0.037495)+m_DD

m_DD <- 34.89 # 3rd quartil
optimize(mean_exp,c(0,1))
# beta=0.02868046
mean_exp(0.02868046)+m_DD

optimize(mean_power,c(2,4),tol=0.00001)
mean_power(2.029508)+m_DD
# alfa=2.029508

m_DD <- 12.33 # 1st quartil
optimize(mean_exp,c(0,1))
# beta=0.08111446
mean_exp(0.08111446)+m_DD

# Generate parameters file for simulation with metacommunity using
# the frequencies of the summed BCI+Cocoli+Sherman plots

parm <- data.frame( n=c(rep(0,3),1:nrow(tot1)) ,prob=c(rep(0,3),prob=tot1$prob))
parm$text <- "" 
parm$z <- 0
parm$text[1] <- paste(500,500,sep="\t")
parm$text[2] <- nrow(tot1)
parm$text[3] <- paste(0,1,0.2,0.037495,0.0017,sep="\t")
parm$text[4:455] <-   with(parm[4:455,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
write.table(parm$text,"bci452.inp",sep="\t",row.names=F,col.names=F,quote=F)

# Generate parameter's file with metacommunity from a logseries fitted with 
# BCI+Cocoli+Sherman

ff <-fisherfit(tot1[tot1$Type=="BCI",]$Freq)
ff$estimate
ff<-fisher.ecosystem(N=N,S=S,alpha=ff$estimate,nmax=N)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
ff$prob <- ff$FreqT/sum(ff$FreqT)

parm <- data.frame( n=c(rep(0,3),1:nrow(ff)) ,prob=c(rep(0,3),prob=ff$prob))
parm$text <- "" 
parm$z <- 0
parm$text[1] <- paste(500,500,sep="\t")
parm$text[2] <- nrow(ff)
parm$text[3] <- paste(0,1,0.2,0.037495,0.003,sep="\t")
nff <- nrow(ff)+3
parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
write.table(parm$text,"bci445.inp",sep="\t",row.names=F,col.names=F,quote=F)

# Generar archivo de parametros con metacomunidad a partir de
# con theta a partir de Etienne 2007 de BCI+Cocoli+Sherman

N=500*500
a=260
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
ff$prob <- ff$FreqT/sum(ff$FreqT)

parm <- data.frame( n=c(rep(0,3),1:nrow(ff)) ,prob=c(rep(0,3),prob=ff$prob))
parm$text <- "" 
parm$z <- 0
parm$text[1] <- paste(500,500,sep="\t")
parm$text[2] <- nrow(ff)
parm$text[3] <- paste(0,1,0.2,0.037495,0.003,sep="\t")
nff <- nrow(ff)+3
parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
write.table(parm$text,"bci1826.inp",sep="\t",row.names=F,col.names=F,quote=F)

rm(ff,parm,nff,eti,ana)
rm(tot1)

```

First I do some exploratory simulations to adjust the parameters the key file for multiple simulations is pomac.lin there each line is a different run that I can set with different parameters

    BirthRate=1
    MortalityRate=0.2 0.3
    DispersalDistance=0.0375 0.0287 0.0811 
    ColonizationRate=0.001 0.003 0.005

I run the simulations for each parameter combination
I copy pomacExplo.lin to pomac.lin and change the "basename" 
parameter in bci452.par

```{r explo_simul}

source('Fun_Multi_patt.r')

setwd("Simul")
# copy the simulation file parameter file
system("cp pomacExp_Explo.lin pomac.lin")

# change the output file
system("sed -i 's/bciExpEtienne/bciExpZ/g' bci452Z.par")

# Perform the simulations
system("./ipsNeutralExp bci452Z.par bci452.inp")

setwd("..")

# reads the output of multifractal spectra of neutral model
md1 <- readNeutral_calcDq("Simul/bciExpZmfOrd.txt")
md0 <-with(md1, md1[q==1,])

with(md0, md0[Dq>= 1.83 & Dq<=1.85,])
with(md0, md0[Dq>= 1.83 & Dq<=1.85 & Time>50,])
# En ningun caso da la misma dimension fractal
# Esto puede ser porque no tiene la misma resolucion o cobertura habria que 
# ver que densidad de puntos tienen las estimaciones de BCI = 0.36

# Tambien probe con las metacomunidades bci445 y bci1826 pero dan riquezas menores
# y fuera del intervalo

md0 <- read.table("Simul/bciExpZDensity.txt",header=T)
md0 <- md0[order(-md0$Richness),]
with(md0, md0[Richness>= 299 & Richness<=306 & Time>10, ])
# 0.2  0.0375  0.005
# 0.2  0.0287  0.005 da menor H

with(md0, md0[H>=3.91 & H<=4 & Time>50, ])
# 0.2  0.0375  0.001 da mayor S

# I Use parameters that result in approximately the same richness than BCI
names(md0)[2:4]<-c("MortalityRate","DispersalDistance","ColonizationRate")
md0  <- with(md0, md0[Time %in% c(1,5,10,15,seq(20,100,by=10)),])
md0  <- with(md0, md0[MortalityRate==0.2 & DispersalDistance==0.0287 & ColonizationRate==0.005,])
md0 <- md0[,c(6,7,9,10)]
require(pander)
options(scipen=3,digits=5)
panderOptions('table.style','grid')
pander(md0)

compMdl <- with(md1, md1[MortalityRate==0.2 & DispersalDistance==0.0287 & ColonizationRate==0.005,])

compMdl <- with(compMdl, compMdl[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])

rm(md1,md0)

require(lattice)
require(Hmisc)

qci<- with(compMdl, sapply(SD.Dq,calcCI,7,0.05))
compMdl$LowCI <- compMdl$Dq-qci
compMdl$HighCI <- compMdl$Dq+qci

md1 <- with(compMdl, compMdl[Time>=5 &Time<11,])

png("Fig9_DqComp_Neut452_5.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
    	     panel.xYplot(...)},
  		     ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

md1 <- with(compMdl, compMdl[Time>=30 &Time<60,])
png("Fig9_DqComp_Neut452_30.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
  		     ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

md0 <- compMdl[compMdl$q!=0,]
range(md0$R.Dq)
# 0.947 0.999
png("FigS5_RDq_Neut452.png", width=6,height=6,units="in",res=600)
histogram(~R.Dq,data=md0,xlab=expression(italic(R^2)))
dev.off()

# Leo archivo con las simulaciones de ese set de parametros para ver si hay o no hay 
# diferencias en los intervalos de confianza.

# Dejo solo dos tiempos para comparar los SD

compMdl <- with(compMdl, compMdl[Time %in% c(5,60),])
compMdl$Type <- "regr" 
compMdl <-  compMdl[,c(4:7,9:11)]

```

Ten repeated simulations with chosen parameters

    BirthRate=1
    MortalityRate=0.2 
    DispersalDistance=0.0287 
    ColonizationRate=0.005

```{r simul10}

source('Fun_Multi_patt.r')

setwd("Simul")
# copy the simulation file parameter file
system("cp pomacExp_10.lin pomac.lin")

# change the output file
system("sed -i 's/bciExpZ/bciExpZ005/g' bci452Z.par")

# Perform the simulations
system("./ipsNeutralExp bci452Z.par bci452.inp")

setwd("..")

# Read the simulations with same parameters
#
md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")

md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])
md0 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
md0 <-ldply(md0)
names(md0)[1] <- "Time"

md0$Time <- as.numeric(md0$Time)
md0$Dq <- as.numeric(md0$Dq)
md0$LowCI <- as.numeric(md0$LowCI)
md0$HighCI <- as.numeric(md0$HighCI)

md1 <- with(md0, md0[Time>=5 &Time<11,])
png("Fig9_DqComp_Neut452_B5.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
    	     ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

md1 <- with(md0, md0[Time>=30 &Time<60,])
png("Fig9_DqComp_Neut452_B30.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
           ylab=expression(italic(D[q])),
  		     xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()

# Los SD son menores que las estimadas por mfSBA
md1 <- with(md0, md0[Time==5 | Time==60,])

common_cols <- intersect(colnames(compMdl), colnames(md1))
compMdl <- rbind(  md1[common_cols], compMdl[common_cols])

#Calculate D1 and DeltaDq(-5,5)
require(plyr)

d1_delta <- ddply(compMdl, .(Time,Type),summarize, 
                  DeltaDq = Dq[q==-5]-Dq[q==5], 
                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
                  D1=Dq[q==1],
                  SD.D1=SD.Dq[q==1]   )

# A pandoc table could be generated with pander

require(pander)
options(scipen=3,digits=5)
panderOptions('table.style','grid')
pander(d1_delta)

# Table S2

# Plot with SRS at 5 and 30 years

# the neutral model has to be run again changing the .par file
# to save the image files and the output name to not overrite the previous 
# simulations 
#
# sa N
# baseName bciExpZa
# 
# Then the program multiSpeciesSBA do the SRS ordering 
# I run cpp/SpatialAnalysis/mfsba/multiSpeciesSBA to show the SRS 
#

require(RColorBrewer)
col.l = c("white",brewer.pal(8,"Dark2"))

png("Fig9_Neut452_5.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciExpZa-5Reord.sed","5 Years",1:500,col.l)
#plot_image("Simul/bciExpZa-5.sed","5 Years")
dev.off()

#plot_image("Simul/bciExpZa-30.sed","30 Years")
png("Fig9_Neut452_30.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciExpZa-30Reord.sed", "30 Years",1:500,col.l)
dev.off()

rm(common_cols)
rm(md0,md1,bci4,rq1,qci)

```

Compare Dq from different times using ten simulations

```{r compareDq}

require(statmod)
require(reshape2)
md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")

md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])
md1 <- with(md1, md1[q!=0,])
md1$rep <- rep( 1:10,each=480)

compMd1 <- melt(md1, id.vars=c("Time","rep","q"),measure.var="Dq")
names(compMd1)

c1 <-dcast(compMd1, Time+rep ~ q)
names(c1[,13:22])
c1 <- with(c1, c1[Time<11,])

# Positive q
compareGrowthCurves(c1$Time,c1[,13:22],nsim=1000)

# Negative q 
names(c1[,3:12])
compareGrowthCurves(c1$Time,c1[,3:12],nsim=1000)
# the output is table S3

c1 <-dcast(compMd1, Time+rep ~ q)
c1 <- with(c1, c1[Time>=30 & Time<60,])

# Positive q
compareGrowthCurves(c1$Time,c1[,13:22],nsim=1000)

# Negative q 
compareGrowthCurves(c1$Time,c1[,3:12],nsim=1000)
# The output is in TABLE S4

rm(md1,compMd1,c1)
```

Perform simulations using power law kernel

```{r simulPower}
setwd("Simul")
# copy the simulation file parameter file
system("cp pomacPow_10.lin pomac.lin")

# change the output file
system("sed -i 's/bciExpZ005/bciPowZ005/g' bci452Z.par")

# Perform the simulations
system("./ipsNeutralExp bci452Z.par bci452.inp")

setwd("..")

```

Dq Comparison between exponential and power dispersal

```{r compareExpPow}

require(statmod)
require(reshape2)

md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")

#md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=20)),])
md0 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
md0 <-ldply(md0)
names(md0)[1] <- "Time"

md0$Time <- as.numeric(md0$Time)
md0$Dq <- as.numeric(md0$Dq)
md0$LowCI <- as.numeric(md0$LowCI)
md0$HighCI <- as.numeric(md0$HighCI)
md0$Type <- "Exp"

md1 <- readNeutral_calcDq("Simul/bciPowZ005mfOrd.txt")
#md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=20)),])
md00 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
md00 <-ldply(md00)
names(md00)[1] <- "Time"

md00$Time <- as.numeric(md00$Time)
md00$Dq <- as.numeric(md00$Dq)
md00$LowCI <- as.numeric(md00$LowCI)
md00$HighCI <- as.numeric(md00$HighCI)
md00$Type <- "Pow"

compMdlExpPow <- rbind(md0,md00)
md1 <- with(compMdlExpPow, compMdlExpPow[Time %in% c(5,6,7,8,9,10,15,20,25,seq(30,100,by=20)),])
require(Hmisc)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q|Type, data=md1, nx=FALSE, groups=Time, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
           ylab=expression(italic(D[q])),
           xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Dispersal",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )

# Compare different dispersals and BCI
#
md1 <- with(compMdlExpPow, compMdlExpPow[Time == 90,])

require(plyr)

md2 <- ddply(compBCI, .(q), summarize, 
                  SD.Dq=sd(Dq),
                  Dq=mean(Dq))

qci<- with(md2, sapply(SD.Dq,calcCI,7,0.05))
md2$LowCI <- md2$Dq - qci
md2$HighCI <- md2$Dq + qci
md2$Type <- "BCI"

names(md1)
names(md2)
names(md1[,c(2:5,7:8)])

md1 <- rbind(md2,md1[,c(2:5,7:8)])

png("Fig10_DqComp_NeutExpPow.png", width=6,height=6,units="in",res=600)
with(md1,
    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Type, type="l",
           scales=list(tck=-1),
           cap=.01,
           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
           panel=function(...){
           panel.abline(h=2, col="grey", lty=2)
           panel.xYplot(...)},
           ylab=expression(italic(D[q])),
           xlab=expression(italic(q)),
           label.curves=F,
           auto.key=list(x=.65,y=.9,title="Dispersal",cex.title=.9, lines=T,points=F,cex=.7),
           )
       )
dev.off()
rm(md1,md2)

# Compare the different dispersals

require(statmod)
require(reshape2)
md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")
md1 <- with(md1, md1[Time == 90 & q!=0,])
md1$rep <- rep( 1:10,each=nrow(md1)/10)
md1$Type <- "Exp"

md2 <- readNeutral_calcDq("Simul/bciPowZ005mfOrd.txt")
md2 <- with(md2, md2[Time == 90 & q!=0,])
md2$rep <- rep( 1:10,each=nrow(md2)/10)
md2$Type <- "Pow"

# Get BCI Dq

md3 <- with(compBCI, compBCI[q!=0,])
md3$Type <- "BCI"
names(md3)[5]="rep"
md3$rep <- rep( 1:7,each=20)
names(md3[,c(1:5,8)])
names(md2[,c(5:10)])
md1 <- rbind(md1[,c(5:10)],md2[,c(5:10)])

compMd1 <- melt(rbind(md1,md3[,c(1:5,8)]), id.vars=c("Type","rep","q"),measure.var="Dq")
names(compMd1)

c1 <-dcast(compMd1, Type+rep ~ q)
# Positive q
names(c1[,13:22])
compareGrowthCurves(c1$Type,c1[,13:22],nsim=1000)

#   Group1 Group2      Stat P.Value adj.P.Value
#1    BCI    Exp -49.19708       0           0
#2    BCI    Pow -12.16894       0           0
#3    Exp    Pow  81.79017       0           0

# Negative q 
names(c1[,3:12])
compareGrowthCurves(c1$Type,c1[,3:12],nsim=1000)

#  Group1 Group2      Stat P.Value adj.P.Value
#1    BCI    Exp 110.70741       0           0
#2    BCI    Pow  16.72702       0           0
#3    Exp    Pow -90.12642       0           0

rm(c1,md1,md2,md3,md00)

# Plot spatial distribution of the models

require(RColorBrewer)
col.l = c("white",brewer.pal(8,"Dark2"))
#col.l = colorRampPalette(c(brewer.pal(8,"Paired")))(64)

png("Fig10_Neut452_Exp90.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciExpZa-90Reord.sed","",1:500,col.l,5)
dev.off()

png("Fig10_Neut452_Pow90.png", width=6,height=6,units="in",res=600)
plot_image("Simul/bciPowZa-90Reord.sed","",1:500,col.l,5)
dev.off()
```

DeltaDq Comparison between BCI, exponential and power dispersal

```{r DeltaD5_BCI_vs_mdl, echo=FALSE}

require(plyr)

# Calculate DeltaD5 for BCI, compBCI was previously saved.

d1_delta <- ddply(compBCI, .(Year),summarize, 
                  DeltaDq = Dq[q==-5]-Dq[q==5], 
                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
                  D1=Dq[q==1],
                  SD.D1=SD.Dq[q==1]   )

# Calculate SD of DeltaDq using all years of BCI
#sd_DeltaD5 <- sd(d1_delta$DeltaDq)
#calcCI(sd_DeltaD5,7,0.05)
#mean(d1_delta$DeltaDq)  
# CI 0.01475477
# Mean 1.101303

md1 <- with(compMdlExpPow, compMdlExpPow[Time %in% seq(30,60,by=5),])

d2_delta <- ddply(md1, .(Time,Type),summarize, 
                  DeltaDq = Dq[q==-5]-Dq[q==5], 
                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
                  D1=Dq[q==1],
                  SD.D1=SD.Dq[q==1]   )
names(d1_delta)[1]="Time"
d1_delta$Type = "BCI"
names(d2_delta)
names(d1_delta)
d2_delta <- rbind(d2_delta,d1_delta)
d1_delta <- ddply(d2_delta, .(Type), summarize, 
                  SD.DeltaDq=sd(DeltaDq),
                  SD.D1=sd(D1),
                  D1=mean(D1),
                  DeltaDq=mean(DeltaDq))

# A pandoc table could be generated with pander
require(lattice)
#bwplot(Type ~ DeltaDq,data=d2_delta)
#bwplot(Type ~ D1,data=d2_delta)

#require(pander)
#options(scipen=3,digits=5)
#panderOptions('table.style','grid')
#pander(d1_delta)

qci<- with(d1_delta, sapply(SD.DeltaDq,calcCI,7,0.05))
d1_delta$CI.DeltaDq <- qci
require(ggplot2)
ggplot(d1_delta, aes(x=Type, y=DeltaDq)) +
geom_errorbar(aes(ymin=DeltaDq-CI.DeltaDq, ymax=DeltaDq+CI.DeltaDq), width=.1) +
geom_point(fill="white",shape=21)

rm(d1_delta,d2_delta,qci,md1)
```

### 2014-04-05 R/Neutral_simul.Rmd
Clean source add fragments

--- 2014-03-28 R/Neutral_Model_BCI.Rmd
@@
-# Multifractal patterns for spatial neutral simulacions based on BCI
+# Multifractal analysis of multispecies spatial distributions - Model simulations
+
+I generate parameter files for the simulation of neutral/hierarchical model using logseries as the metacommunity distribution
+
+```{r generateLogSerParms}
+
+oldcd <-getwd()
+source("R/Neutral_fun.r")
+
+# Generate a SAD for metacommunity using a logseries 
+#
+# side is the side of the simulation lattice
+#
+# N is the total number of individuals 
+#
+# S is the species richness 
+#
+
+require(untb)
+side <- 500
+N <- side*side
+S <- 450 
+ff<-fisher.ecosystem(N=N,S=S,nmax=N)
+plot(ff)
+nrow(ff)
+ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
+ff$prob <- ff$FreqT/sum(ff$FreqT)
+
+# Parameters
+#
+# Mortality = 0.2 - 0.4
+# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
+#                         2.5 -> 0.4
+# Colonization = 0.001 -0.0001
+# Replacement  = 0 - 1
+
+setwd("Simul")
+#undebug(genNeutralParms)
+# First generate de inp file with species and metacommunity parameters 
+genNeutralParms("fishE",500,ff$prob,1,0.2,0.04,0.001)
+
+# Then pomac.lin to simulate a range of parmeters and repetitions.
+#
+# Generates pomac.lin for exponential dispersal to compare hierarchical and neutral communities 
+# and see when they have similar H and compare if they have similar SAD
+
+genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,1))
+
+# we need the par file with the simulations parameters
+
+par <- read.table("sim.par",quote="",stringsAsFactors=F)
+# Change base name
+par[par$V1=="baseName",]$V2 <- "Exp452"
+# Change model type
+par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
+
+# I have to run the model with the parameter ReplacementRate turned on!! take care
+
+```
 
@@
 
-"Because common local species are likely to be
-widespread metacommunity species, a better estimate can
-often be obtained from fitting only the common species in
-the local community." Hubell pag 300
+```{r addCoccoliShermanBCI}
 
-```{r addCoccoliShermanBCI}
+rm(list = ls())
+
 # BCI folder data
 #
-BCIwd <- "~/Dropbox/BCI"
+BCIwd <- "~/Dropbox/Projects/BCI"
 
-getwd(oldcd)
+oldcd <-getwd()
 # "~/Dropbox/Multifractals/NaturalCommunities"
@@
 # Parametro theta de Etienne 2007 
-N=500*500
+N=500*500*4 # assume a metacommunity with 1.000.000
 a=260
@@
 ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
+tot1 <- tot1[tot1$Type!="Etienne",]
 tot1 <-rbind(tot1,ff)
@@
 require(ggplot2)
-g <- ggplot(data=tot1,aes(x=Ord,y=log(FreqT),col=Type)) + geom_line()
+ggplot(data=tot1,aes(x=Ord,y=log(FreqT),col=Type)) + geom_line()
 
-g
 #lsf <- function(x) log(rad.logserf(tot1[tot1$Type=="BCI",]$Freq,a)(x))
@@
 
-# Select only the raw data
+# Select only the raw data BCI+Cocoli+Sherman
 #
@@
 
-rm(lsf,ff,tot)
+rm(lsf,ff,tot,bci4)
 ```

### 2014-04-05 R/Neutral_fun.r

@@ -1,0 +1,28 @@
+
+# Generate inp parameters file for simulation
+#
+genNeutralParms <- function(fname,side,mprob,birth,mortality,dispersal,colonization){
+  S <- length(mprob)
+  parm <- data.frame( n=c(rep(0,3),1:S) ,prob=c(rep(0,3),prob=mprob))
+  parm$text <- "" 
+  parm$z <- 0
+  parm$text[1] <- paste(side,side,sep="\t")
+  parm$text[2] <- S
+  parm$text[3] <- paste(0,birth,mortality,dispersal,colonization,sep="\t")
+  nff <- S+3
+  parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
+  fname <- paste0(fname,S,".inp")
+  write.table(parm$text,fname,sep="\t",row.names=F,col.names=F,quote=F)
+}
+
+
+# Generates pomac.lin paramenter file for multiple simulations
+#
+genPomacParms <- function(fname,GrowthR,MortR,DispD,ColonR,ReplaceR,numRep=1)
+  {
+  pom <- expand.grid(GrowthRate=GrowthR,MortalityRate=MortR, DispersalDistance=DispD, 
+    ColonizationRate=ColonR,ReplacementRate=ReplaceR)
+  pom <- pom[rep(seq_len(nrow(pom)), numRep), ]
+  if(!grepl("lin",fname)) fname <-paste0(fname,".lin")
+  write.table(pom,fname,sep="\t",row.names=F,col.names=T,quote=F)
+}

### 2014-04-30 R/Neutral_simul.Rmd
add ks test neutral vs non-neutral

@@
 #
-# Generates pomac.lin for exponential dispersal to compare hierarchical and neutral communities 
+# Generates pomac.lin for multiple simulations exponential dispersal to compare hierarchical and neutral communities  
 # and see when they have similar H and compare if they have similar SAD
@@
 # Change base name
-par[par$V1=="baseName",]$V2 <- "Exp452"
-# Change model type
+
+# Number of time steps 
+par[par$V1=="nEvals",]$V2 <- 100
+# Change interval to measure Density and Diversity
+par[par$V1=="inter",]$V2 <- 10
 par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
+par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
+par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
+par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
+                              # 1:several simulations with pomac.lin parameters
 
-# I have to run the model with the parameter ReplacementRate turned on!! take care
+write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
+
+# Run the model with the parameter ReplacementRate turned on = Hierarchical 
+# and exponential dispersal 
+#
+# Set the location of the binary 
+neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"
+
+# copy pomExp.lin to pomac.lin
+system("cp pomExp.lin pomac.lin")
+
+system(paste(neuBin,"sim.par","fishE.inp"),wait=F)
 
@@
 
-I add the BCI 1995 Coccoli & Sherman plot data. One option is to standarize the abundaces using total no. of individuals, but I finally used the raw data added as metacommunity.
+Now I will read the output generated from simulations (not from pomac) to test if the SAD are equal in time using Kolmogorov Smirnov test.
 
-I also fit a logseries and compare different metacomunities generated with different parameters.
+```{r testRAD_KS}
 
-```{r addCoccoliShermanBCI}
+den <- read.delim("Simul/Exp467Density.txt")
+names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
 
-rm(list = ls())
+# from 7 to 473 there are species densities
 
-# BCI folder data
-#
-BCIwd <- "~/Dropbox/Projects/BCI"
+require(reshape2)
 
-oldcd <-getwd()
-# "~/Dropbox/Multifractals/NaturalCommunities"
+# Put simpler names to variables to identify species
+names(den)[7:473]<-as.character(1:467)
 
-setwd(BCIwd)
-source('Fun_logseries.r')
-library(vegan)
+den1 <- melt(den,id.vars=c("Time"),measure.vars=c(7:473),variable.name="Species")
 
-load('bci.full4.rdata')
+# Kolmogorov-smirnov test for two distributions
 
-bci4 <- get.AbundVec_BCI(bci.full4)
-N <- sum(bci4$Freq)
+with(den1,ks.test(den1[Time==10 & value>0,]$value,den1[Time==100 & value>0,]$value))
 
-rm(bci.full4)
-
-load('cocoli.full1.rdata')
-tcoc <- get.AbundVec_BCI(cocoli.full1)
-
-rm(cocoli.full1)
-tot <- rbind(tcoc,bci4[,1:3])
-
-load('sherman.full1.rdata')
-tshe <- get.AbundVec_BCI(sherman.full1)
-tot <- rbind(tot,tshe)
-rm(sherman.full1)
-rm(tcoc,tshe)
+require(ggplot2)
+#den2<-with(den1,den1[Time==90 & value>0,])
+#den2 <- den2[order(den2$value),]
+#den2$Ord <- nrow(den2):1
 
@@
 
-tot1 <-ddply(tot,.(sp),summarise,FreqT=sum(Freq))
-tot <- tot[order(tot$sp),]
-tot1$prob <- tot1$FreqT/sum(tot1$FreqT)
-tot1 <- tot1[rev(order(tot1$prob)),]
-#plot(log(tot1$prob))
-
-setwd(oldcd)
-
-N <- sum(tot1$FreqT)
-lsf <- fit.logser(tot1$FreqT)
-a <-  data.frame(t(unlist(lsf$summary)))$alfa
-require(vegan)
-require(untb)
-fisherfit(tot1$FreqT)
-# el alpha obtenido por fisherfit es diferente
-tot1$Type <-"BCI"
-tot1$Ord <- 1:nrow(tot1)
-
-rm(lsf)
-
-# generate some communities using untb to graph comparisons
-#
-lsf <- rand.neutral(N,a)
-ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Neutral")
-tot1 <-rbind(tot1,ff)
-S=nrow(tot1[tot1$Type=="BCI",])
-
-ff<-fisher.ecosystem(N=N,S=S,alpha=a,nmax=N)
-ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff),Type="Fisher fit 1")
-tot1 <-rbind(tot1[tot1$Type!="Fisher",],ff)
-
-ff <-fisherfit(tot1[tot1$Type=="BCI",]$Freq)
-ff$estimate
-ff<-fisher.ecosystem(N=N,S=S,alpha=ff$estimate,nmax=N)
-ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff),Type="Fisher fit 2")
-tot1 <-rbind(tot1,ff)
-
-# Parametro theta de Etienne 2007 
-N=500*500*4 # assume a metacommunity with 1.000.000
-a=260
-lsf <- rand.neutral(N,a)
-ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
-tot1 <- tot1[tot1$Type!="Etienne",]
-tot1 <-rbind(tot1,ff)
-
-require(ggplot2)
-ggplot(data=tot1,aes(x=Ord,y=log(FreqT),col=Type)) + geom_line()
-
-#lsf <- function(x) log(rad.logserf(tot1[tot1$Type=="BCI",]$Freq,a)(x))
-#g + stat_function(fun=lsf)
-#g
-
-# Select only the raw data BCI+Cocoli+Sherman
-#
-tot1 <-tot1[tot1$Type=="BCI",]
-
-rm(lsf,ff,tot,bci4)
-```
-
-Now generate parameter files to simulate neutral models.
-
-```{r genParms, echo=F}
-# Parameters from Etienne 2007
-eti <- read.table("Etienne2007_I.dat", header=T)
-# calculate m (migration from metacommunity) with the number of individuals for the simulation
-N=500*500
-mean(eti$I)/(mean(eti$I)+N-1)
-# m =  0.0001596079
-max(eti$I)/(max(eti$I)+N-1)
-# m = 0.0001769294
-min(eti$I)/(min(eti$I)+N-1)
-# m = 0.0001452595
-
-ana <- read.table("Anand2010_DD.dat", header=T)
-m_DD <-mean(ana$DD)
-mean_power <-function(alfa,x=1) abs(((alfa-1)/(alfa-2)*x)-m_DD)
-mean_exp <- function(beta) abs(1/beta -m_DD)
-
-optimize(mean_power,c(2,4))
-# alfa=2.038974
-mean_power(2.038974)+m_DD
-
-# Range for exponential kernel 
-optimize(mean_exp,c(0,1))
-# beta=0.037495
-mean_exp(0.037495)+m_DD
-
-m_DD <- 34.89 # 3rd quartil
-optimize(mean_exp,c(0,1))
-# beta=0.02868046
-mean_exp(0.02868046)+m_DD
-
-optimize(mean_power,c(2,4),tol=0.00001)
-mean_power(2.029508)+m_DD
-# alfa=2.029508
-
-m_DD <- 12.33 # 1st quartil
-optimize(mean_exp,c(0,1))
-# beta=0.08111446
-mean_exp(0.08111446)+m_DD
-
-# Generate parameters file for simulation with metacommunity using
-# the frequencies of the summed BCI+Cocoli+Sherman plots
-
-parm <- data.frame( n=c(rep(0,3),1:nrow(tot1)) ,prob=c(rep(0,3),prob=tot1$prob))
-parm$text <- "" 
-parm$z <- 0
-parm$text[1] <- paste(500,500,sep="\t")
-parm$text[2] <- nrow(tot1)
-parm$text[3] <- paste(0,1,0.2,0.037495,0.0017,sep="\t")
-parm$text[4:455] <-   with(parm[4:455,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
-write.table(parm$text,"bci452.inp",sep="\t",row.names=F,col.names=F,quote=F)
-
-# Generate parameter's file with metacommunity from a logseries fitted with 
-# BCI+Cocoli+Sherman
-
-ff <-fisherfit(tot1[tot1$Type=="BCI",]$Freq)
-ff$estimate
-ff<-fisher.ecosystem(N=N,S=S,alpha=ff$estimate,nmax=N)
-ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
-ff$prob <- ff$FreqT/sum(ff$FreqT)
-
-parm <- data.frame( n=c(rep(0,3),1:nrow(ff)) ,prob=c(rep(0,3),prob=ff$prob))
-parm$text <- "" 
-parm$z <- 0
-parm$text[1] <- paste(500,500,sep="\t")
-parm$text[2] <- nrow(ff)
-parm$text[3] <- paste(0,1,0.2,0.037495,0.003,sep="\t")
-nff <- nrow(ff)+3
-parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
-write.table(parm$text,"bci445.inp",sep="\t",row.names=F,col.names=F,quote=F)
-
-# Generar archivo de parametros con metacomunidad a partir de
-# con theta a partir de Etienne 2007 de BCI+Cocoli+Sherman
-
-N=500*500
-a=260
-lsf <- rand.neutral(N,a)
-ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
-ff$prob <- ff$FreqT/sum(ff$FreqT)
-
-parm <- data.frame( n=c(rep(0,3),1:nrow(ff)) ,prob=c(rep(0,3),prob=ff$prob))
-parm$text <- "" 
-parm$z <- 0
-parm$text[1] <- paste(500,500,sep="\t")
-parm$text[2] <- nrow(ff)
-parm$text[3] <- paste(0,1,0.2,0.037495,0.003,sep="\t")
-nff <- nrow(ff)+3
-parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
-write.table(parm$text,"bci1826.inp",sep="\t",row.names=F,col.names=F,quote=F)
-
-rm(ff,parm,nff,eti,ana)
-rm(tot1)
+den2 <- ddply(den1,.(Time), function(x) { 
+  #tmp <- x[x$value>0,]
+  tmp <- x[order(x$value),]
+  tmp$Ord <- nrow(x):1
+  data.frame(tmp)
+  })
+den2 <- with(den2,den2[value>0 & (Time==10 | Time==100),])
+g <- ggplot(den2,aes(x=Ord,y=log(value),colour=as.character(Time))) + geom_line()
+g
 
@@
 
-First I do some exploratory simulations to adjust the parameters the key file for multiple simulations is pomac.lin there each line is a different run that I can set with different parameters
+Thus the SAD at Time=10 is not different from Time=100
 
-    BirthRate=1
-    MortalityRate=0.2 0.3
-    DispersalDistance=0.0375 0.0287 0.0811 
-    ColonizationRate=0.001 0.003 0.005
+Let's try simulations with different parameters using pomac and at Time=100
 
-I run the simulations for each parameter combination
-I copy pomacExplo.lin to pomac.lin and change the "basename" 
-parameter in bci452.par
-
-```{r explo_simul}
-
-source('Fun_Multi_patt.r')
+```{r simul_pomac467}
 
 setwd("Simul")
-# copy the simulation file parameter file
-system("cp pomacExp_Explo.lin pomac.lin")
 
-# change the output file
-system("sed -i 's/bciExpEtienne/bciExpZ/g' bci452Z.par")
+# we need the par file with the simulations parameters
 
-# Perform the simulations
-system("./ipsNeutralExp bci452Z.par bci452.inp")
+par <- read.table("sim.par",quote="",stringsAsFactors=F)
+# Change base name
 
-setwd("..")
+# Number of time steps 
+par[par$V1=="nEvals",]$V2 <- 100
+# Change interval to measure Density and Diversity
+par[par$V1=="inter",]$V2 <- 100
+par[par$V1=="init",]$V2 <- 100
 
-# reads the output of multifractal spectra of neutral model
-md1 <- readNeutral_calcDq("Simul/bciExpZmfOrd.txt")
-md0 <-with(md1, md1[q==1,])
+par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
+par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
+par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
+par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
+                              # 1:several simulations with pomac.lin parameters
 
-with(md0, md0[Dq>= 1.83 & Dq<=1.85,])
-with(md0, md0[Dq>= 1.83 & Dq<=1.85 & Time>50,])
-# En ningun caso da la misma dimension fractal
-# Esto puede ser porque no tiene la misma resolucion o cobertura habria que 
-# ver que densidad de puntos tienen las estimaciones de BCI = 0.36
+write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
 
-# Tambien probe con las metacomunidades bci445 y bci1826 pero dan riquezas menores
-# y fuera del intervalo
+# delete old simulations
+system("rm Exp467*")
 
-md0 <- read.table("Simul/bciExpZDensity.txt",header=T)
-md0 <- md0[order(-md0$Richness),]
-with(md0, md0[Richness>= 299 & Richness<=306 & Time>10, ])
-# 0.2  0.0375  0.005
-# 0.2  0.0287  0.005 da menor H
+# copy pomExp.lin to pomac.lin
+system("cp pomExp.lin pomac.lin")
 
-with(md0, md0[H>=3.91 & H<=4 & Time>50, ])
-# 0.2  0.0375  0.001 da mayor S
-
-# I Use parameters that result in approximately the same richness than BCI
-names(md0)[2:4]<-c("MortalityRate","DispersalDistance","ColonizationRate")
-md0  <- with(md0, md0[Time %in% c(1,5,10,15,seq(20,100,by=10)),])
-md0  <- with(md0, md0[MortalityRate==0.2 & DispersalDistance==0.0287 & ColonizationRate==0.005,])
-md0 <- md0[,c(6,7,9,10)]
-require(pander)
-options(scipen=3,digits=5)
-panderOptions('table.style','grid')
-pander(md0)
-
-compMdl <- with(md1, md1[MortalityRate==0.2 & DispersalDistance==0.0287 & ColonizationRate==0.005,])
-
-compMdl <- with(compMdl, compMdl[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])
-
-rm(md1,md0)
-
-require(lattice)
-require(Hmisc)
-
-qci<- with(compMdl, sapply(SD.Dq,calcCI,7,0.05))
-compMdl$LowCI <- compMdl$Dq-qci
-compMdl$HighCI <- compMdl$Dq+qci
-
-md1 <- with(compMdl, compMdl[Time>=5 &Time<11,])
-
-png("Fig9_DqComp_Neut452_5.png", width=6,height=6,units="in",res=600)
-with(md1,
-    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
-           scales=list(tck=-1),
-           cap=.01,
-           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
-           panel=function(...){
-           panel.abline(h=2, col="grey", lty=2)
-    	     panel.xYplot(...)},
-  		     ylab=expression(italic(D[q])),
-  		     xlab=expression(italic(q)),
-           label.curves=F,
-           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
-           )
-       )
-dev.off()
-
-md1 <- with(compMdl, compMdl[Time>=30 &Time<60,])
-png("Fig9_DqComp_Neut452_30.png", width=6,height=6,units="in",res=600)
-with(md1,
-    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
-           scales=list(tck=-1),
-           cap=.01,
-           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
-           panel=function(...){
-           panel.abline(h=2, col="grey", lty=2)
-           panel.xYplot(...)},
-  		     ylab=expression(italic(D[q])),
-  		     xlab=expression(italic(q)),
-           label.curves=F,
-           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
-           )
-       )
-dev.off()
-
-md0 <- compMdl[compMdl$q!=0,]
-range(md0$R.Dq)
-# 0.947 0.999
-png("FigS5_RDq_Neut452.png", width=6,height=6,units="in",res=600)
-histogram(~R.Dq,data=md0,xlab=expression(italic(R^2)))
-dev.off()
-
-# Leo archivo con las simulaciones de ese set de parametros para ver si hay o no hay 
-# diferencias en los intervalos de confianza.
-
-# Dejo solo dos tiempos para comparar los SD
-
-compMdl <- with(compMdl, compMdl[Time %in% c(5,60),])
-compMdl$Type <- "regr" 
-compMdl <-  compMdl[,c(4:7,9:11)]
+system(paste(neuBin,"sim.par","fishE.inp"),wait=F)
 
@@
 
-Ten repeated simulations with chosen parameters
+Now I will read the densities for different parameters and test SADs and Shannon
 
-    BirthRate=1
-    MortalityRate=0.2 
-    DispersalDistance=0.0287 
-    ColonizationRate=0.005
+```{r testKS_pomac467}
 
-```{r simul10}
+den <- read.delim("Exp467Density.txt")
+names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
 
-source('Fun_Multi_patt.r')
+# from 7 to 473 there are species densities
+# Put simpler names to variables to identify species
+names(den)[7:473]<-as.character(1:467)
 
-setwd("Simul")
-# copy the simulation file parameter file
-system("cp pomacExp_10.lin pomac.lin")
+require(reshape2)
 
-# change the output file
-system("sed -i 's/bciExpZ/bciExpZ005/g' bci452Z.par")
+den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")
 
-# Perform the simulations
-system("./ipsNeutralExp bci452Z.par bci452.inp")
+# Kolmogorov-smirnov test for two distributions
 
-setwd("..")
+parms <- unique(den1[,1:4])
+combo <- combn(nrow(parms),2)
 
-# Read the simulations with same parameters
-#
-md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")
+mks <-adply(combo,2, function(x) {
+      p1 <- parms[x[1],]
+      p2 <- parms[x[2],]
+      d1 <- merge(den1,p1)
+      d2 <- merge(den1,p2)
+      ks <- ks.test(d1$value,d2$value)
+      out <-data.frame(t(paste(p1,p2,sep="-")),p.value=ks$p.value)
+      names(out)[1:length(names(p1))]<-names(p1)
+      return(out)      
+      })
 
-md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])
-md0 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
-md0 <-ldply(md0)
-names(md0)[1] <- "Time"
+mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
 
-md0$Time <- as.numeric(md0$Time)
-md0$Dq <- as.numeric(md0$Dq)
-md0$LowCI <- as.numeric(md0$LowCI)
-md0$HighCI <- as.numeric(md0$HighCI)
+# wich are not different
+format(mks[mks$p.adjust>0.05,c(2:5,7)],digits=4)
 
-md1 <- with(md0, md0[Time>=5 &Time<11,])
-png("Fig9_DqComp_Neut452_B5.png", width=6,height=6,units="in",res=600)
-with(md1,
-    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
-           scales=list(tck=-1),
-           cap=.01,
-           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
-           panel=function(...){
-           panel.abline(h=2, col="grey", lty=2)
-           panel.xYplot(...)},
-    	     ylab=expression(italic(D[q])),
-  		     xlab=expression(italic(q)),
-           label.curves=F,
-           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
-           )
-       )
-dev.off()
+#rm(d1,d2,p1,p2,out,ks,x)
 
-md1 <- with(md0, md0[Time>=30 &Time<60,])
-png("Fig9_DqComp_Neut452_B30.png", width=6,height=6,units="in",res=600)
-with(md1,
-    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Time, type="l",
-           scales=list(tck=-1),
-           cap=.01,
-           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
-           panel=function(...){
-           panel.abline(h=2, col="grey", lty=2)
-           panel.xYplot(...)},
-           ylab=expression(italic(D[q])),
-  		     xlab=expression(italic(q)),
-           label.curves=F,
-           auto.key=list(x=.65,y=.9,title="Year",cex.title=.9, lines=T,points=F,cex=.7),
-           )
-       )
-dev.off()
-
-# Los SD son menores que las estimadas por mfSBA
-md1 <- with(md0, md0[Time==5 | Time==60,])
-
-common_cols <- intersect(colnames(compMdl), colnames(md1))
-compMdl <- rbind(  md1[common_cols], compMdl[common_cols])
-
-#Calculate D1 and DeltaDq(-5,5)
-require(plyr)
-
-d1_delta <- ddply(compMdl, .(Time,Type),summarize, 
-                  DeltaDq = Dq[q==-5]-Dq[q==5], 
-                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
-                  D1=Dq[q==1],
-                  SD.D1=SD.Dq[q==1]   )
-
-# A pandoc table could be generated with pander
-
-require(pander)
-options(scipen=3,digits=5)
-panderOptions('table.style','grid')
-pander(d1_delta)
-
-# Table S2
-
-# Plot with SRS at 5 and 30 years
-
-# the neutral model has to be run again changing the .par file
-# to save the image files and the output name to not overrite the previous 
-# simulations 
-#
-# sa N
-# baseName bciExpZa
-# 
-# Then the program multiSpeciesSBA do the SRS ordering 
-# I run cpp/SpatialAnalysis/mfsba/multiSpeciesSBA to show the SRS 
-#
-
-require(RColorBrewer)
-col.l = c("white",brewer.pal(8,"Dark2"))
-
-png("Fig9_Neut452_5.png", width=6,height=6,units="in",res=600)
-plot_image("Simul/bciExpZa-5Reord.sed","5 Years",1:500,col.l)
-#plot_image("Simul/bciExpZa-5.sed","5 Years")
-dev.off()
-
-#plot_image("Simul/bciExpZa-30.sed","30 Years")
-png("Fig9_Neut452_30.png", width=6,height=6,units="in",res=600)
-plot_image("Simul/bciExpZa-30Reord.sed", "30 Years",1:500,col.l)
-dev.off()
-
-rm(common_cols)
-rm(md0,md1,bci4,rq1,qci)
+# USING THE SAME adply technique a data.frame for ggplot could be generated!!!!!
 
@@
 
-Compare Dq from different times using ten simulations
-
-```{r compareDq}
-
-require(statmod)
-require(reshape2)
-md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")
-
-md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=5)),])
-md1 <- with(md1, md1[q!=0,])
-md1$rep <- rep( 1:10,each=480)
-
-compMd1 <- melt(md1, id.vars=c("Time","rep","q"),measure.var="Dq")
-names(compMd1)
-
-c1 <-dcast(compMd1, Time+rep ~ q)
-names(c1[,13:22])
-c1 <- with(c1, c1[Time<11,])
-
-# Positive q
-compareGrowthCurves(c1$Time,c1[,13:22],nsim=1000)
-
-# Negative q 
-names(c1[,3:12])
-compareGrowthCurves(c1$Time,c1[,3:12],nsim=1000)
-# the output is table S3
-
-c1 <-dcast(compMd1, Time+rep ~ q)
-c1 <- with(c1, c1[Time>=30 & Time<60,])
-
-# Positive q
-compareGrowthCurves(c1$Time,c1[,13:22],nsim=1000)
-
-# Negative q 
-compareGrowthCurves(c1$Time,c1[,3:12],nsim=1000)
-# The output is in TABLE S4
-
-rm(md1,compMd1,c1)
-```
-
-Perform simulations using power law kernel
-
-```{r simulPower}
-setwd("Simul")
-# copy the simulation file parameter file
-system("cp pomacPow_10.lin pomac.lin")
-
-# change the output file
-system("sed -i 's/bciExpZ005/bciPowZ005/g' bci452Z.par")
-
-# Perform the simulations
-system("./ipsNeutralExp bci452Z.par bci452.inp")
-
-setwd("..")
-
-```
-
-Dq Comparison between exponential and power dispersal
-
-```{r compareExpPow}
-
-require(statmod)
-require(reshape2)
-
-md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")
-
-#md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=20)),])
-md0 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
-md0 <-ldply(md0)
-names(md0)[1] <- "Time"
-
-md0$Time <- as.numeric(md0$Time)
-md0$Dq <- as.numeric(md0$Dq)
-md0$LowCI <- as.numeric(md0$LowCI)
-md0$HighCI <- as.numeric(md0$HighCI)
-md0$Type <- "Exp"
-
-md1 <- readNeutral_calcDq("Simul/bciPowZ005mfOrd.txt")
-#md1 <- with(md1, md1[Time %in% c(5,6,7,8,9,seq(10,100,by=20)),])
-md00 <- with(md1,by(md1,Time,calcDq_bootCI,0,"boot"))
-md00 <-ldply(md00)
-names(md00)[1] <- "Time"
-
-md00$Time <- as.numeric(md00$Time)
-md00$Dq <- as.numeric(md00$Dq)
-md00$LowCI <- as.numeric(md00$LowCI)
-md00$HighCI <- as.numeric(md00$HighCI)
-md00$Type <- "Pow"
-
-compMdlExpPow <- rbind(md0,md00)
-md1 <- with(compMdlExpPow, compMdlExpPow[Time %in% c(5,6,7,8,9,10,15,20,25,seq(30,100,by=20)),])
-require(Hmisc)
-with(md1,
-    xYplot(Cbind(Dq,LowCI,HighCI) ~ q|Type, data=md1, nx=FALSE, groups=Time, type="l",
-           scales=list(tck=-1),
-           cap=.01,
-           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
-           panel=function(...){
-           panel.abline(h=2, col="grey", lty=2)
-           panel.xYplot(...)},
-           ylab=expression(italic(D[q])),
-           xlab=expression(italic(q)),
-           label.curves=F,
-           auto.key=list(x=.65,y=.9,title="Dispersal",cex.title=.9, lines=T,points=F,cex=.7),
-           )
-       )
-
-# Compare different dispersals and BCI
-#
-md1 <- with(compMdlExpPow, compMdlExpPow[Time == 90,])
-
-require(plyr)
-
-md2 <- ddply(compBCI, .(q), summarize, 
-                  SD.Dq=sd(Dq),
-                  Dq=mean(Dq))
-
-qci<- with(md2, sapply(SD.Dq,calcCI,7,0.05))
-md2$LowCI <- md2$Dq - qci
-md2$HighCI <- md2$Dq + qci
-md2$Type <- "BCI"
-
-names(md1)
-names(md2)
-names(md1[,c(2:5,7:8)])
-
-md1 <- rbind(md2,md1[,c(2:5,7:8)])
-
-png("Fig10_DqComp_NeutExpPow.png", width=6,height=6,units="in",res=600)
-with(md1,
-    xYplot(Cbind(Dq,LowCI,HighCI) ~ q, data=md1, nx=FALSE, groups=Type, type="l",
-           scales=list(tck=-1),
-           cap=.01,
-           ylim=c(min(LowCI)-.01,max(HighCI)+.01),
-           panel=function(...){
-           panel.abline(h=2, col="grey", lty=2)
-           panel.xYplot(...)},
-           ylab=expression(italic(D[q])),
-           xlab=expression(italic(q)),
-           label.curves=F,
-           auto.key=list(x=.65,y=.9,title="Dispersal",cex.title=.9, lines=T,points=F,cex=.7),
-           )
-       )
-dev.off()
-rm(md1,md2)
-
-# Compare the different dispersals
-
-require(statmod)
-require(reshape2)
-md1 <- readNeutral_calcDq("Simul/bciExpZ005mfOrd.txt")
-md1 <- with(md1, md1[Time == 90 & q!=0,])
-md1$rep <- rep( 1:10,each=nrow(md1)/10)
-md1$Type <- "Exp"
-
-md2 <- readNeutral_calcDq("Simul/bciPowZ005mfOrd.txt")
-md2 <- with(md2, md2[Time == 90 & q!=0,])
-md2$rep <- rep( 1:10,each=nrow(md2)/10)
-md2$Type <- "Pow"
-
-# Get BCI Dq
-
-md3 <- with(compBCI, compBCI[q!=0,])
-md3$Type <- "BCI"
-names(md3)[5]="rep"
-md3$rep <- rep( 1:7,each=20)
-names(md3[,c(1:5,8)])
-names(md2[,c(5:10)])
-md1 <- rbind(md1[,c(5:10)],md2[,c(5:10)])
-
-compMd1 <- melt(rbind(md1,md3[,c(1:5,8)]), id.vars=c("Type","rep","q"),measure.var="Dq")
-names(compMd1)
-
-c1 <-dcast(compMd1, Type+rep ~ q)
-# Positive q
-names(c1[,13:22])
-compareGrowthCurves(c1$Type,c1[,13:22],nsim=1000)
-
-#   Group1 Group2      Stat P.Value adj.P.Value
-#1    BCI    Exp -49.19708       0           0
-#2    BCI    Pow -12.16894       0           0
-#3    Exp    Pow  81.79017       0           0
-
-# Negative q 
-names(c1[,3:12])
-compareGrowthCurves(c1$Type,c1[,3:12],nsim=1000)
-
-#  Group1 Group2      Stat P.Value adj.P.Value
-#1    BCI    Exp 110.70741       0           0
-#2    BCI    Pow  16.72702       0           0
-#3    Exp    Pow -90.12642       0           0
-
-rm(c1,md1,md2,md3,md00)
-
-# Plot spatial distribution of the models
-
-require(RColorBrewer)
-col.l = c("white",brewer.pal(8,"Dark2"))
-#col.l = colorRampPalette(c(brewer.pal(8,"Paired")))(64)
-
-png("Fig10_Neut452_Exp90.png", width=6,height=6,units="in",res=600)
-plot_image("Simul/bciExpZa-90Reord.sed","",1:500,col.l,5)
-dev.off()
-
-png("Fig10_Neut452_Pow90.png", width=6,height=6,units="in",res=600)
-plot_image("Simul/bciPowZa-90Reord.sed","",1:500,col.l,5)
-dev.off()
-```
-
-DeltaDq Comparison between BCI, exponential and power dispersal
-
-```{r DeltaD5_BCI_vs_mdl, echo=FALSE}
-
-require(plyr)
-
-# Calculate DeltaD5 for BCI, compBCI was previously saved.
-
-d1_delta <- ddply(compBCI, .(Year),summarize, 
-                  DeltaDq = Dq[q==-5]-Dq[q==5], 
-                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
-                  D1=Dq[q==1],
-                  SD.D1=SD.Dq[q==1]   )
-
-# Calculate SD of DeltaDq using all years of BCI
-#sd_DeltaD5 <- sd(d1_delta$DeltaDq)
-#calcCI(sd_DeltaD5,7,0.05)
-#mean(d1_delta$DeltaDq)  
-# CI 0.01475477
-# Mean 1.101303
-
-md1 <- with(compMdlExpPow, compMdlExpPow[Time %in% seq(30,60,by=5),])
-
-d2_delta <- ddply(md1, .(Time,Type),summarize, 
-                  DeltaDq = Dq[q==-5]-Dq[q==5], 
-                  SD.DeltaDq=sqrt(SD.Dq[q==-5]^2+SD.Dq[q==5]^2),
-                  D1=Dq[q==1],
-                  SD.D1=SD.Dq[q==1]   )
-names(d1_delta)[1]="Time"
-d1_delta$Type = "BCI"
-names(d2_delta)
-names(d1_delta)
-d2_delta <- rbind(d2_delta,d1_delta)
-d1_delta <- ddply(d2_delta, .(Type), summarize, 
-                  SD.DeltaDq=sd(DeltaDq),
-                  SD.D1=sd(D1),
-                  D1=mean(D1),
-                  DeltaDq=mean(DeltaDq))
-
-# A pandoc table could be generated with pander
-require(lattice)
-#bwplot(Type ~ DeltaDq,data=d2_delta)
-#bwplot(Type ~ D1,data=d2_delta)
-
-#require(pander)
-#options(scipen=3,digits=5)
-#panderOptions('table.style','grid')
-#pander(d1_delta)
-
-qci<- with(d1_delta, sapply(SD.DeltaDq,calcCI,7,0.05))
-d1_delta$CI.DeltaDq <- qci
-require(ggplot2)
-ggplot(d1_delta, aes(x=Type, y=DeltaDq)) +
-geom_errorbar(aes(ymin=DeltaDq-CI.DeltaDq, ymax=DeltaDq+CI.DeltaDq), width=.1) +
-geom_point(fill="white",shape=21)
-
-rm(d1_delta,d2_delta,qci,md1)
-```
+The most important not-different are the ones that correspond to neutral vs non-neutral
+thus we will try to differentiate them using Dq

### 2014-04-30 R/Neutral_fun.r

@@ -1,17 +1,18 @@
 
 # Generate inp parameters file for simulation
 #
-genNeutralParms <- function(fname,side,mprob,birth,mortality,dispersal,colonization){
+genNeutralParms <- function(fname,side,mprob,birth,mortality,dispersal,colonization,replace=0){
   S <- length(mprob)
   parm <- data.frame( n=c(rep(0,3),1:S) ,prob=c(rep(0,3),prob=mprob))
   parm$text <- "" 
   parm$z <- 0
   parm$text[1] <- paste(side,side,sep="\t")
   parm$text[2] <- S
-  parm$text[3] <- paste(0,birth,mortality,dispersal,colonization,sep="\t")
+  parm$text[3] <- paste(0,birth,mortality,dispersal,colonization,replace,sep="\t")
   nff <- S+3
   parm$text[4:nff] <-   with(parm[4:nff,], paste(n,z,z,z,format(sort(prob),scientific=F),sep="\t"))                    
-  fname <- paste0(fname,S,".inp")
+  if(!grepl(".inp",fname)) fname <-paste0(fname,".inp")
+
   write.table(parm$text,fname,sep="\t",row.names=F,col.names=F,quote=F)
 }
 
@@ -23,6 +24,6 @@ genPomacParms <- function(fname,GrowthR,MortR,DispD,ColonR,ReplaceR,numRep=1)
   pom <- expand.grid(GrowthRate=GrowthR,MortalityRate=MortR, DispersalDistance=DispD, 
     ColonizationRate=ColonR,ReplacementRate=ReplaceR)
   pom <- pom[rep(seq_len(nrow(pom)), numRep), ]
-  if(!grepl("lin",fname)) fname <-paste0(fname,".lin")
+  if(!grepl(".lin",fname)) fname <-paste0(fname,".lin")
   write.table(pom,fname,sep="\t",row.names=F,col.names=T,quote=F)
 }

### 2014-05-08 R/Neutral_simul.Rmd
Add simulations with more ReplacementR values

@@
 ```{r generateLogSerParms}
+
+s_wait <- F # variable to make R wait until simulations ends or not
 
@@
 
-system(paste(neuBin,"sim.par","fishE.inp"),wait=F)
+system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)
 
@@
 
-Let's try simulations with different parameters using pomac and at Time=100
+Let try simulations with different parameters using pomac and at Time=100
 
@@
 ```{r testKS_pomac467}
+# Read simulation output and change from wide to long format NO TIME
+#
+meltDensityOut_NT <- function(fname,num_sp){
+  den <- read.delim(fname)
+  names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
+
+  # from 7 to 473 there are species densities
+  # Put simpler names to variables to identify species
+  names(den)[7:(6+num_sp)]<-as.character(1:num_sp)
+
+  require(reshape2)
+
+  den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")
+
+}
 
@@
 
+require(plyr)
 mks <-adply(combo,2, function(x) {
@@
       ks <- ks.test(d1$value,d2$value)
-      out <-data.frame(t(paste(p1,p2,sep="-")),p.value=ks$p.value)
-      names(out)[1:length(names(p1))]<-names(p1)
+      out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
+      ln <-length(names(p1))*3
+      names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
       return(out)      
       })
+
+#p1 <- parms[1,]
+#p2 <- parms[9,]
+#d1 <- merge(den1,p1)
+#d2 <- merge(den1,p2)
+#ks <- ks.test(d1$value,d2$value)
+#out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
+#ln <-length(names(p1))*3
+#names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
+#rm(d1,d2,p1,p2,out,ks,ln)
 
@@
 # wich are not different
-format(mks[mks$p.adjust>0.05,c(2:5,7)],digits=4)
 
-#rm(d1,d2,p1,p2,out,ks,x)
+format(mks[mks$p.adjust>0.05,c(10:13,14:15)],digits=4)
+format(mks[mks$p.adjust>0.1,c(10:13,14:15)],digits=4)
 
-# USING THE SAME adply technique a data.frame for ggplot could be generated!!!!!
+format(mks[mks$p.value>0.01,c(10:13,14:15)],digits=4)
+
+# Graph on pair with different mechanisms but not different SAD
+#
+# eks: 1 row data.frame with 2 sets of parms for which ks.test was done (fixed TIME)
+# den1: full data in long format
+#
+mergePairSAD <- function(eks, den1){
+# eks <- mks[61,]
+
+  den2 <-merge(den1,eks,by.x=c(1:4),by.y=c(2:5))[,1:6]
+  den2 <- den2[den2$value>0,]
+  den2$parms <-paste(eks[,2:5],collapse="_")
+  den2$Rank <- nrow(den2) - rank(den2$value) +1
+
+  den3 <-merge(den1,eks,by.x=c(1:4),by.y=c(6:9))[,1:6]
+  den3 <- den3[den3$value>0,]
+  den3$parms <-paste(eks[,6:9],collapse="_")
+  den3$Rank <- nrow(den3) - rank(den3$value) +1
+  den2 <- rbind(den2,den3)
+
+  }
+# SE PODRIA HACER CON ddply para hacer varias filas del mks !!!!!
+
+#den2 <- ddply(den1,.(Time), function(x) { 
+  #tmp <- x[x$value>0,]
+#  tmp <- x[order(x$value),]
+#  tmp$Ord <- nrow(x):1
+#  data.frame(tmp)
+#  })
+
+format(mks[mks$p.value<0.05 & mks$p.adjust>0.05,c(10:13,14:15)],digits=4)
+
+debug(plotPairSAD)
+psa <-mergePairSAD(mks[61,],den1)
+# p.value = 
+require(ggplot2)
+g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line()
+g
+
+psa <- mergePairSAD(mks[105,],den1)
+(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
+g + geom_point()
+```
+
+In this case there are no semejant SAD for different mechanisms (neutral vs hierarchical) but some of adjusted p values lead to not reject differences when SADs seems different like mks[61,],105,107
+
+Now I will simulate with a smaller Replacement = 0.01 / 0.1 and compare with Replacement=0
+
+```{r simul_pomac467_R001,echo=F,message=F,warning=F}
+
+setwd("Simul")
+
+# read par file with simulations parameters
+
+par <- read.table("sim.par",quote="",stringsAsFactors=F)
+
+# Number of time steps 
+par[par$V1=="nEvals",]$V2 <- 100
+
+par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
+par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
+par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
+par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
+par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
+par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
+                              # 1:several simulations with pomac.lin parameters
+
+write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
+
+# I will not delete old simulations
+# system("rm Exp467*")
+
+# I have to modify pomExp.lin to make different simulations
+#undebug(genPomacParms)
+
+genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0.01))
+
+# copy pomExp.lin to pomac.lin
+system("cp pomExp.lin pomac.lin")
+
+system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)
+
+# add more paremeter combinations 
+genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0.1,0.01))
+system("cp pomExp.lin pomac.lin")
+system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)
+
+########### TEST THIS FUNCTION
+den4 <- meltDensityOut_NT("Exp467Density.txt",nrow(ff))
 
 ```
-
-The most important not-different are the ones that correspond to neutral vs non-neutral
-thus we will try to differentiate them using Dq

### 2014-05-10 R/Neutral_simul.Rmd
Add funct to melt SAD to long & simul w/Replacement

@@
 ```{r testKS_pomac467}
-# Read simulation output and change from wide to long format NO TIME
-#
-meltDensityOut_NT <- function(fname,num_sp){
-  den <- read.delim(fname)
-  names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
 
-  # from 7 to 473 there are species densities
-  # Put simpler names to variables to identify species
-  names(den)[7:(6+num_sp)]<-as.character(1:num_sp)
-
-  require(reshape2)
-
-  den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")
-
-}
-
-den <- read.delim("Exp467Density.txt")
-names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
-
-# from 7 to 473 there are species densities
-# Put simpler names to variables to identify species
-names(den)[7:473]<-as.character(1:467)
-
-require(reshape2)
-
-den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")
+den1 <- meltDensityOut_NT("Simul/Exp467Density.txt",nrow(ff))
 
@@
 
-# Graph on pair with different mechanisms but not different SAD
-#
-# eks: 1 row data.frame with 2 sets of parms for which ks.test was done (fixed TIME)
-# den1: full data in long format
-#
-mergePairSAD <- function(eks, den1){
-# eks <- mks[61,]
-
-  den2 <-merge(den1,eks,by.x=c(1:4),by.y=c(2:5))[,1:6]
-  den2 <- den2[den2$value>0,]
-  den2$parms <-paste(eks[,2:5],collapse="_")
-  den2$Rank <- nrow(den2) - rank(den2$value) +1
-
-  den3 <-merge(den1,eks,by.x=c(1:4),by.y=c(6:9))[,1:6]
-  den3 <- den3[den3$value>0,]
-  den3$parms <-paste(eks[,6:9],collapse="_")
-  den3$Rank <- nrow(den3) - rank(den3$value) +1
-  den2 <- rbind(den2,den3)
-
-  }
 # SE PODRIA HACER CON ddply para hacer varias filas del mks !!!!!
@@
 
-debug(plotPairSAD)
 psa <-mergePairSAD(mks[61,],den1)
@@
 
-########### TEST THIS FUNCTION
-den4 <- meltDensityOut_NT("Exp467Density.txt",nrow(ff))
+# Read all simulations and change to long format
+
+den1 <- meltDensityOut_NT("Simul/Exp467Density.txt",nrow(ff))
+
+pairKS_SAD(den1)
+
+format(mks[mks$p.adjust>0.05,c(10:13,14:15)],digits=4)
+
+nrow(mks[mks$p.adjust>0.05,c(10:13,14:15)])/nrow(mks)
+
+psa <- mergePairSAD(mks[468,],den1)
+
+require(ggplot2)
+
+(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
 
 ```
+
+The proportion of equal distributions is 0.30 what happens if we test Dq

### 2014-05-10 R/Neutral_fun.r

@@ -27,3 +27,68 @@ genPomacParms <- function(fname,GrowthR,MortR,DispD,ColonR,ReplaceR,numRep=1)
   if(!grepl(".lin",fname)) fname <-paste0(fname,".lin")
   write.table(pom,fname,sep="\t",row.names=F,col.names=T,quote=F)
 }
+
+# Merge data from 2 simulations 
+# 
+# eks: 1 row data.frame with 2 sets of parms for which ks.test was done (fixed TIME)
+# den1: full data in long format
+#
+mergePairSAD <- function(eks, den1){
+  # eks <- mks[61,]
+  
+  den2 <-merge(den1,eks,by.x=c(1:4),by.y=c(2:5))[,1:6]
+  den2 <- den2[den2$value>0,]
+  den2$parms <-paste(eks[,2:5],collapse="_")
+  den2$Rank <- nrow(den2) - rank(den2$value) +1
+  
+  den3 <-merge(den1,eks,by.x=c(1:4),by.y=c(6:9))[,1:6]
+  den3 <- den3[den3$value>0,]
+  den3$parms <-paste(eks[,6:9],collapse="_")
+  den3$Rank <- nrow(den3) - rank(den3$value) +1
+  den2 <- rbind(den2,den3)
+  
+}
+
+# pairwise KS test for all combinations of parameters in denl= density in long format
+# parameters are in columns 1:4
+# 
+#
+pairKS_SAD <- function(denl){
+  
+  parms <- unique(denl[,1:4])
+  combo <- combn(nrow(parms),2)
+  
+  require(plyr)
+  mks <-adply(combo,2, function(x) {
+    p1 <- parms[x[1],]
+    p2 <- parms[x[2],]
+    d1 <- merge(denl,p1)
+    d2 <- merge(denl,p2)
+    ks <- ks.test(d1$value,d2$value)
+    out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
+    ln <-length(names(p1))*3
+    names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
+    return(out)      
+  })
+  mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
+  return(mks)
+}
+
+
+
+
+# Read simulation output and change from wide to long format NO TIME
+#
+meltDensityOut_NT <- function(fname,num_sp){
+  den <- read.delim(fname)
[…]

### 2014-07-18 Neutral_simul.Rmd
Several modifications to Rmd

# Multifractal analysis of multispecies spatial distributions - Model simulations

I generate parameter files for the simulation of neutral/hierarchical model using logseries as the metacommunity distribution

```{r setup, eval=T }

simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

```

This is run only once to generate the metacommunity then set eval=FALSE and generate
a set of parameter files to modify

```{r generateLogSerParms, eval=FALSE,echo=F,message=F,warning=F}
# Generate a SAD for metacommunity using a logseries 
#
# side is the side of the simulation lattice
#
# N is the total number of individuals 
#
# S is the species richness 
#

require(untb)
side <- 500
N <- side*side
S <- 450 
ff<-fisher.ecosystem(N=N,S=S,nmax=N)
plot(ff)
nrow(ff)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
ff$prob <- ff$FreqT/sum(ff$FreqT)

# Parameters
#
# Mortality = 0.2 - 0.4
# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
#                         2.5 -> 0.4
# Colonization = 0.001 -0.0001
# Replacement  = 0 - 1

setwd("Simul")
#undebug(genNeutralParms)
# First generate de inp file with species and metacommunity parameters 
genNeutralParms("fishE",500,ff$prob,1,0.2,0.04,0.001)

# Then pomac.lin to simulate a range of parmeters and repetitions.
#
# Generates pomac.lin for multiple simulations exponential dispersal to compare hierarchical and neutral communities  
# and see when they have similar H and compare if they have similar SAD

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,1))

# we need the par file with the simulations parameters

par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100
# Change interval to measure Density and Diversity
par[par$V1=="inter",]$V2 <- 10
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

# Run the model with the parameter ReplacementRate turned on = Hierarchical 
# and exponential dispersal 
#
# Set the location of the binary 
#neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

# copy pomExp.lin to pomac.lin
#system("cp pomExp.lin pomac.lin")

# make simulations
#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

```

## Simulations with different parameters using pomac and at Time=100

Now I will simulate the model to Time=100 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and ten repetitions

```{r simul_pomac467_T100,echo=F,message=F,warning=F}

setwd("Simul")

spMeta <- 467 # nrow(ff) number of species in the generated metacommunity

bName <- paste0("Exp", spMeta) # Base name based in the dispersal "Exp" and number of species in metacommunity "467"

if(simul) {

  # Delete old simulations
  system("rm Exp467T100*")

  # read par file with simulations parameters

  par <- read.table("sim.par",quote="",stringsAsFactors=F)

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 100

  par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0(bName ,"T100") # Time = 100 
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters

  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

  # I have to modify pomExp.lin to make different simulations
  #undebug(genPomacParms)

  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)

  # copy pomExp.lin to pomac.lin
  system("cp pomExp.lin pomac.lin")

  system(paste(neuBin,"sim.par","fishE.inp"))
}

# Read all simulations and change to long format

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)

# have to make averages of 
require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

names(den2)[6] <- "value" # the functions use this field name

# Select a subset to test the procedure !
#
#den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]

mks100 <- pairKS_SAD(den2)

# Which are not different
format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
compM <- data.frame(time=100,notdif=propNotDiffSAD(mks100),method="SAD")

# Plot the first pairs not different 
#
mks <- mks100[mks100$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

# Plot the first pair different 
#
mks <- mks100[mks100$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

# Calculate ranks for each parameter combination with different ReplacementRate
#
den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
den3 <- calcRankSAD(den2)

(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

rm(mks,psa,den1,den2,den3)

#
# Now check differences using multifractals mfSAD o mfSRS
#

# Leer Dq SRS
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="SRS"))

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

c3 <- c2
c3$method <- "SRS"

# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
#

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

# Build data.frame with proportion
#
compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="DqSAD"))

c2$method <- "DqSAD"
c3 <- rbind(c3,c2)

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)

# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!

kable(compM)

setwd(oldcd)
rm(c1,c2,Dq2)
rm(den1,den)
save.image()
```

# Simulations at T=500

```{r simul_pomac467_T500, eval=FALSE,echo=F,message=F,warning=F }

setwd("Simul")

# read par file with simulations parameters
if(simul)
{
  system("rm Exp467T100*")

  par <- read.table("sim.par",quote="",stringsAsFactors=F)

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 500
  par[par$V1=="inter",]$V2 <- 500 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 500  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T500")
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters

  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

  # I will not delete old simulations
  # system("rm Exp467*")

  # I have to modify pomExp.lin to make different simulations

  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.01,0.1,1))

  # copy pomExp.lin to pomac.lin
  system("cp pomExp.lin pomac.lin")

  s <- paste(neuBin,"sim.par","fishE.inp")
  s
  system(s)
}

# Read all simulations and change to long format

den1 <- meltDensityOut_NT(paste0(bName,"T500Density.txt"),spMeta)

# have to make averages of 
require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

names(den2)[6] <- "value" # the functions use this field name

# Test pairwise diferences in SAD
#
mks100 <- pairKS_SAD(den2)

# Which are not different
format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSAD(mks100),method="SAD"))

# Plot the first pairs not different 
#
mks <- mks100[mks100$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

# Plot the first pair different 
#
mks <- mks100[mks100$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

# Calculate ranks for each parameter combination with different ReplacementRate
#
den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
den3 <- calcRankSAD(den2)

(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

rm(mks,psa,den1,den2,den3)

#
# Now check differences using multifractals mfSAD o mfSRS
#

# Leer Dq SRS
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfOrd.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="SRS"))

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

c2$method <- "SRS"
c3 <- rbind(c3,c2)

# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
#

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

# Build data.frame with proportion
#
compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="DqSAD"))

c2$method <- "DqSAD"
c3 <- rbind(c3,c2)

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)

# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!

kable(compM)

setwd(oldcd)
rm(c1,c2,Dq2)
rm(den1,den)
save.image()

```

Now the same set of simulations for T=1000

```{r simul_pomac467_T1000, eval=FALSE,echo=F,message=F,warning=F}
setwd("Simul")

# read par file with simulations parameters

par <- read.table("sim.par",quote="",stringsAsFactors=F)

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 1000
par[par$V1=="inter",]$V2 <- 1000 # interval to measure Density and Diversity
par[par$V1=="init",]$V2 <- 1000  # Firs time of measurement = interval
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T1000")
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

# I will not delete old simulations
# system("rm Exp467*")

# I have to modify pomExp.lin to make different simulations

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.01,0.1,1))

# copy pomExp.lin to pomac.lin
system("cp pomExp.lin pomac.lin")

s <- paste(neuBin,"sim.par","fishE.inp")
s
if(simul) system(s,wait=s_wait)

den1 <- meltDensityOut_NT("Exp467T1000Density.txt",nrow(ff))

mks1000 <- pairKS_SAD(den1)

# Which are not different
format(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
nrow(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)])/nrow(mks1000)

propNotDiffSAD(mks100)  
propNotDiffSAD(mks500)  
propNotDiffSAD(mks1000)  
```

The the proportion of different SAD is constant from T=500 it seems we reach steady state. I have to compare now using H and Dq, for that I should do repeated simulations
of each combination.

```{r boot_H_pomac467_T500,eval=FALSE,echo=F,message=F,warning=F}

setwd("Simul")

require(plyr)
require(boot)
require(vegan)

# den <- readWideDensityOut("Exp467T100Density.txt")
num_sp <- nrow(ff)
# how to apply a function to each row of a data frame
hh <- function(x) diversity(x[7:(6+num_sp)])
H <- apply(den,1,hh)

#H <- lapply(den,function(x) diversity(x[7:(6+num_sp)]))
#ldply(H)
# data.frame(colembolos = rowSums(spe[,1:5]), acaros=rowSums(spe[,6:33]),lombrices=rowSums(spe[,34:41]))
den[c(1,7),c("H","Richness")]
den[c(2,4),c("H","Richness")]

difh <- den[c(2,4),7:(6+num_sp)]*(500*500)
difh <- H_bss(difh)

print(difh)
summary(difh)

ciH <-ddply(s_col,.(Ambiente),function(df) boot_shannon(df[,1:5]) )

```

### 2014-07-18 R/Test_Neutral_simul.Rmd
Several modifications to Rmd

--- 2014-04-30 R/Neutral_simul.Rmd
@@
-# Multifractal analysis of multispecies spatial distributions - Model simulations
+# TEST for Multifractal analysis of multispecies spatial distributions - Model simulations
 
@@
 
-```{r generateLogSerParms}
+```{r setup, eval=T }
+
+s_wait <- T # variable to make R wait until simulations ends or not
+
+simul  <- F # variable to perform or not the simulations
 
@@
 
+# Set the location of the binary 
+#
+neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"
+
+```
+
+## Generate a metacommunity using a logseries
+
+side: is the side of the simulation lattice
+
+N: is the total number of individuals
+
+S: is the species richness
+
+```{r generateLogSerParms, eval=FALSE,echo=F,message=F,warning=F}
 # Generate a SAD for metacommunity using a logseries 
@@
 
-system(paste(neuBin,"sim.par","fishE.inp"),wait=F)
+# make simulations
+if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)
 
@@
 
-Now I will read the output generated from simulations (not from pomac) to test if the SAD are equal in time using Kolmogorov Smirnov test.
+## Test: Simulations with Time 1-100
 
-```{r testRAD_KS}
+Now I will read the output generated from simulations (not from pomac) to test if the SAD are equal in time using Kolmogorov Smirnov test. These simulations have TIME as a variable
+
+```{r testRAD_KS,eval=FALSE, echo=F,message=F,warning=F}
 
@@
 Thus the SAD at Time=10 is not different from Time=100
-
-Let's try simulations with different parameters using pomac and at Time=100
-
-```{r simul_pomac467}
-
-setwd("Simul")
-
-# we need the par file with the simulations parameters
-
-par <- read.table("sim.par",quote="",stringsAsFactors=F)
-# Change base name
-
-# Number of time steps 
-par[par$V1=="nEvals",]$V2 <- 100
-# Change interval to measure Density and Diversity
-par[par$V1=="inter",]$V2 <- 100
-par[par$V1=="init",]$V2 <- 100
-
-par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
-par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
-par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
-par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
-                              # 1:several simulations with pomac.lin parameters
-
-write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
-
-# delete old simulations
-system("rm Exp467*")
-
-# copy pomExp.lin to pomac.lin
-system("cp pomExp.lin pomac.lin")
-
-system(paste(neuBin,"sim.par","fishE.inp"),wait=F)
-
-```
-
-Now I will read the densities for different parameters and test SADs and Shannon
-
-```{r testKS_pomac467}
-
-den <- read.delim("Exp467Density.txt")
-names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
-
-# from 7 to 473 there are species densities
-# Put simpler names to variables to identify species
-names(den)[7:473]<-as.character(1:467)
-
-require(reshape2)
-
-den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")
-
-# Kolmogorov-smirnov test for two distributions
-
-parms <- unique(den1[,1:4])
-combo <- combn(nrow(parms),2)
-
-mks <-adply(combo,2, function(x) {
-      p1 <- parms[x[1],]
-      p2 <- parms[x[2],]
-      d1 <- merge(den1,p1)
-      d2 <- merge(den1,p2)
-      ks <- ks.test(d1$value,d2$value)
-      out <-data.frame(t(paste(p1,p2,sep="-")),p.value=ks$p.value)
-      names(out)[1:length(names(p1))]<-names(p1)
-      return(out)      
-      })
-
-mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
-
-# wich are not different
-format(mks[mks$p.adjust>0.05,c(2:5,7)],digits=4)
-
-#rm(d1,d2,p1,p2,out,ks,x)
-
-# USING THE SAME adply technique a data.frame for ggplot could be generated!!!!!
-
-```
-
-The most important not-different are the ones that correspond to neutral vs non-neutral
-thus we will try to differentiate them using Dq

### 2014-07-18 R/Neutral_fun.r

@@ -49,6 +49,20 @@ mergePairSAD <- function(eks, den1){
   
 }
 
+# Calculate Ranks for every parameter combination, for ggplot2  
+#
+calcRankSAD  <- function(den)
+{
+  require(plyr)
+  hh <- function(x) { 
+  x1 <- x[x$value>0,]
+  x1$parms <- paste(unique(x[,1:4]),collapse="_")
+  x1$Rank <- nrow(x1) - rank(x1$value) +1
+  return(x1)
+  }
+  ddply(den, .(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate),hh )
+}
+
 # pairwise KS test for all combinations of parameters in denl= density in long format
 # parameters are in columns 1:4
 # 
@@ -91,4 +105,124 @@ meltDensityOut_NT <- function(fname,num_sp){
   
   den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")
   
+}
+
+# Read simulation output and set variable names in wide format 
+#
+readWideDensityOut <- function(fname,num_sp){
+  den <- read.delim(fname)
+  names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
+  return(den)
+}
+
+
+# Proportion of not different SAD at 0.05 Hommel adjusted level 
+#
+propNotDiffSAD <- function(mk) nrow(mk[mk$p.adjust>0.05,c(10:13,14:15)])/nrow(mk)
+
+# Proportion of not different SRS at 0.05 Hommel adjusted level 
+#
+propNotDiffSRS <- function(mk) nrow(mk[mk$adj.P.Value>0.05,])/nrow(mk)
+
+
+# Calculates Dq from a data.frame read from the output of neutral model 
+# auxiliar function for the next one
+#
+calcDq_frame <- function(pp)
+{
+  pp$Dq  <- with(pp,ifelse(q==1,alfa,Tau/(q-1)))
+  pp$SD.Dq  <- with(pp,ifelse(q==1,SD.alfa,abs(SD.Tau/(q-1))))
+  pp$R.Dq <- with(pp,ifelse(q==1,R.alfa,R.Tau))
+  return(pp[,c(1:6,15:17)])
+}              
[…]

### 2014-07-21 Neutral_simul.Rmd
Add compMethods_Time function

@@
 neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"
+
+# Load data if run only one chunk 
+load(".RData")
 
@@
 ff$prob <- ff$FreqT/sum(ff$FreqT)
+
+spMeta <- nrow(ff)
 
@@
 ```{r simul_pomac467_T100,echo=F,message=F,warning=F}
-
 setwd("Simul")
@@
 
-# Read all simulations and change to long format
+m <- compMethods_Time(bName,100,spMeta)
+
+mks1 <- m$mPval
+mks1 <- mks1[mks1$method=="SAD",]
+
+# Which are not different
+format(mks1[mks1$p.adjust>0.05,],digits=4)
 
 den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)
+# Select a subset to test the procedure !
+#
+den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]
 
-# have to make averages of 
 require(plyr)
@@
 
-names(den2)[6] <- "value" # the functions use this field name
-
-# Select a subset to test the procedure !
-#
-#den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
-
-mks100 <- pairKS_SAD(den2)
-
-# Which are not different
-format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)
-
-# which is the proportion of not different
-compM <- data.frame(time=100,notdif=propNotDiffSAD(mks100),method="SAD")
-
 # Plot the first pairs not different 
 #
-mks <- mks100[mks100$p.adjust>0.05,]
+
+mks <- mks1[mks1$p.adjust>0.05,]
 psa <- mergePairSAD(mks[1,],den2)
@@
 
-(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
+(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line() + ggtitle("SAD not dif"))
 
@@
 #
-mks <- mks100[mks100$p.adjust<=0.05,]
+mks <- mks1[mks1$p.adjust<=0.05,]
 psa <- mergePairSAD(mks[1,],den2)
-(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
+(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line()
+ + ggtitle("SAD different"))
 
@@
 
-rm(mks,psa,den1,den2,den3)
+rm(mks,psa)
 
@@
 
-#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])
-
-# Testing pairwise differences
-#
-c2 <- compDq_frame(Dq1,35)
-
-compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="SRS"))
-
-#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")
-
-c3 <- c2
-c3$method <- "SRS"
-
 # Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
@@
 
-plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
-plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
-plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
+plotDq_ReplaceR(Dq1,0.2,0.04,0.0001, "SRS")
+plotDq_ReplaceR(Dq1,0.2,0.4,0.001, "SRS")
+plotDq_ReplaceR(Dq1,0.2,0.04,0.001, "SRS")
+
+mks1 <- m$mPval
+mks1 <- mks1[mks1$method=="SRS",]
+
+mks <- mks1[mks1$p.adjust<=0.05,]
+# NO FUNCIONA MERGE
+#psa <- mergePairSAD(mks[1,],Dq1)
+
 #
@@
 
-#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])
-
-# Testing pairwise differences
-#
-c2 <- compDq_frame(Dq1,35)
-
-# Build data.frame with proportion
-#
-compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="DqSAD"))
-
-c2$method <- "DqSAD"
-c3 <- rbind(c3,c2)
-
-#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")
-
-plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
-plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
-plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
+plotDq_ReplaceR(Dq1,0.2,0.04,0.001,"DqSAD")
+plotDq_ReplaceR(Dq1,0.2,0.4,0.001,"DqSAD")
+plotDq_ReplaceR(Dq1,0.2,0.04,0.0001,"DqSAD")
 
@@
 
-kable(compM)
+compM
+
+m$compM
+
+compM <- m$compM
+
+mPval <- m$mPval
 
 setwd(oldcd)
-rm(c1,c2,Dq2)
+rm(c1,c2,Dq2,Dq1)
 rm(den1,den)
 save.image()
+
 ```
 
-# Simulations at T=500
+## Simulations at Time=500
 
-```{r simul_pomac467_T500, eval=FALSE,echo=F,message=F,warning=F }
+```{r simul_pomac467_T500, eval=T,echo=F,message=F,warning=F }
 
@@
 {
-  system("rm Exp467T100*")
+  # Delete old simulations
+  system("rm Exp467T500*")
 
@@
   par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
-  par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T500")
+  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T500")
   par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
@@
 
-  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.01,0.1,1))
+  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
 
@@
   s
-  system(s)
+  system(s,wait=F)
 }
 
-# Read all simulations and change to long format
+m <- compMethods_Time(bName,500,spMeta)
 
-den1 <- meltDensityOut_NT(paste0(bName,"T500Density.txt"),spMeta)
+compM <- rbind(compM,m$compM)
 
-# have to make averages of 
-require(plyr)
-den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))
-
-names(den2)[6] <- "value" # the functions use this field name
-
-# Test pairwise diferences in SAD
-#
-mks100 <- pairKS_SAD(den2)
-
-# Which are not different
-format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)
-
-# which is the proportion of not different
-compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSAD(mks100),method="SAD"))
-
-# Plot the first pairs not different 
-#
-mks <- mks100[mks100$p.adjust>0.05,]
-psa <- mergePairSAD(mks[1,],den2)
-
-require(ggplot2)
-
-(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
-
-# Plot the first pair different 
-#
-mks <- mks100[mks100$p.adjust<=0.05,]
-psa <- mergePairSAD(mks[1,],den2)
-(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
-
-# Calculate ranks for each parameter combination with different ReplacementRate
-#
-den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
-den3 <- calcRankSAD(den2)
-
-(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
-
-rm(mks,psa,den1,den2,den3)
-
-#
-# Now check differences using multifractals mfSAD o mfSRS
-#
-
-# Leer Dq SRS
-#
-Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfOrd.txt"))
-
-#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])
-
-# Testing pairwise differences
-#
-c2 <- compDq_frame(Dq1,35)
-
-compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="SRS"))
-
-#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")
-
-c2$method <- "SRS"
-c3 <- rbind(c3,c2)
-
-# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
-#
-
-plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
-plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
-plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
-#
-#
-# Leer Dq SAD
-#
-Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))
-
-#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])
-
-# Testing pairwise differences
-#
-c2 <- compDq_frame(Dq1,35)
-
-# Build data.frame with proportion
-#
-compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="DqSAD"))
-
-c2$method <- "DqSAD"
-c3 <- rbind(c3,c2)
-
-#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")
-
-plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
-plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
-plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
-
-# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!
-
-kable(compM)
+mPval <- rbind(mPval,m$mPval)
 

### 2014-07-21 R/Neutral_fun.r

@@ -36,15 +36,15 @@ genPomacParms <- function(fname,GrowthR,MortR,DispD,ColonR,ReplaceR,numRep=1)
 mergePairSAD <- function(eks, den1){
   # eks <- mks[61,]
   
-  den2 <-merge(den1,eks,by.x=c(1:4),by.y=c(2:5))[,1:6]
-  den2 <- den2[den2$value>0,]
-  den2$parms <-paste(eks[,2:5],collapse="_")
-  den2$Rank <- nrow(den2) - rank(den2$value) +1
+  den2 <-merge(den1,eks,by.x=c(1:4),by.y=c(1:4))[,1:6]
+  den2 <- den2[den2$den>0,]
+  den2$parms <-paste(eks[,1:4],collapse="_")
+  den2$Rank <- nrow(den2) - rank(den2$den) +1
   
-  den3 <-merge(den1,eks,by.x=c(1:4),by.y=c(6:9))[,1:6]
-  den3 <- den3[den3$value>0,]
-  den3$parms <-paste(eks[,6:9],collapse="_")
-  den3$Rank <- nrow(den3) - rank(den3$value) +1
+  den3 <-merge(den1,eks,by.x=c(1:4),by.y=c(5:8))[,1:6]
+  den3 <- den3[den3$den>0,]
+  den3$parms <-paste(eks[,5:8],collapse="_")
+  den3$Rank <- nrow(den3) - rank(den3$den) +1
   den2 <- rbind(den2,den3)
   
 }
@@ -79,9 +79,9 @@ pairKS_SAD <- function(denl){
     d1 <- merge(denl,p1)
     d2 <- merge(denl,p2)
     ks <- ks.test(d1$value,d2$value)
-    out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
-    ln <-length(names(p1))*3
-    names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
+    out <-data.frame(p1,p2,stat=ks$statistic,p.value=ks$p.value,stringsAsFactors=F)
+    ln <-length(names(p1))*2
+    names(out)[1:(ln)]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2))
     return(out)      
   })
   mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
[…]

### 2014-08-11 Neutral_simul.Rmd
Add KS comparison of DqSAD/SRS

@@
 
-# Load data if run only one chunk 
-load(".RData")
+require(pander)
+panderOptions('table.split.table',Inf)
 
@@
 
-```{r simul_pomac467_T100,echo=F,message=F,warning=F}
+```{r simul_pomac467_T100, eval=T,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 # Which are not different
-format(mks1[mks1$p.adjust>0.05,],digits=4)
+pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")
 
@@
 #
-den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]
+#den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]
 
@@
 
-rm(mks,psa)
+rm(mks,psa,den2,den3)
 
@@
 mks1 <- m$mPval
-mks1 <- mks1[mks1$method=="SRS",]
+mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
+pander(mks1,split.tables=Inf,caption="SRS not different")
 
-mks <- mks1[mks1$p.adjust<=0.05,]
 # NO FUNCIONA MERGE
@@
 
+mks1 <- m$mPval
+mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
+pander(mks1,caption="DqSAD not different")
+
 # Revisar R2 y validez de rangos porque para q positivos da creciente!!!!
-
-compM
-
-m$compM
 
@@
 rm(c1,c2,Dq2,Dq1)
-rm(den1,den)
+rm(den1,den,mks1,mks,mks100)
 save.image()
@@
 
-m <- compMethods_Time(bName,500,spMeta)
+m <- compMethods_Time(bName,1000,spMeta)
 
@@
 
+pander(compM,caption="Proportion of not different")
+
+mks1 <- m$mPval
+mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
+pander(mks1,caption="DqSAD not different T=1000")
+
+Dq1 <- readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt"))
+
+mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=1000")
+
 mPval <- rbind(mPval,m$mPval)
 
+mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]
+
 setwd(oldcd)
-rm(c1,c2,Dq2)
-rm(den1,den)
+rm(m,mks1)
 save.image()
@@
 
-```{r simul_pomac467_T1000, eval=FALSE,echo=F,message=F,warning=F}
+```{r simul_pomac467_T1000, eval=T,echo=F,message=F,warning=F}
+
+# Load data if run only one chunk 
+#load(".RData")
+
 setwd("Simul")
+
+if(simul)
+{
+  # Delete old simulations
+  system("rm Exp467T1000*")
 
@@
   par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
-par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T1000")
+  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T1000")
   par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
@@
 
-# I will not delete old simulations
-# system("rm Exp467*")
-
   # I have to modify pomExp.lin to make different simulations
 
-genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.01,0.1,1))
+  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
 
@@
   s
-if(simul) system(s,wait=s_wait)
+  if(simul) system(s,wait=F)
+}
 
-den1 <- meltDensityOut_NT("Exp467T1000Density.txt",nrow(ff))
+m <- compMethods_Time(bName,1000,spMeta)
 
-mks1000 <- pairKS_SAD(den1)
+compM <- rbind(compM,m$compM)
 
-# Which are not different
-format(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)],digits=4)
+pander(compM,caption="Proportion of not different")
 
-# which is the proportion of not different
-nrow(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)])/nrow(mks1000)
+mks1 <- m$mPval
+mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
+pander(mks1,caption="DqSAD not different T500")
 
-propNotDiffSAD(mks100)  
-propNotDiffSAD(mks500)  
-propNotDiffSAD(mks1000)  
+mPval <- rbind(mPval,m$mPval)
+
+setwd(oldcd)
+rm(m,mks1)
+save.image()
+
 ```
@@
 
-```{r boot_H_pomac467_T500,eval=FALSE,echo=F,message=F,warning=F}
+```{r plot_Time_pomac467,eval=T,echo=F,message=F,warning=F}
 
@@
 
-require(plyr)
-require(boot)
-require(vegan)
+# Plot different SAD with time
 
-# den <- readWideDensityOut("Exp467T100Density.txt")
-num_sp <- nrow(ff)
-# how to apply a function to each row of a data frame
-hh <- function(x) diversity(x[7:(6+num_sp)])
-H <- apply(den,1,hh)
+# Plot different Dq SRS with time
 
-#H <- lapply(den,function(x) diversity(x[7:(6+num_sp)]))
-#ldply(H)
-# data.frame(colembolos = rowSums(spe[,1:5]), acaros=rowSums(spe[,6:33]),lombrices=rowSums(spe[,34:41]))
-den[c(1,7),c("H","Richness")]
-den[c(2,4),c("H","Richness")]
+Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))
+Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfOrd.txt")))
+Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfOrd.txt")))
 
-difh <- den[c(2,4),7:(6+num_sp)]*(500*500)
-difh <- H_bss(difh)
+mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust>0.05,]
 
-print(difh)
-summary(difh)
+mergePair_plotDq(mks1[1,],Dq1,"SRS not different")
 
-ciH <-ddply(s_col,.(Ambiente),function(df) boot_shannon(df[,1:5]) )
+mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust<=0.05,]
+
+mergePair_plotDq(mks1[4,],Dq1,"SRS different")
+
+# Plot different Dq SAD with time
+
+Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
+Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfSAD.txt")))
+Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt")))
+
+mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]
+
+mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different")
+
+mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust<=0.05,]
+
+mergePair_plotDq(mks1[4,],Dq1,"DqSAD different")
+
+setwd(oldcd)
 
 ```
+
+```{r compKS_pomac467,eval=T,echo=F,message=F,warning=F}
+source("R/Neutral_fun.r")
+
+setwd("Simul")
+
+m <- compMethod_DqKS_Time(bName,100,spMeta)
+
+compM <- rbind(compM,m$compM)
+
+pander(compM,caption="Proportion of not different")
+
+mPval <- rbind(mPval,m$mPval)
+
+m <- compMethod_DqKS_Time(bName,500,spMeta) 
+compM <- rbind(compM,m$compM)
+pander(compM,caption="Proportion of not different")
+mPval <- rbind(mPval,m$mPval)
+
+m <- compMethod_DqKS_Time(bName,1000,spMeta) 
+compM <- rbind(compM,m$compM)
+pander(compM,caption="Proportion of not different")
+mPval <- rbind(mPval,m$mPval)
+
+setwd(oldcd)
+
+rm(m)
+
+compM
+
+save.image()
+
+names(mPval)
+unique(mPval$method)
+m <- with(mPval,mPval[method=="DqSADKS" & time==100,])
+propNotDiffSAD(m)
+
+```

### 2014-08-11 R/Fun_Multi_patt.r

@@ -1,0 +1,287 @@
+# Functions for Multifractal analysis 
+
+## p-model
+
+# Calculates pmodel using the C++ compiled program
+# the output is a file in "sed" format 
+#
+# I use the following to have only one parameter:
+# $p2=p3=p4=(1-p1)/3$
+#
+# fname: output file name
+# p1: p1 parameter for pmodel
+# iter: (default=9) gives the image size $lado = 2^iter$
+# rnd: how I assign p at each step S->random with reposition
+#
+
+calc_pmodel1 <- function(fname,p1,iter=9,rnd="S")
+  {
+  if(p1==0 | iter<2) stop("p1 == 0 or iter<2") 
+  if(file.exists(fname))
+    file.remove(fname)
+  p2 <- p3 <- p4 <- (1-p1)/3
+  syst.txt <- paste("./pmodel", p1,p2,p3,p4,iter,fname,rnd)
+  system(syst.txt)
+  }
+
+# Plot a sed file from pmodel using lattice
+#
+# fname: sed file with pmodel output
+# p1: parameter for title
+#
+plot_pmodel1 <- function(fname,p1)
+  {
+  require(lattice)
+  per <- read.table(fname, skip=2,header=F)
+  per <-data.matrix(per)*(2^(2*iter))
+  col.l <- colorRampPalette(c('white', 'green', 'purple', 'yellow', 'brown'))(64) 
+  levelplot(per, scales = list(draw = FALSE),xlab =NULL, ylab = NULL,col.regions=col.l,
+            useRaster=T,
+            main=list( paste("p1=",p1),cex=1))
+  }
+
+# Plot a sed file
+#
+# fname: file name
+# gname: graph title 
+# dX: range in columns to plot
+# col: vector of colors to make the color palette
+# shf: shift in the vector of colors 
+#
+plot_image <- function(fname,gname,dX=0,col=0,shf=0)
+  {
+  require(lattice)
+  require(RColorBrewer)
+  per <-data.matrix(read.table(fname, skip=2,header=F))
+  if(length(dX)>1) per <- per[,dX]
+  mp = max(per)
+  if(mp<50) {
+    mp = 50
[…]

### 2014-08-11 R/Neutral_fun.r

@@ -88,6 +88,66 @@ pairKS_SAD <- function(denl){
   return(mks)
 }
 
+# pairwise KS test for Dq of all combinations of variable rep
+# 
+#
+pairKS_DqByRep <- function(Dq,rep){
+  
+  parms <- unique(rep)
+  combo <- combn(parms,2)
+  hh <- function(x) {
+    p1 <- x[1]
+    p2 <- x[2]
+    d1 <- Dq[rep==p1]
+    d2 <- Dq[rep==p2]
+    ks <- ks.test(d1,d2)
+    out <-data.frame(p1,p2,stat=ks$statistic,p.value=ks$p.value,stringsAsFactors=F)
+    #  ln <-length(names(p1))*2
+    #  names(out)[1:(ln)]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2))
+    return(out)      
+  }
+  
+  require(plyr)
+  mks <-adply(combo,2, hh)
+  mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
+  return(mks[,2:ncol(mks)])
+}
+
+# pairwise KS test for Dq of all combinations parameters 
+# 
+# dql: data frame with Dq and in columns 1:4 of dql parameter
+# numq: number of repetitions for each parameter combination, if >1 selects one of
+# de repetitions to do the comparison.
+#
+pairKS_Dq <- function(dql,numq=1){
+  
+  require(plyr)
+
+  parms <- unique(dql[,1:4])
+  combo <- combn(nrow(parms),2)
+
+  if( numq>1){
+    dql <- ddply(dql,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate),
+    function(x) { n <- nrow(x)/35
+                  rp <- rep( 1:n,each=35)
+                  return(x[rp==sample(n,1),])}
+                  )
+  }
+  
+  mks <-adply(combo,2, function(x) {
+    p1 <- parms[x[1],]
+    p2 <- parms[x[2],]
+    d1 <- merge(dql,p1)
+    d2 <- merge(dql,p2)
+    ks <- ks.test(d1$Dq,d2$Dq)
+    out <-data.frame(p1,p2,stat=ks$statistic,p.value=ks$p.value,stringsAsFactors=F)
+    ln <-length(names(p1))*2
[…]

### 2014-08-11 R/Test_DqComp.r

@@ -1,0 +1,279 @@
+# Example for 
+# http://stackoverflow.com/questions/25085537/permute-groups-in-a-data-frame-r#
+#
+#DqStr <- "Group   q        Dq       SD.Dq
+#    1 -3.0 0.7351 0.0067
+#    1 -2.5 0.6995 0.0078
+#    1 -2.0 0.6538 0.0093
+#    2 -3.0 0.7203 0.0081
+#    2 -2.5 0.6829 0.0094
+#    2 -2.0 0.6350 0.0112"
+#    
+#    Dq1 <- read.table(textConnection(DqStr), header=TRUE)
+#    
+#    g <-unique(Dq1$q)
+#    Dq2<- data.frame()
+#    for(n in g)
+#    {
+#      Dqq <- Dq1[Dq1$q==n,]
+#      Dqq$Group <-sample(Dqq$Group)
+#      Dq2 <- rbind(Dq2,Dqq)    
+#    }
+#
+#    n <- -3
+#    print(n)
+#    Dqq <- Dq1[Dq1$q==g,]
+#    Dqq$Group <-sample(Dqq$Group)
+#    Dq2 <- rbind(Dq2,Dqq)    
+#    print(Dq2[,1:2])
+#    library(plyr)
+#    ddply(Dq1,.(q), function(x) { x$Group <- sample(x$Group)
+#                                  data.frame(x)})
+#
+#Dq1$Group <- with(Dq1, ave(Group, q, FUN = sample))
+#Dq1
+
+# Test for comparing two curves with sd
+#
+
+source("R/Test_Dq_fun.r")
+
+
+# Test with other data
+#
+setwd("Simul")
+Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
+Dq1$Time <- rep( 1:(nrow(Dq1)/35),each=35)
+Dq1$n <- 6
+
+plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
+
+Dqq <- sel_ReplaceR(Dq1,0.2,0.04,0.001,1)
+names(Dqq)
+
+
+Dqq<- Dqq[1:70,c(5:8,10)]
[…]

### 2014-08-11 R/Test_DqSAD.r

@@ -1,0 +1,52 @@
+# Two problems 
+# 
+# Why DqSAD is not strictly decreasing
+rm(list = ls())
+
+load(".RData")
+
+setwd("Simul")
+
+Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
+plotDq_ReplaceR(Dq1,0.2,0.04,0.001,"DqSAD")
+
+
+Dqq <- sel_ReplaceR(Dq1,0.2,0.04,0.001,0)
+Dqq <- sel_ReplaceR(Dq1,0.2,0.04,0.001,0.1)
+
+Dqq[12:24, c("q","Dq","SD.Dq")]
+
+# At q=6 it began to increase!!!
+
+# Make simulations without pomac and use plotDqFit
+
+par <- read.table("sim.par",quote="",stringsAsFactors=F)
+# Change base name
+
+# Number of time steps 
+par[par$V1=="nEvals",]$V2 <- 100
+# Change interval to measure Density and Diversity
+par[par$V1=="inter",]$V2 <- 100
+par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
+par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
+par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"")
+par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
+# 1:several simulations with pomac.lin parameters 
+
+
+write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
+
+
+# Run the model with the parameter ReplacementRate turned on = Hierarchical 
+# and exponential dispersal 
+#
+# Set the location of the binary xp"
+
+# make simulations
+
+s <- paste(neuBin,"sim.par","fishE.inp")
+s
+
+if(simul) system(s,wait=F)
+
+

### 2014-08-11 R/Test_Dq_fun.r

@@ -1,0 +1,148 @@
+
+
+# Modified functions from package statmod to compare curves
+#require(statmod)
+#
+
+# y1 is a matrix with columns mean,sd,n
+#
+meanAbsT <-function (y1, y2) 
+{
+  if (is.null(dim(y1)) || is.null(dim(y2))) 
+    return(NA)
+  y1 <- as.matrix(y1)
+  y2 <- as.matrix(y2)
+  if (ncol(y1) != ncol(y2)) 
+    stop("Number of time points must match")
+  m1 <- y1[,1]
+  m2 <- y2[,1]
+  v1 <- y1[,2]*y1[,2]
+  v2 <- y2[,2]*y2[,2]
+  n1 <- y1[,3]
+  n2 <- y2[,3]
+  s <- ((n1 - 1) * v1 + (n2 - 1) * v2)/(n1 + n2 - 2)
+  t.stat <- abs(m1 - m2)/sqrt(s * (1/n1 + 1/n2))
+  weighted.mean(t.stat, w = (n1 + n2 - 2)/(n1 + n2), na.rm = TRUE)
+}
+
+# Comparing two curves with SD for each point
+# using group permutations and an average T statistics
+#
+# NOT working the curves are always equal!!!
+#
+compareTwoGCurves <- function (group, y, q, nsim = 100, fun = meanAbsT) 
+{
+    group <- as.vector(group)
+    g <- unique(group)
+    if (length(g) != 2) 
+        stop("Must be exactly 2 groups")
+    stat.obs <- fun(y[group == g[1], , drop = FALSE], y[group == 
+        g[2], , drop = FALSE])
+    asbig <- 0
+    for (i in 1:nsim) {
+        pgroup <- ave(group, q, FUN = sample)
+        stat <- fun(y[pgroup == g[1], , drop = FALSE], y[pgroup == 
+            g[2], , drop = FALSE])
+        if (abs(stat) >= abs(stat.obs)) 
+            asbig <- asbig + 1
+    }
+    list(stat = stat.obs, p.value = asbig/nsim)
+}
+
+
+# Comparing two curves with SD for each point  
+# testing for (y1-y1)/(y1+y2)/2 have a normal distribution
+# or that it is equal to 0 so they come from the same population
+#
+# NOT WORK for Dq curves very similar are always different
+#
[…]

### 2014-08-13 Neutral_simul.Rmd
Add time to pvalues table

@@
 
-```{r simul_pomac467_T100, eval=T,echo=F,message=F,warning=F}
+```{r simul_pomac467_T100, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 # Which are not different
-pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")
+#pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")
 
@@
 
-rm(mks,psa,den2,den3)
+rm(mks,psa,den2)
 
@@
 
-mks1 <- m$mPval
-mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
-pander(mks1,split.tables=Inf,caption="SRS not different")
+#mks1 <- m$mPval
+#mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
+#pander(mks1,split.tables=Inf,caption="SRS not different")
 
@@
 mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
-pander(mks1,caption="DqSAD not different")
+#pander(mks1,caption="DqSAD not different")
 
@@
 setwd(oldcd)
-rm(c1,c2,Dq2,Dq1)
+rm(Dq1,den1)
 rm(den1,den,mks1,mks,mks100)
@@
 ```{r simul_pomac467_T500, eval=T,echo=F,message=F,warning=F }
+load(".RData")
 
@@
 
-m <- compMethods_Time(bName,1000,spMeta)
+m <- compMethods_Time(bName,500,spMeta)
 
@@
 mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
-pander(mks1,caption="DqSAD not different T=1000")
+pander(mks1,caption="DqSAD not different T=500")
 
-Dq1 <- readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt"))
+Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))
 
-mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=1000")
+mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=500")
 
@@
 setwd(oldcd)
-rm(m,mks1)
+rm(Dq1,m,mks1)
 save.image()
@@
 mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
-pander(mks1,caption="DqSAD not different T500")
+pander(mks1,caption="DqSAD not different T1000")
 

### 2014-08-13 R/Neutral_fun.r

@@ -323,6 +323,8 @@ compMethod_DqKS_Time <- function(bName,Time,spMeta)
   # Read all simulations and change to long format
   fname <- paste0(bName,"T",Time,"mfSAD.txt")
   Dq1 <- readNeutral_calcDq(fname)
+  # Subset for testing 
+  #
   #Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])
 
   # Testing pairwise differences
@@ -335,8 +337,8 @@ compMethod_DqKS_Time <- function(bName,Time,spMeta)
   compM <- rbind(compM, data.frame(time=Time,notdif=propNotDiffSAD(mK1),method="DqSADKS"))
 
   mKS <- rbind(mKS,mK1)
-  mkS$time <- Time
-  
+  mKS$time <- Time
+
   return(list("compM"=compM,"mPval"=mKS))
 }
 

### 2014-08-19 SP_simul.Rmd
Add generation spatial distributions with different SAD

# Multifractal analysis of multispecies spatial distributions - Spatial patterns simulations

I generate different a spatial patterns to compare SRSDq SADdq and SAD

```{r setup, eval=T }

simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
mfBin <- "~/Dropbox/cpp/SpatialAnalysis/mfsba" # /mfSBA /multiSpeciesSBA
pmBin <- "~/Dropbox/cpp/SpatialAnalysis/p-model/pmodel"

require(pander)
panderOptions('table.split.table',Inf)

```

# Banded pattern 64 species 256 side

First generate a pattern with  SAR z=1 using simply bands of species z=0.5 because I am using area as Borda-de-Agua instead of side.

```{r simul_z1, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

spa <- genBand_image(64,256)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_256.sed")

Dq1<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"
hist(Dq1$R)

spa <- matrix(sample(spa),nrow=256)
save_matrix_as_sed(spa,"band64_256rnz.sed")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_density(alpha=0.2)

plot_sed_image(spa,"Randomized 64sp")

Dq2<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "dqSAD"
Dq3<- Dq2
plotDq(Dq3,"Type")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

plotDqFit("t.band64_256rnz.sed","q.sed")

# Analizing this last it means that the scaling is broken at side 16
#

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 16 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 2 16 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD2-16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")
# copy pomExp.lin to pomac.lin
#system("cp pomExp.lin pomac.lin")

# make simulations
#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

setwd(oldcd)
```

* For SRS the positive part seems to reflect the equal SAD and the negative the spatial pattern

# Banded pattern 64 species 512 side

To see if there is any efect of side

```{r simul_z1_512, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

spa <- genBand_image(64,512)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_512.sed")

Dq1<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"

spa <- matrix(sample(spa),nrow=512)
save_matrix_as_sed(spa,"band64_512rnz.sed")

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)

plot_sed_image(spa,"Randomized 64sp")

Dq2<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "dqSAD"
Dq3<- Dq2

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

plotDqFit("t.band64_512rnz.sed","q.sed")

# Analizing this last it means that the scaling is broken at side 16
#

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 16 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD16-512"
Dq3<- rbind(Dq3,Dq2)

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 2 16 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD2-16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")

setwd(oldcd)
```

Thus DqSAD works in the range 2-16

# Now simulate an image with logseries SAD for 64 species

* Discrete bands?
* Random

```{r simul_ls_512, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

require(untb)
side <- 512
N <- side*side
S <- 64 
repeat {
  ff<-fisher.ecosystem(N=N,S=S,nmax=N)
  nsp <- nrow(ff)
  if(nsp==S) break
}
plot(ff)
N
spa <- matrix(rep(1:nsp,ff),nrow=side)
plot_sed_image(spa,"Regular Fisher  64sp")
save_matrix_as_sed(spa,"fish64_512.sed")

Dq1<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"

# 
spa <- matrix(sample(spa),nrow=512)
save_matrix_as_sed(spa,"fisher64_512rnz.sed")
plot_sed_image(spa,"Rnz Fisher  64sp",0,64,5)

Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)

# Ahora con SAD

Dq3<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 E",mfBin,T)
Dq3$Type <- "DqSAD"
#Dq3<- rbind(Dq3,Dq2)

Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)

plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)
Dq3[Dq3$R.Dq<0.6,]
setwd(oldcd)
```

### 2014-08-19 R/Neutral_fun.r

@@ -471,33 +471,99 @@ plotDqFit <- function(fname,qname)
 #  dev.off()    
 }
 
-# Compare 2 communities
+
+# Calculates theoretic Dq from pmodel
 #
-H_bss <- function (comm, R = 2000, index = "shannon") 
-{
-  if (length(rownames(comm)) > 2) 
-    stop("Please supply community of only 2 samples.\n\n")
-  require(vegan)
-  RT <- rowSums(comm)
-  DF <- sum(rowSums(comm > 0)) - 2
-  CT <- colSums(comm)
-  Hx <- as.numeric(diversity(comm, index = index))[1]
-  Hy <- as.numeric(diversity(comm, index = index))[2]
-  Ho <- abs(Hx - Hy)
-  Hb <- vector(mode = "numeric", length = R)
-  for (i in 1:R) {
-    Mb <- r2dtable(1, RT, CT)
-    Mb <- as.matrix(Mb[[1]])
-    Hd <- as.numeric(abs(diversity(Mb, index = index)[1] - 
-                           diversity(Mb, index = index)[2]))
-    Hb[i] <- Hd
+calcDqTeor <- function(q,p1) {
+  if( q==1)
+    q <- q+1e-10
+  p2 <- p3 <- p4 <- (1-p1)/3
+  f1 <- p1/(p1+p2+p3+p4)
+  f2 <- p2/(p1+p2+p3+p4)
+  f3 <- p3/(p1+p2+p3+p4)
+  f4 <- p4/(p1+p2+p3+p4)
+  dq <- log2(f1^q+f2^q+f3^q+f4^q)/(1-q)
+  return(dq)
   }
-  Q <- quantile(Hb, c(0.025, 0.975))
-  Z <- abs((Ho - mean(Hb))/sd(Hb))
-  P <- mean(abs(Hb) > Ho)
-  Pz <- pt(Z, df = DF, lower.tail = FALSE) * 2
-  result <- list(H.orig = c(Hx, Hy), statistic = Ho, z.score = Z, 
-                 CI = Q, p.sim = P, p.z = Pz, df = DF, Index = index)
-  class(result) = "Hbss"
-  return(result)
+
+
+# Save a matrix as a sed file with type BI (floating point)
+#
+save_matrix_as_sed <- function(mat,fname)
+{
+  header <- paste(nrow(mat),ncol(mat),"BI")
+  write.table(header,file=fname,row.names=F,col.names=F,quote=F)
[…]

### 2014-08-19 R/Test_Dq_fun.r

@@ -1,7 +1,8 @@
+# Compare Dq without repetition the most interesting are 
+# compareTwoCurvesT and KS.test
 
 
 # Modified functions from package statmod to compare curves
-#require(statmod)
 #
 
 # y1 is a matrix with columns mean,sd,n

### 2014-08-21 SP_simul.Rmd
Add local multifractal approach to introduction

@@
 
-spa <- genBand_image(64,256)
+spa <- genUniformSAD_image(64,256)
 plot_sed_image(spa,"Banded 64sp")
@@
 
-spa <- genBand_image(64,512)
+spa <- genUniformSAD_image(64,512)
 plot_sed_image(spa,"Banded 64sp")
@@
 
-require(untb)
-side <- 512
-N <- side*side
-S <- 64 
-repeat {
-  ff<-fisher.ecosystem(N=N,S=S,nmax=N)
-  nsp <- nrow(ff)
-  if(nsp==S) break
-}
-plot(ff)
-N
-spa <- matrix(rep(1:nsp,ff),nrow=side)
-plot_sed_image(spa,"Regular Fisher  64sp")
+# Generate an image following a logseries distribution with 64 sp 
+# an regular spatial distribution
+spa <- genFisherSAD_image(64,512)
+
+plot_sed_image(spa,"Regular Fisher  64sp",0,64,10)
 save_matrix_as_sed(spa,"fish64_512.sed")

### 2014-08-21 R/Neutral_fun.r

@@ -561,9 +561,26 @@ plot_sed_image <- function(fname,gname,dX=0,col=0,shf=0)
 
 # Generate a banded image with nSp species and side = side
 #
-genBand_image <- function(nSp,side)
+genUniformSAD_image <- function(nSp,side)
 {
   if( side %% nSp != 0 )
     stop("Number of species [nSp] must divide [side]")
   matrix(rep(1:nSp,each=side*side/nSp),nrow=side)
+}
+
+# Generate a regular image with Fisherian SAD with nsp species and side = side
+# Requires untb package
+#
+genFisherSAD_image <- function(nsp,side)
+{
+  require(untb)
+  N <- side*side
+  repeat {
+    ff<-fisher.ecosystem(N=N,S=nsp,nmax=N)
+    if(nsp==nrow(ff)) {
+      m <- matrix(rep(1:nsp,ff),nrow=side)
+      if(ncol(m)>=side) break
+    }
+  }
+  return(m)
 }

### 2014-08-27 SP_simul.Rmd
add spatial pattern simulations

@@
 ```{r setup, eval=T }
+load(".RData")
 
@@
 mfBin <- "~/Dropbox/cpp/SpatialAnalysis/mfsba" # /mfSBA /multiSpeciesSBA
-pmBin <- "~/Dropbox/cpp/SpatialAnalysis/p-model/pmodel"
 
@@
 
-# Banded pattern 64 species 256 side
+# Banded pattern of species with uniform  SAD 256 side
 
@@
 
-spa <- genUniformSAD_image(64,256)
-plot_sed_image(spa,"Banded 64sp")
-save_matrix_as_sed(spa,"band64_256.sed")
+DqF <- compMethods_UniformSAD(8,256)
 
-Dq1<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 S",mfBin,T)
-Dq1$Type <- "SRS"
-hist(Dq1$R)
+DqF <- rbind(DqF,compMethods_UniformSAD(64,256))
 
-spa <- matrix(sample(spa),nrow=256)
-save_matrix_as_sed(spa,"band64_256rnz.sed")
-
-Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 S",mfBin,T)
-Dq2$Type <- "rnzSRS"
-Dq1<- rbind(Dq1,Dq2)
-plotDq(Dq1,"Type")
-
-ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_density(alpha=0.2)
-
-plot_sed_image(spa,"Randomized 64sp")
-
-Dq2<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 E",mfBin,T)
-Dq2$Type <- "dqSAD"
-Dq3<- Dq2
-plotDq(Dq3,"Type")
-
-Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 E",mfBin,T)
-Dq2$Type <- "rnzDqSAD"
-Dq3<- rbind(Dq3,Dq2)
-plotDq(Dq3,"Type")
-
-plotDqFit("t.band64_256rnz.sed","q.sed")
+DqF <- rbind(DqF,compMethods_UniformSAD(256,256))
 
@@
 #  
+#Dq2<- calcDq_multiSBA(fname1,"q.sed 16 1024 20 E",mfBin,T)
+#Dq2$Type <- "rnzDqSAD16-512"
+#Dq3<- rbind(Dq3,Dq2)
+#
+##Dq2<- calcDq_multiSBA(fname1,"q.sed 2 16 20 E",mfBin,T)
+#Dq2$Type <- "rnzDqSAD2-16"
+#Dq3<- rbind(Dq3,Dq2)
+#plotDq(Dq3,"Type")
 
-Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 16 512 20 E",mfBin,T)
-Dq2$Type <- "rnzDqSAD16"
-Dq3<- rbind(Dq3,Dq2)
-plotDq(Dq3,"Type")
-
-Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 2 16 20 E",mfBin,T)
-Dq2$Type <- "rnzDqSAD2-16"
-Dq3<- rbind(Dq3,Dq2)
-plotDq(Dq3,"Type")
-
-ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")
-# copy pomExp.lin to pomac.lin
-#system("cp pomExp.lin pomac.lin")
-
-# make simulations
-#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)
-
+pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")
 setwd(oldcd)
@@
 
-spa <- genUniformSAD_image(64,512)
-plot_sed_image(spa,"Banded 64sp")
-save_matrix_as_sed(spa,"band64_512.sed")
-
-Dq1<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 S",mfBin,T)
-Dq1$Type <- "SRS"
-
-spa <- matrix(sample(spa),nrow=512)
-save_matrix_as_sed(spa,"band64_512rnz.sed")
-
-Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
-Dq2$Type <- "rnzSRS"
-Dq1<- rbind(Dq1,Dq2)
-plotDq(Dq1,"Type")
-
-ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)
-
-plot_sed_image(spa,"Randomized 64sp")
-
-Dq2<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 E",mfBin,T)
-Dq2$Type <- "dqSAD"
-Dq3<- Dq2
-
-Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
-Dq2$Type <- "rnzDqSAD"
-Dq3<- rbind(Dq3,Dq2)
-plotDq(Dq3,"Type")
-
-plotDqFit("t.band64_512rnz.sed","q.sed")
-
-# Analizing this last it means that the scaling is broken at side 16
-#
-
-Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 16 512 20 E",mfBin,T)
-Dq2$Type <- "rnzDqSAD16-512"
-Dq3<- rbind(Dq3,Dq2)
-
-Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 2 16 20 E",mfBin,T)
-Dq2$Type <- "rnzDqSAD2-16"
-Dq3<- rbind(Dq3,Dq2)
-plotDq(Dq3,"Type")
-
-ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")
+DqF <- rbind(DqF,compMethods_UniformSAD(64,512))
 
@@
 
-Thus DqSAD works in the range 2-16
+Thus DqSAD works in the range 2-8 2-16 2-32 depending on the number of species
 
-# Now simulate an image with logseries SAD for 64 species
+# Now simulate an image with logseries SAD with 8, 64 & 256 species
 
-* Discrete bands?
-* Random
+# Test logseries SAD side = 256
 
-```{r simul_ls_512, eval=T,echo=F,message=F,warning=F}
+```{r simul_ls_256, eval=T,echo=F,message=F,warning=F}
 setwd("Simul")
 
-# Generate an image following a logseries distribution with 64 sp 
-# an regular spatial distribution
-spa <- genFisherSAD_image(64,512)
+DqF <- rbind(DqF,compMethods_FisherSAD(8,256))
 
-plot_sed_image(spa,"Regular Fisher  64sp",0,64,10)
-save_matrix_as_sed(spa,"fish64_512.sed")
+DqF <- rbind(DqF,compMethods_FisherSAD(64,256))
 
-Dq1<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 S",mfBin,T)
-Dq1$Type <- "SRS"
+DqF <- rbind(DqF,compMethods_FisherSAD(256,256))
 
-# 
-spa <- matrix(sample(spa),nrow=512)
-save_matrix_as_sed(spa,"fisher64_512rnz.sed")
-plot_sed_image(spa,"Rnz Fisher  64sp",0,64,5)
+setwd(oldcd)
 
-Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
-Dq2$Type <- "rnzSRS"
-Dq1<- rbind(Dq1,Dq2)
-plotDq(Dq1,"Type")
+```
 
-ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)
+# Test logseries SAD side=512
 
-# Ahora con SAD
+```{r simul_ls_512b, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
 
-Dq3<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 E",mfBin,T)
-Dq3$Type <- "DqSAD"
-#Dq3<- rbind(Dq3,Dq2)
+DqF <- rbind(DqF,compMethods_FisherSAD(8,512,F))
 
-Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
-Dq2$Type <- "rnzDqSAD"
-Dq3<- rbind(Dq3,Dq2)
+DqF <- rbind(DqF,compMethods_FisherSAD(64,512,F))
 
-plotDq(Dq3,"Type")
+DqF <- rbind(DqF,compMethods_FisherSAD(256,512,F))
 
-ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)
-Dq3[Dq3$R.Dq<0.6,]
 setwd(oldcd)
+rm(Dq1,Dq2,spa)
+
 ```
+
+# Simulate with logseries and the neutral model
+
+```{r simul_neu_256, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
+
+DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T))
+
+DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T))
+
+DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T))
+setwd(oldcd)
+rm(nsp,side,spa)
+save.image()
+
+```

### 2014-08-27 R/Neutral_fun.r

@@ -554,9 +554,9 @@ plot_sed_image <- function(fname,gname,dX=0,col=0,shf=0)
   if(length(col)==1) col.l <- colorRampPalette(c('white', 'green', 'purple', 'yellow', 'brown'))(mp) 
   else col.l <- colorRampPalette(col)(mp) 
   if( shf>0) col.l = col.l[shf:mp]
-  levelplot(per, scales = list(draw = FALSE),xlab =NULL, ylab = NULL,col.regions=col.l,
+  print(levelplot(per, scales = list(draw = FALSE),xlab =NULL, ylab = NULL,col.regions=col.l,
             useRaster=T,at=seqat,
-            main=list( gname,cex=1))
+            main=list( gname,cex=1)))
   }
 
 # Generate a banded image with nSp species and side = side
@@ -570,6 +570,7 @@ genUniformSAD_image <- function(nSp,side)
 
 # Generate a regular image with Fisherian SAD with nsp species and side = side
 # Requires untb package
+# Returns a matrix representing the spatial distribution and a vector with proportions of each sp
 #
 genFisherSAD_image <- function(nsp,side)
 {
@@ -582,5 +583,225 @@ genFisherSAD_image <- function(nsp,side)
       if(ncol(m)>=side) break
     }
   }
-  return(m)
+ 
+  prob <- ff/sum(ff)
+  return(list("m"=m,"prob"=prob))
+}
+
+  
+# Generate a Fisher logseries SAD with a regular spatial distribution
+# randomize it and calculates SRS and DqSAD multifractal estimations
+#
+compMethods_FisherSAD <- function(nsp,side,gen=T) {
+
+  if(!exists("mfBin")) stop("Variable mfBin not set (mfSBA binary)")
+
+  fname <- paste0("fisher",nsp,"_",side,".sed")
+  if(file.exists(fname) & gen==F)
+  {
+    spa <- read_sed(fname)
+  } else {
+    spa <- genFisherSAD_image(nsp,side)$m
[…]

### 2014-09-15 SP_simul.Rmd
Add Anderson-Darling test and power calculation

@@
 panderOptions('table.split.table',Inf)
+options("scipen"=100, "digits"=4)
 
@@
 
-```{r simul_z1, eval=T,echo=F,message=F,warning=F}
+```{r simul_z1, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 
-```{r simul_z1_512, eval=T,echo=F,message=F,warning=F}
+```{r simul_z1_512, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 
-```{r simul_ls_256, eval=T,echo=F,message=F,warning=F}
+```{r simul_ls_256, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 
-```{r simul_ls_512b, eval=T,echo=F,message=F,warning=F}
+```{r simul_ls_512b, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
 
-DqF <- rbind(DqF,compMethods_FisherSAD(8,512,F))
+DqF <- rbind(DqF,compMethods_FisherSAD(8,512))
 
-DqF <- rbind(DqF,compMethods_FisherSAD(64,512,F))
+DqF <- rbind(DqF,compMethods_FisherSAD(64,512))
 
-DqF <- rbind(DqF,compMethods_FisherSAD(256,512,F))
+DqF <- rbind(DqF,compMethods_FisherSAD(256,512))
 
@@
 
-```{r simul_neu_256, eval=T,echo=F,message=F,warning=F}
+```{r simul_neu_256, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
 
-DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T))
+DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T)$Dq)
 
-DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T))
+DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T)$Dq)
 
-DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T))
+DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T)$Dq)
 setwd(oldcd)
 rm(nsp,side,spa)
+
+save.image()
+```
+
+# Test if at time 500 the model is at steady state
+
+```{r test_neutralTime, eval=F,echo=F,message=F,warning=F}
+setwd("Simul")
+
+simul_NeutralPlotTime(8,256,T,500,"L")
+simul_NeutralPlotTime(64,256,T,500,"L")
+simul_NeutralPlotTime(256,256,T,500,"L")
+
+simul_NeutralPlotTime(8,512,T,500,"L")
+simul_NeutralPlotTime(64,512,T,500,"L")
+simul_NeutralPlotTime(256,512,T,500,"L")
+
+simul_NeutralPlotTime(8,512,T,500,"U")
+simul_NeutralPlotTime(64,512,T,500,"U")
+simul_NeutralPlotTime(256,512,T,500,"U")
+
+setwd(oldcd)
+
+```
+
+Compare Neutral and Logseries using 10 simulations with KS and permutations with side =256
+
+```{r test_SAD256, eval=F,echo=F,message=F,warning=F}
+setwd("Simul")
+
+cc <- comp_NeutralLogseries(8,256)
+compGC <-splitFields_comp(cc$comp)
+DqGC   <-cc$Dq
+SadGC  <-cc$SAD
+
+cc <- comp_NeutralLogseries(64,256)
+compGC <-rbind(compGC,splitFields_comp(cc$comp))
+DqGC   <-rbind(DqGC  ,cc$Dq)
+SadGC  <-rbind(SadGC ,cc$SAD)
+
+cc <- comp_NeutralLogseries(256,256)
+compGC <-rbind(compGC,splitFields_comp(cc$comp))
+DqGC   <-rbind(DqGC  ,cc$Dq)
+SadGC  <-rbind(SadGC ,cc$SAD)
+
+setwd(oldcd)
 save.image()
@@
 ```
+
+Compare Neutral and Logseries using 10 simulations with KS and permutations with side =512
+
+```{r test_SAD512, eval=F,echo=F,message=F,warning=F}
+setwd("Simul")
+
+cc <- comp_NeutralLogseries(8,512)
+compGC <-rbind(compGC,splitFields_comp(cc$comp))
+DqGC   <-rbind(DqGC  ,cc$Dq)
+SadGC  <-rbind(SadGC ,cc$SAD)
+
+cc <- comp_NeutralLogseries(64,512)
+compGC <-rbind(compGC,splitFields_comp(cc$comp))
+DqGC   <-rbind(DqGC  ,cc$Dq)
+SadGC  <-rbind(SadGC ,cc$SAD)
+
+cc <- comp_NeutralLogseries(256,512)
+compGC <-rbind(compGC,splitFields_comp(cc$comp))
+DqGC   <-rbind(DqGC  ,cc$Dq)
+SadGC  <-rbind(SadGC ,cc$SAD)
+
+# Simulations with side=512 not done
+#
+#compSP <- rbind(compSP,compKS_NeutralLogseries(8,512))
+#compSP <- rbind(compSP,compKS_NeutralLogseries(64,512))
+#compSP <- rbind(compSP,compKS_NeutralLogseries(256,512))
+rm(cc)
+
+setwd(oldcd)
+save.image()
+```
+
+Compare Neutral and Uniform 10 simulations with KS and permutations with side 256 and 512
+
+```{r test_SAD256U, eval=F,echo=F,message=F,warning=F}
+setwd("Simul")
+# Agregar una parametro meta (metacommunity) a variables para identificar
+# Agregar comparacion de SAD uniforme con Neutral uniforme por KS
+#
+cc <- comp_NeutralUniform(8,256)
+compUN <-splitFields_comp(cc$comp)
+DqUN   <-cc$Dq
+SadUN  <-cc$SAD
+
+cc <- comp_NeutralUniform(64,256)
+compUN <-rbind(compUN,splitFields_comp(cc$comp))
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(256,256)
+compUN <-rbind(compUN,splitFields_comp(cc$comp))
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(8,512)
+compUN <-rbind(compUN,splitFields_comp(cc$comp))
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(64,512)
+compUN <-rbind(compUN,splitFields_comp(cc$comp))
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(256,512)
+compUN <-rbind(compUN,splitFields_comp(cc$comp))
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+rm(cc)
+
+setwd(oldcd)
+# Delete duplicated fields Side2 NmSp2
+compGC <- compGC[,-(6:7)]
+compUN <- compUN[,-(6:7)]
+# merge
+
+compT <- rbind(compGC,compUN)
+# Reorganize 
+compT <- compT[,c(2,3,1,4:10)]
+rm(compGC,compUN)
+
+# merge SAD
+SadT <- rbind(SadGC,SadUN)
+rm(SadGC,SadUN)
+
+# merge Dq
+
+DqT <- rbind(DqGC,DqUN)
+rm(DqGC,DqUN)
+
+save.image()
+
+```
+
+```{r power_adtest, eval=T,echo=F,message=F,warning=F}
+
+power <- calcPower_AD(DqT,SadT,8,256)
+power <- rbind(power,calcPower_AD(DqT,SadT,64,256))
+power <- rbind(power,calcPower_AD(DqT,SadT,256,256))
+
+power <- rbind(power,calcPower_AD(DqT,SadT,8,512))
+power <- rbind(power,calcPower_AD(DqT,SadT,64,512))
+power <- rbind(power,calcPower_AD(DqT,SadT,256,512))
+
+# Cada 12 cambia rep(8,12)
+nsp <- c(rep(8,12),rep(64,12),rep(256,12),rep(8,12),rep(64,12),rep(256,12))
+save.image()
+```

### 2014-09-15 R/Neutral_fun.r

@@ -63,6 +63,21 @@ calcRankSAD  <- function(den)
   ddply(den, .(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate),hh )
 }
 
+# Calculate Ranks for every parameter combination in columns cols, for variable vv, using data.frame den 
+# to use ggplot2  
+#
+calcRankSAD_by  <- function(den,vv,cols)
+{
+  require(plyr)
+  hh <- function(x) { 
+  x1 <- x[x[[vv]]>0,]
+  x1$parms <- paste(unique(x[,cols]),collapse="_")
+  x1$Rank <- nrow(x1) - rank(x1[[vv]]) +1
+  return(x1)
+  }
+  ddply(den, cols,hh )
+}
+
 # pairwise KS test for all combinations of parameters in denl= density in long format
 # parameters are in columns 1:4
 # 
@@ -87,6 +102,78 @@ pairKS_SAD <- function(denl){
   mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
   return(mks)
 }
+
+# pairwise KS test for all combinations of parameters in variable parms 
+# vv: name of the variable where density or proportion is
+# denl: data.frame with all data
+#
+pairwiseKS_SAD <- function(denl,vv,parms){
+  
+  parms <- unique(parms)
+  combo <- combn(nrow(parms),2)
+  
+  require(plyr)
+  mks <-adply(combo,2, function(x) {
+    p1 <- parms[x[1],]
+    p2 <- parms[x[2],]
+    d1 <- merge(denl,p1)
+    d2 <- merge(denl,p2)
+    ks <- ks.test(d1[,vv],d2[,vv])
+    out <-data.frame(p1,p2,stat=ks$statistic,p.value=ks$p.value,stringsAsFactors=F)
+    ln <-length(names(p1))*2
+    names(out)[1:(ln)]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2))
+    return(out)      
+  })
+  mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
+  return(mks)
+}
+
[…]

### 2014-09-18 Neutral_simulPow.Rmd
Add functions to test neutral Dq with Anderson-Darling and calculate power

--- 2014-08-13 Neutral_simul.Rmd
@@
 panderOptions('table.split.table',Inf)
-
+options("scipen"=100, "digits"=4)
 ```
 
-This is run only once to generate the metacommunity then set eval=FALSE and generate
-a set of parameter files to modify
+## Simulations with different parameters using pomac and at Time=100
 
-```{r generateLogSerParms, eval=FALSE,echo=F,message=F,warning=F}
-# Generate a SAD for metacommunity using a logseries 
-#
-# side is the side of the simulation lattice
-#
-# N is the total number of individuals 
-#
-# S is the species richness 
-#
+Now I will simulate the model to Time=500 with a full set of parameters 
+Replacement = 0,0.001,0.01,0.1,1 and ten repetitions
 
-require(untb)
-side <- 500
-N <- side*side
-S <- 450 
-ff<-fisher.ecosystem(N=N,S=S,nmax=N)
-plot(ff)
-nrow(ff)
-ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
-ff$prob <- ff$FreqT/sum(ff$FreqT)
+```{r simul_LogSerParms, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
 
-spMeta <- nrow(ff)
+time <- 500
+meta <- "L"
+side <- 256
+nsp  <- 64
+
+if(toupper(meta)=="L") {
+  prob <- genFisherSAD(nsp,side)
+  neuParm <- "fishE"
+  bname <- paste0("neuFish",nsp)
+  sadName <- "Neutral"
+} else {
+  prob <- rep(1/nsp,nsp)  
+  neuParm <- "unifE"
+  bname <- paste0("neuUnif",nsp)
+  sadName <- "NeuUnif"
+}
 
@@
 # Replacement  = 0 - 1
+spMeta <- length(prob)
+# First generate de inp file with species and metacommunity parameters 
+genNeutralParms(neuParm,side,prob,1,0.2,0.04,0.0001)
 
-setwd("Simul")
-#undebug(genNeutralParms)
-# First generate de inp file with species and metacommunity parameters 
-genNeutralParms("fishE",500,ff$prob,1,0.2,0.04,0.001)
+# Delete old simulations
+system(paste0("rm ",bname,"*.txt"))
+
+# we need the par file with the simulations parameters
+par <- read.table("sim.par",quote="",stringsAsFactors=F)
+
+# Number of time steps 
+par[par$V1=="nEvals",]$V2 <- time
+par[par$V1=="inter",]$V2 <- time # interval to measure Density and Diversity
+par[par$V1=="init",]$V2 <- time  # Firs time of measurement = interval
+par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
+par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
+par[par$V1=="baseName",]$V2 <- paste0(bName ,"T", time ) 
+par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
+                              # 1:several simulations with pomac.lin parameters
+
+write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
 
@@
 
-genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,1))
+genPomacParms("pomExp",1,c(0.2),c(0.04),c(0.0001),c(0,0.001),3)
 
-# we need the par file with the simulations parameters
-
-par <- read.table("sim.par",quote="",stringsAsFactors=F)
-# Change base name
-
-# Number of time steps 
-par[par$V1=="nEvals",]$V2 <- 100
-# Change interval to measure Density and Diversity
-par[par$V1=="inter",]$V2 <- 10
-par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
-par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
-par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
-par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
-                              # 1:several simulations with pomac.lin parameters
-
-write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
-
-# Run the model with the parameter ReplacementRate turned on = Hierarchical 
-# and exponential dispersal 
-#
-# Set the location of the binary 
-#neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"
-
-# copy pomExp.lin to pomac.lin
-#system("cp pomExp.lin pomac.lin")
-
-# make simulations
-#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)
-
-```
-
-## Simulations with different parameters using pomac and at Time=100
-
-Now I will simulate the model to Time=100 with a full set of parameters 
-Replacement = 0,0.001,0.01,0.1,1 and ten repetitions
-
-```{r simul_pomac467_T100, eval=F,echo=F,message=F,warning=F}
-setwd("Simul")
-
-spMeta <- 467 # nrow(ff) number of species in the generated metacommunity
-
-bName <- paste0("Exp", spMeta) # Base name based in the dispersal "Exp" and number of species in metacommunity "467"
-
-if(simul) {
-
-  # Delete old simulations
-  system("rm Exp467T100*")
-
-  # read par file with simulations parameters
-
-  par <- read.table("sim.par",quote="",stringsAsFactors=F)
-
-  # Number of time steps 
-  par[par$V1=="nEvals",]$V2 <- 100
-
-  par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
-  par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
-  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
-  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
-  par[par$V1=="baseName",]$V2 <- paste0(bName ,"T100") # Time = 100 
-  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
-                                # 1:several simulations with pomac.lin parameters
-
-  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
-
-  # I have to modify pomExp.lin to make different simulations
-  #undebug(genPomacParms)
-
-  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
+#genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
 
@@
 
-  system(paste(neuBin,"sim.par","fishE.inp"))
-}
+system(paste(neuBin,"sim.par",paste0(neuParm,".inp")))
 
-m <- compMethods_Time(bName,100,spMeta)
+# Desde aca function compNeutral_Time  
+#
+fname <- paste0(bname,"T",time,"Density.txt")
 
-mks1 <- m$mPval
-mks1 <- mks1[mks1$method=="SAD",]
+den1 <- meltDensityOut_NT(fname,spMeta)
 
-# Which are not different
-#pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")
-
-den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)
-# Select a subset to test the procedure !
+# Test pairwise diferences in SAD
 #
-#den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]
-
-require(plyr)
-den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))
+mKS <- pairwiseAD_Dif(den1,"value",den1[,1:5])
 
@@
 #
+mks <- mKS[mKS$p.value>0.05,2:ncol(mKS)]
+psa <- mergePairSadRank(mks[1,],den1,"value",1:5)
+psa <- rbind(psa,mergePairSadRank(mks[nrow(mks),],den1,"value",1:5))
+require(ggplot2)
+(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line() + ggtitle("SAD not dif"))
 
-mks <- mks1[mks1$p.adjust>0.05,]
-psa <- mergePairSAD(mks[1,],den2)
+# Build data.frame with proportions
+#
+#compM <- data.frame(time=Time,notdif=propNotDiffSAD(mKS),method="SAD")
 
-require(ggplot2)
+######################### HAY QUE VER DE LOS QUE SON IGUALES si dan distintos con DqSAD /SRS
+qNumber <- 35
+fname <- paste0(bname,"T",time,"mfOrd.txt")
+Dq1 <- readNeutral_calcDq(fname)
+Dq1$rep <- rep( 1:(nrow(Dq1)/qNumber),each=qNumber)
 
-(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line() + ggtitle("SAD not dif"))
-
-# Plot the first pair different 
-#
-mks <- mks1[mks1$p.adjust<=0.05,]
-psa <- mergePairSAD(mks[1,],den2)
-(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line()
- + ggtitle("SAD different"))
-
-# Calculate ranks for each parameter combination with different ReplacementRate
-#
-den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
-den3 <- calcRankSAD(den2)
-
-(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
-
-rm(mks,psa,den2)
+mKS1 <- pairwiseAD_Dif(Dq1,"Dq",den1[,c(1:4,10])   #### TEST THIS!
 
 #
-# Now check differences using multifractals mfSAD o mfSRS
-#
-
-# Leer Dq SRS
-#
-Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))
-
-# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
-#
-
-plotDq_ReplaceR(Dq1,0.2,0.04,0.0001, "SRS")
-plotDq_ReplaceR(Dq1,0.2,0.4,0.001, "SRS")
-plotDq_ReplaceR(Dq1,0.2,0.04,0.001, "SRS")
-
-#mks1 <- m$mPval
-#mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
-#pander(mks1,split.tables=Inf,caption="SRS not different")
-
-# NO FUNCIONA MERGE
-#psa <- mergePairSAD(mks[1,],Dq1)
-
-#
-#
-# Leer Dq SAD
-#
-Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
-
-plotDq_ReplaceR(Dq1,0.2,0.04,0.001,"DqSAD")
-plotDq_ReplaceR(Dq1,0.2,0.4,0.001,"DqSAD")
-plotDq_ReplaceR(Dq1,0.2,0.04,0.0001,"DqSAD")
-
-mks1 <- m$mPval
-mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
-#pander(mks1,caption="DqSAD not different")
-
-# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!
-
-compM <- m$compM
-
-mPval <- m$mPval
 

### 2014-09-18 SP_simul.Rmd
Add functions to test neutral Dq with Anderson-Darling and calculate power

--- 2014-08-27 SP_simul.Rmd
@@
 
-```{r simul_neu_256, eval=T,echo=F,message=F,warning=F}
+```{r simul_neu_256, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
 
-DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T))
+DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T)$Dq)
 
-DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T))
+DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T)$Dq)
 
-DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T))
+DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T)$Dq)
 setwd(oldcd)
 rm(nsp,side,spa)
+
+save.image()
+```
+
+# Test if at time 500 the model is at steady state
+
+```{r test_neutralTime, eval=F,echo=F,message=F,warning=F}
+setwd("Simul")
+
+simul_NeutralPlotTime(8,256,T,500,"L")
+simul_NeutralPlotTime(64,256,T,500,"L")
+simul_NeutralPlotTime(256,256,T,500,"L")
+
+simul_NeutralPlotTime(8,512,T,500,"L")
+simul_NeutralPlotTime(64,512,T,500,"L")
+simul_NeutralPlotTime(256,512,T,500,"L")
+
+simul_NeutralPlotTime(8,512,T,500,"U")
+simul_NeutralPlotTime(64,512,T,500,"U")
+simul_NeutralPlotTime(256,512,T,500,"U")
+
+setwd(oldcd)
+
+```
+
+Perform Neutral with metaccomunity uniform and Uniform, 10 simulations with side 256 and 512
+
+```{r test_SAD256U, eval=F,echo=F,message=F,warning=F}
+setwd("Simul")
+
+cc <- comp_NeutralUniform(8,256)
+DqUN   <-cc$Dq
+SadUN  <-cc$SAD
+
+cc <- comp_NeutralUniform(64,256)
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(256,256)
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(8,512)
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(64,512)
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+cc <- comp_NeutralUniform(256,512)
+DqUN   <-rbind(DqUN  ,cc$Dq)
+SadUN  <-rbind(SadUN ,cc$SAD)
+
+rm(cc)
+
+# merge SAD
+SadT <- rbind(SadGC,SadUN)
+rm(SadGC,SadUN)
+
+# merge Dq
+
+DqT <- rbind(DqGC,DqUN)
+rm(DqGC,DqUN)
+
+setwd(oldcd)
 save.image()
 
+#compT <- rbind(compT,compUN)
+#SadT <- rbind(SadT,SadUN)
+#DqT  <- rbind(DqT,DqUN)
+
 ```
+
+Perform Neutral with metacommunity logseries and Logseries, 10 simulations with side =256/512
+
+```{r test_SAD256, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
+
+cc <- comp_NeutralLogseries(8,256)
+DqT   <-rbind(DqT,cc$Dq)
+SadT  <-rbind(SadT ,cc$SAD)
+
+cc <- comp_NeutralLogseries(64,256)
+DqT   <-rbind(DqT  ,cc$Dq)
+SadT  <-rbind(SadT ,cc$SAD)
+
+cc <- comp_NeutralLogseries(256,256)
+DqT   <-rbind(DqT  ,cc$Dq)
+SadT  <-rbind(SadT ,cc$SAD)
+
+cc <- comp_NeutralLogseries(8,512)
+DqT   <-rbind(DqT  ,cc$Dq)
+SadT  <-rbind(SadT ,cc$SAD)
+
+cc <- comp_NeutralLogseries(64,512)
+DqT   <-rbind(DqT  ,cc$Dq)
+SadT  <-rbind(SadT ,cc$SAD)
+
+cc <- comp_NeutralLogseries(256,512)
+DqT   <-rbind(DqT  ,cc$Dq)
+SadT  <-rbind(SadT ,cc$SAD)
+
+# Simulations with side=512 not done
+#
+#compSP <- rbind(compSP,compKS_NeutralLogseries(8,512))
+#compSP <- rbind(compSP,compKS_NeutralLogseries(64,512))
+#compSP <- rbind(compSP,compKS_NeutralLogseries(256,512))
+rm(cc)
+
+setwd(oldcd)
+save.image()
+```
+
+Now check if all simulations are done a make power calculations
+
+```{r power_adtest, eval=T,echo=F,message=F,warning=F}
+# Check all simulations are present
+require(plyr)
+ddply(SadT,3:6,summarize, max(rep))
+ddply(DqT,5:8,summarize, max(rep),min(rep))
+powad <- data.frame()
+
+powad <- rbind(powad,calcPower_AD(DqT,SadT,8,256))
+powad <- rbind(powad,calcPower_AD(DqT,SadT,64,256))
+powad <- rbind(powad,calcPower_AD(DqT,SadT,256,256))
+
+powad <- rbind(powad,calcPower_AD(DqT,SadT,8,512))
+powad <- rbind(powad,calcPower_AD(DqT,SadT,64,512))
+powad <- rbind(powad,calcPower_AD(DqT,SadT,256,512))
+
+save.image()
+```
+
+Make plots of power and type I error
+
+```{r power_adtest, eval=T,echo=F,message=F,warning=F}
+
+plot_DqPowerTypeI <- function(pp,tit){
+  require(ggplot2)
+  pp$Type2[pp$Type2=="SRS"] <- "DqSRS" 
+  pp$Type2[grepl("rnz",pp$Type2)] <- "Power"
+  pp$Type2[grepl("Dq",pp$Type2)] <- "Type I"
+
+  g <-ggplot(pp, aes(factor(NumSp), power, colour = as.factor(Side))) +
+    geom_point(aes(shape=as.factor(Side)),size=4) + ggtitle(tit) + theme_bw() +
+    facet_grid(Type1~Type2) + scale_colour_discrete(name="Size") +
+    scale_shape_discrete(name="Size") + scale_x_discrete(name="Number of Species")
+  print(g)
+}
+#powad <- power
+p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Uniform" ,])
+plot_DqPowerTypeI(p1,"Uniform")
+
+p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="NeuUnif" ,])
+plot_DqPowerTypeI(p1,"NeuUnif")
+
+p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Logseries" ,])
+plot_DqPowerTypeI(p1,"Logseries")
+
+p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Neutral" ,])
+plot_DqPowerTypeI(p1,"Neutral")
+
+```

### 2014-09-18 R/Neutral_fun.r

@@ -49,6 +49,26 @@ mergePairSAD <- function(eks, den1){
   
 }
 
+# Merge data from 2 simulations 
+# 
+# eks: 1 row data.frame with 2 sets of parms for which ks.test was done (fixed TIME)
+# den1: full data in long format
+#
+mergePairSadRank <- function(eks, den1,vv,cols=1:4){
+  # eks <- mks[61,]
+  
+  den2 <-merge(den1,eks,by.x=cols,by.y=cols)[,1:(length(cols)+2)]
+  den2$parms <-paste(eks[,cols],collapse="_")
+  den2$Rank <- nrow(den2) - rank(den2[[vv]]) +1
+  
+  cols1 <- cols+length(cols)
+  den3 <-merge(den1,eks,by.x=cols,by.y=cols1)[,1:(length(cols)+2)]
+  den3$parms <-paste(eks[,cols1],collapse="_")
+  den3$Rank <- nrow(den3) - rank(den3[[vv]]) +1
+  den2 <- rbind(den2,den3)
+  
+}
+
 # Calculate Ranks for every parameter combination, for ggplot2  
 #
 calcRankSAD  <- function(den)
@@ -154,6 +174,37 @@ pairwiseAD_SAD <- function(denl,vv,parms){
   return(mks)
 }
 
+
+# pairwise Anderson-Darling K test for all combinations of 
+# parameters in variable parms with repetitions, BEWARE last variable in parms must be 
+# the repetition
+# 
+# vv: name of the variable where density or proportion is
+# denl: data.frame with all data
+#
+pairwiseAD_Dif <- function(denl,vv,parms){
+  require(kSamples)
+
+  parms <- unique(parms)
+  combo <- combn(nrow(parms),2)
+  nc <- ncol(parms)-1
+  require(plyr)
+  mks <-adply(combo,2, function(x) {
+    p1 <- parms[x[1],]
+    p2 <- parms[x[2],]
[…]

### 2014-09-29 Neutral_simulPow.Rmd
addparallel and 64bit binary

@@
 ```{r setup, eval=T }
-
-simul  <- F # variable to perform or not the simulations
+load(".RData")
+#simul  <- F # variable to perform or not the simulations
 
@@
 neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"
+neuBin64<- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralE64"
 
@@
 
-```{r simul_LogSerParms, eval=T,echo=F,message=F,warning=F}
+```{r simul256_LogSerParms, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
-
-time <- 500
-meta <- "L"
-side <- 256
-nsp  <- 64
-
-if(toupper(meta)=="L") {
-  prob <- genFisherSAD(nsp,side)
-  neuParm <- "fishE"
-  bname <- paste0("neuFish",nsp)
-  sadName <- "Neutral"
-} else {
-  prob <- rep(1/nsp,nsp)  
-  neuParm <- "unifE"
-  bname <- paste0("neuUnif",nsp)
-  sadName <- "NeuUnif"
-}
-
-# Parameters
-#
-# Mortality = 0.2 - 0.4
-# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
-#                         2.5 -> 0.4
-# Colonization = 0.001 -0.0001
-# Replacement  = 0 - 1
-spMeta <- length(prob)
-# First generate de inp file with species and metacommunity parameters 
-genNeutralParms(neuParm,side,prob,1,0.2,0.04,0.0001)
-
-# Delete old simulations
-system(paste0("rm ",bname,"*.txt"))
-
-# we need the par file with the simulations parameters
-par <- read.table("sim.par",quote="",stringsAsFactors=F)
-
-# Number of time steps 
-par[par$V1=="nEvals",]$V2 <- time
-par[par$V1=="inter",]$V2 <- time # interval to measure Density and Diversity
-par[par$V1=="init",]$V2 <- time  # Firs time of measurement = interval
-par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
-par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
-par[par$V1=="baseName",]$V2 <- paste0(bName ,"T", time ) 
-par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
-                              # 1:several simulations with pomac.lin parameters
-
-write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
-
-# Then pomac.lin to simulate a range of parmeters and repetitions.
-#
-# Generates pomac.lin for multiple simulations exponential dispersal to compare hierarchical and neutral communities  
-# and see when they have similar H and compare if they have similar SAD
-
-genPomacParms("pomExp",1,c(0.2),c(0.04),c(0.0001),c(0,0.001),3)
-
-#genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
-
-# copy pomExp.lin to pomac.lin
-system("cp pomExp.lin pomac.lin")
-
-system(paste(neuBin,"sim.par",paste0(neuParm,".inp")))
-
-# Desde aca function compNeutral_Time  
-#
-fname <- paste0(bname,"T",time,"Density.txt")
-
-den1 <- meltDensityOut_NT(fname,spMeta)
-
-# Test pairwise diferences in SAD
-#
-mKS <- pairwiseAD_Dif(den1,"value",den1[,1:5])
-
-# Plot the first pairs not different 
-#
-mks <- mKS[mKS$p.value>0.05,2:ncol(mKS)]
-psa <- mergePairSadRank(mks[1,],den1,"value",1:5)
-psa <- rbind(psa,mergePairSadRank(mks[nrow(mks),],den1,"value",1:5))
-require(ggplot2)
-(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line() + ggtitle("SAD not dif"))
-
-# Build data.frame with proportions
-#
-#compM <- data.frame(time=Time,notdif=propNotDiffSAD(mKS),method="SAD")
-
-######################### HAY QUE VER DE LOS QUE SON IGUALES si dan distintos con DqSAD /SRS
-qNumber <- 35
-fname <- paste0(bname,"T",time,"mfOrd.txt")
-Dq1 <- readNeutral_calcDq(fname)
-Dq1$rep <- rep( 1:(nrow(Dq1)/qNumber),each=qNumber)
-
-mKS1 <- pairwiseAD_Dif(Dq1,"Dq",den1[,c(1:4,10])   #### TEST THIS!
-
-#
+#simul <- data.frame()
+simul <- rbind(simul,simulNeutral_1Time(8,256,500))
+simul <- rbind(simul,simulNeutral_1Time(64,256,500))
+simul <- rbind(simul,simulNeutral_1Time(256,256,500))
 
 setwd(oldcd)
-rm(Dq1,den1)
-rm(den1,den,mks1,mks,mks100)
 save.image()
@@
 
-## Simulations at Time=500
-
-```{r simul_pomac467_T500, eval=T,echo=F,message=F,warning=F }
-load(".RData")
-
+```{r simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
 
-# read par file with simulations parameters
-if(simul)
-{
-  # Delete old simulations
-  system("rm Exp467T500*")
+simul <- rbind(simul,simulNeutral_1Time(8,512,500))
+simul <- rbind(simul,simulNeutral_1Time(64,512,500))
+simul <- rbind(simul,simulNeutral_1Time(256,512,500))
 
-  par <- read.table("sim.par",quote="",stringsAsFactors=F)
-
-  # Number of time steps 
-  par[par$V1=="nEvals",]$V2 <- 500
-  par[par$V1=="inter",]$V2 <- 500 # interval to measure Density and Diversity
-  par[par$V1=="init",]$V2 <- 500  # Firs time of measurement = interval
-  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
-  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
-  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T500")
-  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
-                                # 1:several simulations with pomac.lin parameters
-
-  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
-
-  # I will not delete old simulations
-  # system("rm Exp467*")
-
-  # I have to modify pomExp.lin to make different simulations
-
-  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
-
-  # copy pomExp.lin to pomac.lin
-  system("cp pomExp.lin pomac.lin")
-
-  s <- paste(neuBin,"sim.par","fishE.inp")
-  s
-  system(s,wait=F)
-}
-
-m <- compMethods_Time(bName,500,spMeta)
-
-compM <- rbind(compM,m$compM)
-
-pander(compM,caption="Proportion of not different")
-
-mks1 <- m$mPval
-mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
-pander(mks1,caption="DqSAD not different T=500")
-
-Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))
-
-mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=500")
-
-mPval <- rbind(mPval,m$mPval)
-
-mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]
+# rename s/'64'/'64_512'/ *neuFish64*.txt
 
 setwd(oldcd)
-rm(Dq1,m,mks1)
 save.image()
@@
 
-Now the same set of simulations for T=1000
+Calculate power of DqSAD DqSRS
 
-```{r simul_pomac467_T1000, eval=T,echo=F,message=F,warning=F}
-
-# Load data if run only one chunk 
-#load(".RData")
-
+```{r power_LogSerParms, eval=T,echo=F,message=F,warning=F}
 setwd("Simul")
 
-if(simul)
+# Testing
+#simul <- data.frame()
+#sim1 <- rbind(simul,simulNeutral_1Time(65,256,100,"L",3))
+#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
+#cc <- powerNeutral_1Time(sim1)
+
+require(doParallel)
+cl <- makeCluster(2)
+registerDoParallel(cl)
+require(foreach)
+
+pow_AD <- data.frame()
+comp_AD<- data.frame()
+foreach(i=1:nrow(simul)) %dopar%
 {
-  # Delete old simulations
-  system("rm Exp467T1000*")
+  cc <- powerNeutral_1Time(simul[i,])
+}
+for(i in 1:nrow(simul)) {
+pow_AD <- rbind(pow_AD, cc[[i]]$pow_AD)
+comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+}
+rm(cc)
+setwd(oldcd)
+save.image()
+```
 
-  # read par file with simulations parameters
+Calculate power by number of species
 
-  par <- read.table("sim.par",quote="",stringsAsFactors=F)
+```{r power_LogSer1, eval=F,echo=T,message=T,warning=T}
+setwd("Simul")
 
-  # Number of time steps 
-  par[par$V1=="nEvals",]$V2 <- 1000
-  par[par$V1=="inter",]$V2 <- 1000 # interval to measure Density and Diversity
-  par[par$V1=="init",]$V2 <- 1000  # Firs time of measurement = interval
-  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
-  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
-  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T1000")
-  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
-                                # 1:several simulations with pomac.lin parameters
-
-  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
-
-  # I have to modify pomExp.lin to make different simulations
-
-  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
-
-  # copy pomExp.lin to pomac.lin
-  system("cp pomExp.lin pomac.lin")
-
-  s <- paste(neuBin,"sim.par","fishE.inp")
-  s
-  if(simul) system(s,wait=F)
+hh <-function(x) {
+  t <- nrow(x)
+  s <- nrow(x[x$p.value<0.05,])
+  data.frame(power=s/t,n=t)
 }
-
-m <- compMethods_Time(bName,1000,spMeta)
-
-compM <- rbind(compM,m$compM)
-
-pander(compM,caption="Proportion of not different")
-
-mks1 <- m$mPval
-mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
-pander(mks1,caption="DqSAD not different T1000")
-
-mPval <- rbind(mPval,m$mPval)
-
-setwd(oldcd)
-rm(m,mks1)
-save.image()
+require(plyr)
+c1 <- ddply(comp_AD,.(Type,NumSp),hh)
+c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2,])
+c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR1==RplR2,])
+c2 <- ddply(c1,.(Type,NumSp),hh)
+unique(c1$MrtR1)
+unique(c1$DspD1)
+unique(c1$ClnR1)
 
 ```
-
-The the proportion of different SAD is constant from T=500 it seems we reach steady state. I have to compare now using H and Dq, for that I should do repeated simulations
-of each combination.
-
-```{r plot_Time_pomac467,eval=T,echo=F,message=F,warning=F}
-
-setwd("Simul")
-
-# Plot different SAD with time
-
-# Plot different Dq SRS with time
-
-Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))
-Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfOrd.txt")))
-Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfOrd.txt")))
-
-mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust>0.05,]
-
-mergePair_plotDq(mks1[1,],Dq1,"SRS not different")
-
-mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust<=0.05,]
-
-mergePair_plotDq(mks1[4,],Dq1,"SRS different")
-
-# Plot different Dq SAD with time
-
-Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
-Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfSAD.txt")))
-Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt")))
-
-mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]
-
-mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different")
-
-mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust<=0.05,]
-
-mergePair_plotDq(mks1[4,],Dq1,"DqSAD different")
-
-setwd(oldcd)
-
-```
-
-```{r compKS_pomac467,eval=T,echo=F,message=F,warning=F}
-source("R/Neutral_fun.r")
-
-setwd("Simul")
-
-m <- compMethod_DqKS_Time(bName,100,spMeta)
-
-compM <- rbind(compM,m$compM)
-
-pander(compM,caption="Proportion of not different")
-
-mPval <- rbind(mPval,m$mPval)
-
-m <- compMethod_DqKS_Time(bName,500,spMeta) 
-compM <- rbind(compM,m$compM)
-pander(compM,caption="Proportion of not different")
-mPval <- rbind(mPval,m$mPval)
-
-m <- compMethod_DqKS_Time(bName,1000,spMeta) 
-compM <- rbind(compM,m$compM)
-pander(compM,caption="Proportion of not different")
-mPval <- rbind(mPval,m$mPval)
-
-setwd(oldcd)
-
-rm(m)
-
-compM
-
-save.image()
-
-names(mPval)
-unique(mPval$method)
-m <- with(mPval,mPval[method=="DqSADKS" & time==100,])
-propNotDiffSAD(m)
-
-```

### 2014-09-29 R/Neutral_fun.r

@@ -184,15 +184,18 @@ pairwiseAD_SAD <- function(denl,vv,parms){
 #
 pairwiseAD_Dif <- function(denl,vv,parms){
   require(kSamples)
-
   parms <- unique(parms)
   combo <- combn(nrow(parms),2)
-  nc <- ncol(parms)-1
+  nc <- ncol(parms)-2
+  pb <- txtProgressBar(min = 0, max = ncol(combo), style = 3)
+  i <- 0
   require(plyr)
   mks <-adply(combo,2, function(x) {
     p1 <- parms[x[1],]
     p2 <- parms[x[2],]
-    if(sum(p1[,1:nc]==p2[,1:nc])<nc) {
+    i <<- i+1 
+    setTxtProgressBar(pb, i)
+    if(sum(p1[,1:nc]==p2[,1:nc])==nc) {
       d1 <- merge(denl,p1)
       d2 <- merge(denl,p2)
       ks <- ad.test(list(d1[,vv],d2[,vv]),method="simulated",nsim=1000)
@@ -202,6 +205,7 @@ pairwiseAD_Dif <- function(denl,vv,parms){
     } else { out<-NULL}
     return(out)      
   })
+  close(pb)
   mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
   return(mks)
 }
@@ -1363,84 +1367,201 @@ calcPower_AD <- function(Dqq,Sad,nsp,side){
   return(pow)
 }
 
-compNeutral_Time <- function(bName,Time,spMeta) 
+simulNeutral_1Time<- function(nsp,side,time,meta="L",rep=10)
 {
-  # Read all simulations and change to long format
-  fname <- paste0(bName,"T",Time,"Density.txt")
+
+  if(toupper(meta)=="L") {
+    prob <- genFisherSAD(nsp,side)
+    neuParm <- "fishE"
+    bname <- paste0("neuFish",nsp,"_",side)
+    sadName <- "Neutral"
+  } else {
+    prob <- rep(1/nsp,nsp)  
+    neuParm <- "unifE"
+    bname <- paste0("neuUnif",nsp,"_",side)
+    sadName <- "NeuUnif"
+  }
+
+  # Parameters
+  #
+  # Mortality = 0.2 - 0.4
+  # Mean Dispersal distance 25  -> Exponential kernel parm  0.04
+  #                         2.5 -> 0.4
[…]

### 2014-09-29 R/test_parallel.r

@@ -1,0 +1,31 @@
+require(doParallel)
+cl <- makeCluster(2)
+registerDoParallel(cl)
+require(foreach)
+
+cc <-foreach(i=1:nrow(simul)) %dopar% 
+{
+  p <- data.frame(a1=i,a=runif(5),b=runif(5))
+  c <- data.frame(c1=i,c=runif(5),d=runif(5))
+  cc <- list("p"=p, "c"=c)
+}
+po <- data.frame()
+co <- data.frame()
+for(i in 1:nrow(simul)) {
+  po <- rbind(po, cc[[i]]$p)
+  co<- rbind(co,cc[[i]]$c)
+}
+
+library(rbenchmark)
+benchmark( foreach(i=1:nrow(simul)) %dopar% 
+{
+  p <- data.frame(a1=i,a=runif(5000),b=runif(5000))
+  c <- data.frame(c1=i,c=runif(5000),d=runif(5000))
+  cc <- list("p"=p, "c"=c)
+}, 
+foreach(i=1:nrow(simul)) %do% 
+{
+  p <- data.frame(a1=i,a=runif(5000),b=runif(5000))
+  c <- data.frame(c1=i,c=runif(5000),d=runif(5000))
+  cc <- list("p"=p, "c"=c)
+})

### 2014-10-09 Neutral_simulPow.Rmd
Add D1 T-test and compareTwoGrowthCurves comparisons, model description in methods

@@
 
-Calculate power of DqSAD DqSRS
+## Calculate power of SAD DqSAD DqSRS for parameters
 
-```{r power_LogSerParms, eval=T,echo=F,message=F,warning=F}
+Mortality=0.2
+Dispersal=0.04
+Colonization=0.001
+
+```{r power_LogSerParms, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 #sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
-#cc <- powerNeutral_1Time(sim1)
+#cc <- powerNeutral_1Time(simul[4,])
 
 require(doParallel)
-cl <- makeCluster(2)
+cn <-detectCores()
+cl <- makeCluster(cn)
 registerDoParallel(cl)
@@
 comp_AD<- data.frame()
-foreach(i=1:nrow(simul)) %dopar%
+cc <- foreach(i=1:nrow(simul)) %dopar%
 {
-  cc <- powerNeutral_1Time(simul[i,])
+    powerNeutral_1Time(simul[i,],0.2, 0.04, 0.001) # Mortality,Dispersal,Colonization
 }
+
 for(i in 1:nrow(simul)) {
@@
 rm(cc)
+pow_AD$MrtR <- 0.2
+pow_AD$DspD <- 0.04
+pow_AD$ClnR <- 0.001
+
+stopCluster(cl)
+
 setwd(oldcd)
@@
 
-Calculate power by number of species
+## Calculate power of SAD DqSAD DqSRS for parameters
 
-```{r power_LogSer1, eval=F,echo=T,message=T,warning=T}
+Mortality=0.2
+Dispersal=0.4
+Colonization=0.001
+
+```{r power_LogSerParms1, eval=F,echo=F,message=T,warning=T}
 setwd("Simul")
 
+#cc <- powerNeutral_1TimeParms(simul,0.2,0.4,0.001)
+
+#pow_AD <- rbind(pow_AD,cc$pow_AD)
+#comp_AD<- rbind(comp_AD,cc$comp_AD)
+#rm(cc)
+
+mm <- 0.2
+dd <- 0.4
+co <- 0.001
+
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+cc <- foreach(i=1:nrow(simul)) %dopar%
+{
+    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
+}
+p_AD <- data.frame()
+
+for(i in 1:nrow(simul)) {
+	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
+	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+}
+rm(cc)
+p_AD$MrtR <- mm
+p_AD$DspD <- dd
+p_AD$ClnR <- co
+
+pow_AD <- rbind(pow_AD, p_AD)
+
+stopCluster(cl)
+
+setwd(oldcd)
+save.image()
+```
+
+## Calculate power of SAD DqSAD DqSRS for parameters
+
+Mortality=0.4
+Dispersal=0.04
+Colonization=0.001
+
+```{r power_LogSerParms2, eval=F,echo=F,message=T,warning=T}
+setwd("Simul")
+
+mm <- 0.4
+dd <- 0.04
+co <- 0.001
+
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+cc <- foreach(i=1:nrow(simul)) %dopar%
+{
+    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
+}
+p_AD <- data.frame()
+
+for(i in 1:nrow(simul)) {
+  	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
+	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+}
+rm(cc)
+p_AD$MrtR <- mm
+p_AD$DspD <- dd
+p_AD$ClnR <- co
+
+pow_AD <- rbind(pow_AD, p_AD)
+
+stopCluster(cl)
+
+setwd(oldcd)
+save.image()
+```
+
+## Calculate power of SAD DqSAD DqSRS for parameters
+
+Mortality=0.4
+Dispersal=0.4
+Colonization=0.001
+
+```{r power_LogSerParms3, eval=F,echo=F,message=T,warning=T}
+setwd("Simul")
+
+mm <- 0.4
+dd <- 0.4
+co <- 0.001
+
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+cc <- foreach(i=1:nrow(simul)) %dopar%
+{
+    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
+}
+p_AD <- data.frame()
+
+for(i in 1:nrow(simul)) {
+    p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
+	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+}
+rm(cc)
+p_AD$MrtR <- mm
+p_AD$DspD <- dd
+p_AD$ClnR <- co
+
+pow_AD <- rbind(pow_AD, p_AD)
+
+stopCluster(cl)
+rm(p_AD)
+setwd(oldcd)
+save.image()
+```
+# Make plots of power!
+
+I do not use simulations with ColonizationRate = 0.0001
+
+Replace NumSp with spMeta=number of species in metacommunity
+
+```{r power_PlotAD, eval=F,echo=F,message=T,warning=T}
+
+require(ggplot2)
+pow_AD$MeanSp <- as.numeric(pow_AD$MeanSp)
+pow_AD$power <- as.numeric(pow_AD$power)
+pow_AD$typeI <- as.numeric(pow_AD$typeI)
+
+# Add field with combination of dispersal & mortality 
+pow_AD$DspMrt <- with(pow_AD,paste0(DspD," - ",MrtR))
+
+# Add number of species in the metacommunity
+pow_AD$spMeta <- ceiling(as.numeric(pow_AD$NumSp)*1.33)
+
+g <- ggplot(pow_AD,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type)
+g+theme_bw()
+
+g <- ggplot(pow_AD,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
+g+theme_bw()
+
+# Recalculate power from comp_AD
+#
+require(plyr)
 hh <-function(x) {
@@
 }
-require(plyr)
-c1 <- ddply(comp_AD,.(Type,NumSp),hh)
-c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2,])
-c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR1==RplR2,])
-c2 <- ddply(c1,.(Type,NumSp),hh)
-unique(c1$MrtR1)
-unique(c1$DspD1)
-unique(c1$ClnR1)
+
+# Calculate power in fuction of replacement rate difference
+# Falta cambiar NumSp por 
+c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+c1$DifR <- with(c1,abs(RplR2-RplR1))
+c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
+#ggsave("power_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
+g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
+
+# Calculate TypeI error in fuction of replacement rate
+c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
+c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
+names(c3)[4]<-"typeI"
+g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
+g+theme_bw()
+
+rm(c1,c2,c3)
 
 ```
+
+DqSAD have higher power but also a very high type I error rate.
+DqSRS have lower power and a lower type I error.
+SAD have low power with a small number of species and a low type I error rate.
+
+The power of the AD or KS test Depends on the number of points used so for SAD the number of species compared change the number of points used for the test, but for DqSRS and DqSAD the number of points is always q=35 thus so we could calculate more dimensions to raise the power of the test.
+
+# Test usign glm whic factors influence power
+
+```{r testAD_factors, eval=F,echo=F,message=T,warning=T}
+require(plyr)
+hh <-function(x) {
+  t <- nrow(x)
+  s <- nrow(x[x$p.value<0.05,])
+  data.frame(count=s,power=s/t,n=t)
+}
+# Calculate power
+c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+c1$DifR <- with(c1,abs(RplR2-RplR1))
+c2 <- ddply(c1,.(NumSp,Side,Type,MrtR1,DspD1,DifR),hh)
+#require(dplyr)
+#c2 <- tbl_df(c1)
+#c3 <- c2 %>% 
+#  group_by(NumSp,Side,Type,MrtR1,DspD1,DifR) %>% 
+#  filter(p.value<0.05) %>% 
+#  summarize(tot=n()) %>% 
+#  summarize(pgt5=n()) 
+model1 <-glm(count~NumSp*Side*Type*MrtR1*DspD1*DifR,poisson,data=c2)
+summary(model1)
+plot(model1)
+
+# HAVE TO USE BINOMIAL !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!1
+
+```
+
+# Use the information dimension t-test with sd from
+
+Fractal dimensions have several problems of estimation (Halley) so we use information dimension with sd estimated by the regression
+
+```{r infoDim_Ttest, eval=F,echo=F,message=T,warning=T}
+setwd("Simul")
+#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
+# 256 = 7 points for Dq
+#
+#cc <- powerNeutral_1T_D1(sim1,7,1)
+# 
+# Dq1 <- readNeutral_calcDq("neuFish65_256T100mfOrd.txt")
+# 
+# D1 <- DqT[DqT$q==1,]
+# dd <- D1[121:122,]
+# 
+# compareTwoCurvesT(dd$Type,dd$Dq,dd$SD.Dq,5)
+# 
+# dd <- D1[c(41,45),]
+# 
+# compareTwoCurvesT(dd$rep,dd$Dq,dd$SD.Dq,5)
+
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+cc <- foreach(i=1:nrow(simul)) %dopar%
+{
+    powerNeutral_1T_D1(simul[i,],log2(simul$side)-1,1,0,0,0.001)
+}
+pow_TD1 <- data.frame()
+comp_TD1<- data.frame()
+
+for(i in 1:nrow(simul)) {
+  pow_TD1 <- rbind(pow_TD1, cc[[i]]$pow_AD)
+  comp_TD1<- rbind(comp_TD1,cc[[i]]$comp_AD)
+}
+rm(cc)
+
+stopCluster(cl)
+
+setwd(oldcd)
+save.image()
+
+```
+
+The power of D1 is around .5 too low
+
+Lets check
+
+```{r power_PlotD1T, eval=F,echo=F,message=T,warning=T}
+
+require(ggplot2)
+pow_AD$MeanSp <- as.numeric(pow_AD$MeanSp)
+pow_AD$power <- as.numeric(pow_AD$power)
+pow_AD$typeI <- as.numeric(pow_AD$typeI)
+
+# Add field with combination of dispersal & mortality 
+pow_AD$DspMrt <- with(pow_AD,paste0(DspD," - ",MrtR))
+
+# En vez de hacer merge fijarse donde genero parametros de simulacion!!!!!!!!
+pad <- merge(pow_AD,simul,by.x=c("Side","NumSp"),by.y=c("side","nsp") )
+
+g <- ggplot(pad,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type)
+g+theme_bw()
+
+g <- ggplot(pow_AD,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
+g+theme_bw()
+
+# Recalculate power from comp_AD
+#
+require(plyr)
+hh <-function(x) {
+  t <- nrow(x)
+  s <- nrow(x[x$p.value<0.05,])
+  data.frame(power=s/t,n=t)
+}
+
+# Calculate power in fuction of replacement rate difference
+# Falta cambiar NumSp por 
+c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+c1$DifR <- with(c1,abs(RplR2-RplR1))
+c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
+#ggsave("power_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
+g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
+
+# Calculate TypeI error in fuction of replacement rate
+c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
+c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
+names(c3)[4]<-"typeI"
+g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
+g+theme_bw()
+
+rm(c1,c2,c3)
+
+```
+
+```{r power_GCtest, eval=F,echo=F,message=T,warning=T}
+setwd("Simul")
+# sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
+#
+#cc <- powerNeutral_1T_GC(simul[1,],3,0,0,0.001)
+
+# Error en
+# [1] "0.2_0.04_0.0001_1_1 4 0.2_0.04_0.0001_0.1_0 3"
+
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+cc <- foreach(i=1:nrow(simul)) %dopar%
+{
+    powerNeutral_1T_GC(simul[i,],3,0,0,0.001)
+}
+pow_GC1 <- data.frame()
+comp_GC1<- data.frame()
+
+for(i in 1:nrow(simul)) {
+
+  pow_GC1 <- rbind(pow_GC1, cc[[i]]$pow_AD)
+  comp_GC1<- rbind(comp_GC1,cc[[i]]$comp_AD)
+  }
+
+setwd(oldcd)
+save.image()
+```
+
+More simulations to do comparisons with GC
+
+```{r more_simul512_LogSerParms, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
+
+simul <- rbind(simul,simulNeutral_1Time(8,512,500,"L",20,F))
+simul <- rbind(simul,simulNeutral_1Time(64,512,500,"L",20,F))
+simul <- rbind(simul,simulNeutral_1Time(256,512,500,"L",20,F))
+
+# rename s/'64'/'64_512'/ *neuFish64*.txt
+
+setwd(oldcd)
+save.image()

### 2014-10-09 R/Neutral_fun.r

@@ -187,25 +187,31 @@ pairwiseAD_Dif <- function(denl,vv,parms){
   parms <- unique(parms)
   combo <- combn(nrow(parms),2)
   nc <- ncol(parms)-2
-  pb <- txtProgressBar(min = 0, max = ncol(combo), style = 3)
-  i <- 0
+  #pb <- txtProgressBar(min = 0, max = ncol(combo), style = 3)
+  #i <- 0
   require(plyr)
   mks <-adply(combo,2, function(x) {
+    
     p1 <- parms[x[1],]
     p2 <- parms[x[2],]
-    i <<- i+1 
-    setTxtProgressBar(pb, i)
+    out<-NULL
+    #i <<- i+1 
+    #setTxtProgressBar(pb, i)
+    # test the error!!!!!!!!!
+    print(paste(paste(p1,collapse="_"),nrow(d1),paste(p2,collapse="_"),nrow(d2)))
     if(sum(p1[,1:nc]==p2[,1:nc])==nc) {
       d1 <- merge(denl,p1)
       d2 <- merge(denl,p2)
-      ks <- ad.test(list(d1[,vv],d2[,vv]),method="simulated",nsim=1000)
-      out <-data.frame(p1,p2,stat=ks$ad[2,2],p.value=ks$ad[2,4],stringsAsFactors=F)
-      ln <-length(names(p1))*2
-      names(out)[1:(ln)]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2))
-    } else { out<-NULL}
+      if(nrow(d1)>2 & nrow(d2)>2) {
+        ks <- ad.test(list(d1[,vv],d2[,vv]),method="simulated",Nsim=1000)
+        out <-data.frame(p1,p2,stat=ks$ad[2,2],p.value=ks$ad[2,4],stringsAsFactors=F)
+        ln <-length(names(p1))*2
+        names(out)[1:(ln)]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2))
+      }
+    }
     return(out)      
   })
-  close(pb)
+  #close(pb)
   mks$p.adjust <- p.adjust(mks$p.value, method="hommel")
   return(mks)
 }
@@ -1367,7 +1373,7 @@ calcPower_AD <- function(Dqq,Sad,nsp,side){
[…]

### 2014-10-09 R/Test_Dq_fun.r

@@ -123,7 +123,7 @@ compareTwoCurvesMC <- function (group, y, sd,nsim = 1000)
 #
 compareTwoCurvesT <- function (group, y, sd,n) 
 {
-  group <- as.vector(group)
+#  group <- as.vector(group)
   g <- unique(group)
   if (length(g) != 2) 
     stop("Must be exactly 2 groups")
@@ -135,9 +135,11 @@ compareTwoCurvesT <- function (group, y, sd,n)
   sd2 <- sd2*sd2
   stat <- (y1-y2)/sqrt((sd1/n)+(sd2/n))
   df <- (sd1/n+sd2/n)^2/( (sd1/n)^2 / (n-1) + (sd2/n)^2 / (n-1)) 
-  p <- p.adjust(pt(stat,df),method="hommel")
+  #p.adjust <- p.adjust(pt(stat,df),method="hommel")
+  p <- pt(stat,df)
   #print(ks.test(y1,y2))
   #print(t.test(y1-y2,mu=0))
+  return(list("stat"=stat,"p"=p))
 }
 
 # Fisher procedure to combine p.value from multiple T test in one p.value

### 2014-10-11 Neutral_simulPow.Rmd
Restrict q<=10 for growthCurve comparison

@@
 
-g <- ggplot(pow_AD,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type)
+g <- ggplot(pow_AD,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
+  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
+  xlab("Metacommunity species number") +
+  scale_size_continuous(name="Type I error") +
+  scale_colour_discrete(name="Disp - Mort")
+
 g+theme_bw()
+ggsave("powAD_spMeta_Side.png", width=6,height=6,units="in",dpi=600)
 
@@
 
+comp_AD$spMeta <- ceiling(as.numeric(comp_AD$NumSp)*1.33)
+
 # Calculate power in fuction of replacement rate difference
@@
 c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
-#ggsave("power_DifReplacement.png", width=6,height=6,units="in",dpi=600)
 
-g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
+g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)+
+  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
+  xlab(bquote(Delta ~"Replacement rate")) +
+  scale_size_continuous(name="Type I error") +
+  scale_colour_discrete(name="")
+
 g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
+
+ggsave("powAD_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+require(pander)
+pandoc.table(c2,style="grid")
 
@@
 
-# Test usign glm whic factors influence power
+# Test usign glm which factors influence power
 
@@
 #cc <- powerNeutral_1T_D1(sim1,7,1)
-# 
-# Dq1 <- readNeutral_calcDq("neuFish65_256T100mfOrd.txt")
-# 
-# D1 <- DqT[DqT$q==1,]
-# dd <- D1[121:122,]
-# 
-# compareTwoCurvesT(dd$Type,dd$Dq,dd$SD.Dq,5)
-# 
-# dd <- D1[c(41,45),]
-# 
-# compareTwoCurvesT(dd$rep,dd$Dq,dd$SD.Dq,5)
 
@@
 require(ggplot2)
-pow_AD$MeanSp <- as.numeric(pow_AD$MeanSp)
-pow_AD$power <- as.numeric(pow_AD$power)
-pow_AD$typeI <- as.numeric(pow_AD$typeI)
+pow_TD1$MeanSp <- as.numeric(pow_TD1$MeanSp)
+pow_TD1$power <- as.numeric(pow_TD1$power)
+pow_TD1$typeI <- as.numeric(pow_TD1$typeI)
+# Add number of species in the metacommunity
+pow_TD1$spMeta <- ceiling(as.numeric(pow_TD1$NumSp)*1.33)
 
-# Add field with combination of dispersal & mortality 
-pow_AD$DspMrt <- with(pow_AD,paste0(DspD," - ",MrtR))
+g <- ggplot(pow_TD1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
+  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
+  xlab("Metacommunity species number") +
+  scale_size_continuous(name="Type I error") +
+  scale_colour_discrete(name="")
 
-# En vez de hacer merge fijarse donde genero parametros de simulacion!!!!!!!!
-pad <- merge(pow_AD,simul,by.x=c("Side","NumSp"),by.y=c("side","nsp") )
-
-g <- ggplot(pad,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type)
 g+theme_bw()
 
-g <- ggplot(pow_AD,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
+ggsave("powTD1_spMeta_Side.png", width=6,height=6,units="in",dpi=600)
+
+g <- ggplot(pow_TD1,aes(x=spMeta,y=typeI)) + geom_point(shape=19,aes(size=power)) + facet_grid(Side ~ Type)
 g+theme_bw()
@@
 # Falta cambiar NumSp por 
-c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+comp_TD1$spMeta <- ceiling(as.numeric(comp_TD1$NumSp)*1.33)
+
+c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
 c1$DifR <- with(c1,abs(RplR2-RplR1))
-c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
-#ggsave("power_DifReplacement.png", width=6,height=6,units="in",dpi=600)
 
-g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
+c2 <- ddply(c1,.(spMeta,Type,DifR),hh)
+
+g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
+  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
+  xlab(bquote(Delta ~"Replacement rate")) +
+  scale_size_continuous(name="Type I error") +
+  scale_colour_discrete(name="")
+
 g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
 
+ggsave("powTD1_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
 # Calculate TypeI error in fuction of replacement rate
-c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
+c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
 c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
@@
 ```
+
+The power of D1 in combination with a T-test is relatively low with a maximun of 0.6 for
 
@@
 
+```{r power_PlotGC, eval=F,echo=F,message=T,warning=T}
+
+require(ggplot2)
+pow_GC1$MeanSp <- as.numeric(pow_GC1$MeanSp)
+pow_GC1$power <- as.numeric(pow_GC1$power)
+pow_GC1$typeI <- as.numeric(pow_GC1$typeI)
+
+# Add number of species in the metacommunity
+pow_GC1$spMeta <- ceiling(as.numeric(pow_GC1$NumSp)*1.33)
+
+g <- ggplot(pow_GC1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
+  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
+  xlab("Metacommunity species number") +
+  scale_size_continuous(name="Type I error") +
+  scale_colour_discrete(name="") 
+g+theme_bw()
+ggsave("powGC_spMeta_Side.png", width=6,height=6,units="in",dpi=600)
+
+# Recalculate power from comp_AD
+#
+require(plyr)
+hh <-function(x) {
+  t <- nrow(x)
+  s <- nrow(x[x$p.value<0.05,])
+  data.frame(power=s/t,n=t)
+}
+
+# Calculate power in fuction of replacement rate difference
+comp_GC1$spMeta <- ceiling(as.numeric(comp_GC1$NumSp)*1.33)
+
+c1 <- with(comp_GC1,comp_GC1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+c1$DifR <- with(c1,abs(RplR2-RplR1))
+
+c2 <- ddply(c1,.(spMeta,Type,DifR),hh)
+
+g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
+  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
+  xlab(bquote(Delta ~"Replacement rate")) +
+  scale_size_continuous(name="Type I error") +
+  scale_colour_discrete(name="")
+
+g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
+
+ggsave("powGC_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+```
+
 More simulations to do comparisons with GC
 
-```{r more_simul512_LogSerParms, eval=T,echo=F,message=F,warning=F}
+```{r more_simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 save.image()
+```
+
+```{r more_simul256_LogSerParms, eval=F,echo=F,message=F,warning=F}
+setwd("Simul")
+
+simul <- rbind(simul,simulNeutral_1Time(8,256,500,"L",20,F))
+simul <- rbind(simul,simulNeutral_1Time(64,256,500,"L",20,F))
+simul <- rbind(simul,simulNeutral_1Time(256,256,500,"L",20,F))
+
+setwd(oldcd)
+save.image()
+```
+Using the GC with q<=10
+
+```{r power_GCq10test, eval=T,echo=F,message=T,warning=T}
+setwd("Simul")
+# sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
+#
+#cc <- powerNeutral_1T_GC(simul[1,],3,0.2,0.04,0.001,10)
+
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+cc <- foreach(i=1:nrow(simul)) %dopar%
+{
+    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001,10)
+}
+pow_GCq10 <- data.frame()
+comp_GCq10<- data.frame()
+
+for(i in 1:nrow(simul)) {
+
+  pow_GCq10 <- rbind(pow_GCq10, cc[[i]]$pow_AD)
+  comp_GCq10<- rbind(comp_GCq10,cc[[i]]$comp_AD)
+  }
+
+# rename s/'64'/'64_512'/ *neuFish64*.txt
+
+setwd(oldcd)
+save.image()
+```

### 2014-10-11 R/Neutral_fun.r

@@ -1838,7 +1838,7 @@ pairwiseGC_Dif <- function(denl,vv,parms,numRep){
 # Compare neutral simulations using Dq compareTwoGrowthCurves 
 # numRep: number of repetitions used for each comparison
 # 
-powerNeutral_1T_GC <- function(pSimul,numRep,mr=0,dd=0,cr=0) 
+powerNeutral_1T_GC <- function(pSimul,numRep,mr=0,dd=0,cr=0,q=NULL) 
 {
   if( nrow(pSimul)>1)
     stop("Only one row of parameters")
@@ -1881,6 +1881,10 @@ powerNeutral_1T_GC <- function(pSimul,numRep,mr=0,dd=0,cr=0)
 
   Dq1$rep <- rep( 1:pSimul$rep,each=simbyrep)
 
+  if(!is.null(q)){
+    Dq1 <-Dq1[abs(Dq1$q)<=q,]
+  }
+
   mKS1 <- pairwiseGC_Dif(Dq1,"Dq",Dq1[,c(1:4,10)],numRep)   #### TEST THIS!
 
   pp  <- calcPower_fromFrame(mKS1)
@@ -1906,7 +1910,11 @@ powerNeutral_1T_GC <- function(pSimul,numRep,mr=0,dd=0,cr=0)
   simbyrep <- nrow(Dq1)/pSimul$rep
 
   Dq1$rep <- rep( 1:pSimul$rep,each=simbyrep)
-  
+
+  if(!is.null(q)){
+    Dq1 <-Dq1[abs(Dq1$q)<=q,]
+  }
+
   mKS2 <- pairwiseGC_Dif(Dq1,"Dq",Dq1[,c(1:4,10)],numRep)  
   
   pp  <- calcPower_fromFrame(mKS2)

### 2014-10-12 Neutral_simulPow.Rmd
add parallel simulNeutral_1Time function

@@
 
+stopCluster(cl)
+
 setwd(oldcd)
@@
 
-require(ggplot2)
+require(ggplot2)
 pow_GC1$MeanSp <- as.numeric(pow_GC1$MeanSp)
@@
 
-```{r more_simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
+```{r more_simul512_LogSerParms, eval=T,echo=F,message=F,warning=F}
 setwd("Simul")
 
-simul <- rbind(simul,simulNeutral_1Time(8,512,500,"L",20,F))
-simul <- rbind(simul,simulNeutral_1Time(64,512,500,"L",20,F))
-simul <- rbind(simul,simulNeutral_1Time(256,512,500,"L",20,F))
+ps <- data.frame(nsp=c(8,64,256),si=rep(c(512,256),each=3))
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
 
-# rename s/'64'/'64_512'/ *neuFish64*.txt
+simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
+{
+    print(ps[i,])
+    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",20,F)
+}
+stopCluster(cl)
 
 setwd(oldcd)
+rm(ps,cn,cl)
 save.image()
@@
 
-```{r more_simul256_LogSerParms, eval=F,echo=F,message=F,warning=F}
+Compare using the GC with q<=10
+
+```{r power_GCq10test, eval=F,echo=F,message=T,warning=T}
 setwd("Simul")
-
-simul <- rbind(simul,simulNeutral_1Time(8,256,500,"L",20,F))
-simul <- rbind(simul,simulNeutral_1Time(64,256,500,"L",20,F))
-simul <- rbind(simul,simulNeutral_1Time(256,256,500,"L",20,F))
-
-setwd(oldcd)
-save.image()
-```
-Using the GC with q<=10
-
-```{r power_GCq10test, eval=T,echo=F,message=T,warning=T}
-setwd("Simul")
-# sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
-#
-#cc <- powerNeutral_1T_GC(simul[1,],3,0.2,0.04,0.001,10)
 
@@
 {
-    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001,10)
+    powerNeutral_1T_GC(simul[i,],3,0,0,0.001,10)
 }
@@
 
-# rename s/'64'/'64_512'/ *neuFish64*.txt
+stopCluster(cl)
 
 setwd(oldcd)
+rm(cc)
 save.image()
+
 ```
+
+The power of compareGrowthCurves is much much greater using the range -10 10 than -24 24, and type I error is lower!!
+
+Lets try with ANderson-Darling test!
+
+```{r power_ADq10test, eval=F,echo=F,message=T,warning=T}
+setwd("Simul")
+
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+cc <- foreach(i=1:nrow(simul)) %dopar%
+{
+    powerNeutral_1Time(simul[i,],0.2,0.04,0.001,10)
+}
+pow_ADq10 <- data.frame()
+comp_ADq10<- data.frame()
+
+for(i in 1:nrow(simul)) {
+
+  pow_ADq10 <- rbind(pow_ADq10, cc[[i]]$pow_AD)
+  comp_ADq10<- rbind(comp_ADq10,cc[[i]]$comp_AD)
+  }
+
+stopCluster(cl)
+
+setwd(oldcd)
+rm(cc)
+save.image()
+
+```

### 2014-10-12 R/Neutral_fun.r

@@ -198,7 +198,6 @@ pairwiseAD_Dif <- function(denl,vv,parms){
     #i <<- i+1 
     #setTxtProgressBar(pb, i)
     # test the error!!!!!!!!!
-    print(paste(paste(p1,collapse="_"),nrow(d1),paste(p2,collapse="_"),nrow(d2)))
     if(sum(p1[,1:nc]==p2[,1:nc])==nc) {
       d1 <- merge(denl,p1)
       d2 <- merge(denl,p2)
@@ -1418,7 +1417,8 @@ simulNeutral_1Time<- function(nsp,side,time,meta="L",rep=10,delo=T)
   par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                 # 1:several simulations with pomac.lin parameters 
 
-  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
+  parfname <- paste0("sim",nsp,"_",side,".par")
+  write.table(par, parfname, sep="\t",row.names=F,col.names=F,quote=F)
 
   # Then pomac.lin to simulate a range of parmeters and repetitions.
   #
@@ -1433,17 +1433,17 @@ simulNeutral_1Time<- function(nsp,side,time,meta="L",rep=10,delo=T)
   # copy pomExp.lin to pomac.lin
   system("cp pomExp.lin pomac.lin")
   s <- system("uname -a",intern=T)
-  if(grepl("i386",s)) {
-    system(paste(neuBin,"sim.par",paste0(neuParm,".inp")))
+  if(grepl("i686",s)) {
+    system(paste(neuBin,parfname,paste0(neuParm,".inp")))
   } else {
-    system(paste(neuBin64,"sim.par",paste0(neuParm,".inp")))
+    system(paste(neuBin64,parfname,paste0(neuParm,".inp")))
   }
   return(data.frame(nsp,side,time,meta,spMeta,rep))
 }
 
 # Compare neutral simulations using anderson-darling test and calculate power
 #
-powerNeutral_1Time <- function(pSimul,mr=0,dd=0,cr=0,graph=F) 
[…]

### 2014-10-16 Neutral_simulPow.Rmd
Change powerNeutral_1T_D1 for compute power D_1SRS & D_0SAD add more methods

@@
 
-## Simulations with different parameters using pomac and at Time=100
+## Neutral Simulations
 
@@
 
-## Calculate power of SAD DqSAD DqSRS for parameters
+## Calculate power of SAD DqSAD DqSRS using q=[-24,24]
 
@@
 
-pow_AD <- data.frame()
-comp_AD<- data.frame()
+pow_ADq24 <- data.frame()
+comp_ADq24<- data.frame()
 cc <- foreach(i=1:nrow(simul)) %dopar%
@@
 for(i in 1:nrow(simul)) {
-pow_AD <- rbind(pow_AD, cc[[i]]$pow_AD)
-comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+pow_ADq24 <- rbind(pow_ADq24, cc[[i]]$pow_AD)
+comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
 }
 rm(cc)
-pow_AD$MrtR <- 0.2
-pow_AD$DspD <- 0.04
-pow_AD$ClnR <- 0.001
+pow_ADq24$MrtR <- 0.2
+pow_ADq24$DspD <- 0.04
+pow_ADq24$ClnR <- 0.001
 
@@
 #cc <- powerNeutral_1TimeParms(simul,0.2,0.4,0.001)
-
-#pow_AD <- rbind(pow_AD,cc$pow_AD)
-#comp_AD<- rbind(comp_AD,cc$comp_AD)
-#rm(cc)
 
@@
 	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
-	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
 }
@@
 
-pow_AD <- rbind(pow_AD, p_AD)
+pow_ADq24 <- rbind(pow_ADq24, p_AD)
 
@@
   	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
-	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
 }
@@
     p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
-	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
+	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
 }
@@
 ```
-# Make plots of power!
+# Make plots of power! using q=[-24,24]
 
@@
 require(ggplot2)
-pow_AD$MeanSp <- as.numeric(pow_AD$MeanSp)
-pow_AD$power <- as.numeric(pow_AD$power)
-pow_AD$typeI <- as.numeric(pow_AD$typeI)
+pow_ADq24$MeanSp <- as.numeric(pow_ADq24$MeanSp)
+pow_ADq24$power <- as.numeric(pow_ADq24$power)
+pow_ADq24$typeI <- as.numeric(pow_ADq24$typeI)
 
 # Add field with combination of dispersal & mortality 
-pow_AD$DspMrt <- with(pow_AD,paste0(DspD," - ",MrtR))
+pow_ADq24$DspMrt <- with(pow_ADq24,paste0(DspD," - ",MrtR))
 
 # Add number of species in the metacommunity
-pow_AD$spMeta <- ceiling(as.numeric(pow_AD$NumSp)*1.33)
+pow_ADq24$spMeta <- ceiling(as.numeric(pow_ADq24$NumSp)*1.33)
 
-g <- ggplot(pow_AD,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
+g <- ggplot(pow_ADq24,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
   ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
@@
 
-g <- ggplot(pow_AD,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
+g <- ggplot(pow_ADq24,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
 g+theme_bw()
 
-# Recalculate power from comp_AD
+# Recalculate power from comp_ADq24
 #
@@
 
-comp_AD$spMeta <- ceiling(as.numeric(comp_AD$NumSp)*1.33)
+comp_ADq24$spMeta <- ceiling(as.numeric(comp_ADq24$NumSp)*1.33)
 
@@
 # Falta cambiar NumSp por 
-c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
 c1$DifR <- with(c1,abs(RplR2-RplR1))
@@
 # Calculate TypeI error in fuction of replacement rate
-c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
+c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
 c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
@@
 # Calculate power
-c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
 c1$DifR <- with(c1,abs(RplR2-RplR1))
@@
 
-# Use the information dimension t-test with sd from
+# Use the information dimension t-test
 
@@
 {
-    powerNeutral_1T_D1(simul[i,],log2(simul$side)-1,1,0,0,0.001)
+    powerNeutral_1T_D1(simul[i,],log2(simul$side)-1,1,0.2,0.04,0.001)
 }
@@
 
-The power of D1 is around .5 too low
-
-Lets check
+## Plot power of D1
 
@@
 
-```{r more_simul512_LogSerParms, eval=T,echo=F,message=F,warning=F}
+```{r more_simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 {
-    print(ps[i,])
     simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",20,F)
@@
 
-```{r power_GCq10test, eval=F,echo=F,message=T,warning=T}
+```{r power_GCq10test, eval=T,echo=F,message=T,warning=T}
 setwd("Simul")
@@
 {
-    powerNeutral_1T_GC(simul[i,],3,0,0,0.001,10)
+    powerNeutral_1T_GC(simul[i,],3,40.2,0.0,0.001,10)
 }

### 2014-10-16 R/Neutral_fun.r

@@ -1377,12 +1377,12 @@ simulNeutral_1Time<- function(nsp,side,time,meta="L",rep=10,delo=T)
 
   if(toupper(meta)=="L") {
     prob <- genFisherSAD(nsp,side)
-    neuParm <- "fishE"
+    neuParm <- paste0("fishE",nsp,"_",side)
     bname <- paste0("neuFish",nsp,"_",side)
     sadName <- "Neutral"
   } else {
     prob <- rep(1/nsp,nsp)  
-    neuParm <- "unifE"
+    neuParm <- paste0("unifE",nsp,"_",side)
     bname <- paste0("neuUnif",nsp,"_",side)
     sadName <- "NeuUnif"
   }
@@ -1395,6 +1395,7 @@ simulNeutral_1Time<- function(nsp,side,time,meta="L",rep=10,delo=T)
   # Colonization = 0.001 -0.0001
   # Replacement  = 0 - 1
   spMeta <- length(prob)
+
   # First generate de inp file with species and metacommunity parameters 
   genNeutralParms(neuParm,side,prob,1,0.2,0.04,0.0001)
 
@@ -1655,7 +1656,7 @@ powerNeutral_1T_D1 <- function(pSimul,n,q=NULL,mr=0,dd=0,cr=0)
   pp  <- calcPower_fromFrame(mKS1)
 
   pow_AD <- data.frame(Side=side,NumSp=nsp,MeanSp=spMeta,Time=time,Type="DqSRS",nPower=pp$nPower,
-                       power=pp$power,nTypeI=pp$nTypeI,typeI=pp$typeI,stringsAsFactors = F)
+                       power=pp$power,nTypeI=pp$nTypeI,typeI=pp$typeI,q=q,stringsAsFactors = F)
  
   #pow_AD  <- rbind(pow_AD,c(side,nsp,m_nsp,time,Type="DqSRS",pp$nPower,pp$power,pp$nTypeI,pp$typeI))
  
@@ -1676,13 +1677,14 @@ powerNeutral_1T_D1 <- function(pSimul,n,q=NULL,mr=0,dd=0,cr=0)
 
   Dq1$rep <- rep( 1:pSimul$rep,each=simbyrep)
   if(!is.null(q)){
+    if(q==1) q <-0
     Dq1 <-Dq1[Dq1$q==q,]
   }
   
[…]

### 2014-10-28 Neutral_simulPow.Rmd
Add paper figures & tables

@@
 Now I will simulate the model to Time=500 with a full set of parameters 
-Replacement = 0,0.001,0.01,0.1,1 and ten repetitions
+Replacement = 0,0.001,0.01,0.1,1 and 30 repetitions
 
-```{r simul256_LogSerParms, eval=F,echo=F,message=F,warning=F}
+```{r simul30_LogSerParms, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
-#simul <- data.frame()
-simul <- rbind(simul,simulNeutral_1Time(8,256,500))
-simul <- rbind(simul,simulNeutral_1Time(64,256,500))
-simul <- rbind(simul,simulNeutral_1Time(256,256,500))
+
+ps <- data.frame(nsp=c(8,64,256),si=rep(c(512,256),each=3))
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+
+simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
+{
+    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",30,F)
+}
+stopCluster(cl)
 
 setwd(oldcd)
-save.image()
-
-```
-
-```{r simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
-setwd("Simul")
-
-simul <- rbind(simul,simulNeutral_1Time(8,512,500))
-simul <- rbind(simul,simulNeutral_1Time(64,512,500))
-simul <- rbind(simul,simulNeutral_1Time(256,512,500))
-
-# rename s/'64'/'64_512'/ *neuFish64*.txt
-
-setwd(oldcd)
+rm(ps,cn,cl)
 save.image()
@@
 # Testing
+#
 #simul <- data.frame()
@@
 
-require(doParallel)
-cn <-detectCores()
-cl <- makeCluster(cn)
-registerDoParallel(cl)
-require(foreach)
-
-pow_ADq24 <- data.frame()
-comp_ADq24<- data.frame()
-cc <- foreach(i=1:nrow(simul)) %dopar%
-{
-    powerNeutral_1Time(simul[i,],0.2, 0.04, 0.001) # Mortality,Dispersal,Colonization
-}
-
-for(i in 1:nrow(simul)) {
-pow_ADq24 <- rbind(pow_ADq24, cc[[i]]$pow_AD)
-comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
-}
-rm(cc)
-pow_ADq24$MrtR <- 0.2
-pow_ADq24$DspD <- 0.04
-pow_ADq24$ClnR <- 0.001
-
-stopCluster(cl)
-
-setwd(oldcd)
-save.image()
-```
-
-## Calculate power of SAD DqSAD DqSRS using q=[-24,24]
-
-Mortality=0.2
-Dispersal=0.4
-Colonization=0.001
-
-```{r power_LogSerParms1, eval=F,echo=F,message=T,warning=T}
-setwd("Simul")
-
-#cc <- powerNeutral_1TimeParms(simul,0.2,0.4,0.001)
-
 mm <- 0.2
-dd <- 0.4
-co <- 0.001
-
-require(doParallel)
-cn <-detectCores()
-cl <- makeCluster(cn)
-registerDoParallel(cl)
-require(foreach)
-
-cc <- foreach(i=1:nrow(simul)) %dopar%
-{
-    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
-}
-p_AD <- data.frame()
-
-for(i in 1:nrow(simul)) {
-	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
-	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
-}
-rm(cc)
-p_AD$MrtR <- mm
-p_AD$DspD <- dd
-p_AD$ClnR <- co
-
-pow_ADq24 <- rbind(pow_ADq24, p_AD)
-
-stopCluster(cl)
-
-setwd(oldcd)
-save.image()
-```
-
-## Calculate power of SAD DqSAD DqSRS using q=[-24,24]
-
-Mortality=0.4
-Dispersal=0.04
-Colonization=0.001
-
-```{r power_LogSerParms2, eval=F,echo=F,message=T,warning=T}
-setwd("Simul")
-
-mm <- 0.4
 dd <- 0.04
@@
 }
-p_AD <- data.frame()
+pow_ADq24 <- data.frame()
+comp_ADq24<- data.frame()
 
 for(i in 1:nrow(simul)) {
-  	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
+  pow_ADq24 <- rbind(pow_ADq24, cc[[i]]$pow_AD)
 	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
 }
+
 rm(cc)
-p_AD$MrtR <- mm
-p_AD$DspD <- dd
-p_AD$ClnR <- co
-
-pow_ADq24 <- rbind(pow_ADq24, p_AD)
 
@@
 save.image()
-```
-
-## Calculate power of SAD DqSAD DqSRS using q=[-24,24]
-
-Mortality=0.4
-Dispersal=0.4
-Colonization=0.001
-
-```{r power_LogSerParms3, eval=F,echo=F,message=T,warning=T}
-setwd("Simul")
-
-mm <- 0.4
-dd <- 0.4
-co <- 0.001
-
-require(doParallel)
-cn <-detectCores()
-cl <- makeCluster(cn)
-registerDoParallel(cl)
-require(foreach)
-
-cc <- foreach(i=1:nrow(simul)) %dopar%
-{
-    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
-}
-p_AD <- data.frame()
-
-for(i in 1:nrow(simul)) {
-    p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
-	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
-}
-rm(cc)
-p_AD$MrtR <- mm
-p_AD$DspD <- dd
-p_AD$ClnR <- co
-
-pow_ADq24 <- rbind(pow_ADq24, p_AD)
-
-stopCluster(cl)
-rm(p_AD)
-setwd(oldcd)
-save.image()
-```
-# Make plots of power! using q=[-24,24]
-
-I do not use simulations with ColonizationRate = 0.0001
-
-Replace NumSp with spMeta=number of species in metacommunity
-
-```{r power_PlotAD, eval=F,echo=F,message=T,warning=T}
-
-require(ggplot2)
-pow_ADq24$MeanSp <- as.numeric(pow_ADq24$MeanSp)
-pow_ADq24$power <- as.numeric(pow_ADq24$power)
-pow_ADq24$typeI <- as.numeric(pow_ADq24$typeI)
-
-# Add field with combination of dispersal & mortality 
-pow_ADq24$DspMrt <- with(pow_ADq24,paste0(DspD," - ",MrtR))
-
-# Add number of species in the metacommunity
-pow_ADq24$spMeta <- ceiling(as.numeric(pow_ADq24$NumSp)*1.33)
-
-g <- ggplot(pow_ADq24,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
-  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
-  xlab("Metacommunity species number") +
-  scale_size_continuous(name="Type I error") +
-  scale_colour_discrete(name="Disp - Mort")
-
-g+theme_bw()
-ggsave("powAD_spMeta_Side.png", width=6,height=6,units="in",dpi=600)
-
-g <- ggplot(pow_ADq24,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
-g+theme_bw()
-
-# Recalculate power from comp_ADq24
-#
-require(plyr)
-hh <-function(x) {
-  t <- nrow(x)
-  s <- nrow(x[x$p.value<0.05,])
-  data.frame(power=s/t,n=t)
-}
-
-comp_ADq24$spMeta <- ceiling(as.numeric(comp_ADq24$NumSp)*1.33)
-
-# Calculate power in fuction of replacement rate difference
-# Falta cambiar NumSp por 
-c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
-c1$DifR <- with(c1,abs(RplR2-RplR1))
-c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
-
-g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)+
-  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
-  xlab(bquote(Delta ~"Replacement rate")) +
-  scale_size_continuous(name="Type I error") +
-  scale_colour_discrete(name="")
-
-g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
-
-ggsave("powAD_DifReplacement.png", width=6,height=6,units="in",dpi=600)
-
-require(pander)
-pandoc.table(c2,style="grid")
-
-# Calculate TypeI error in fuction of replacement rate
-c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
-c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
-names(c3)[4]<-"typeI"
-g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
-g+theme_bw()
-
-rm(c1,c2,c3)
-
 ```
@@
 c1$DifR <- with(c1,abs(RplR2-RplR1))
-c2 <- ddply(c1,.(NumSp,Side,Type,MrtR1,DspD1,DifR),hh)
+c2 <- ddply(c1,.(NumSp,Side,Type,DifR),hh)
 #require(dplyr)
@@
 #  summarize(pgt5=n()) 
-model1 <-glm(count~NumSp*Side*Type*MrtR1*DspD1*DifR,poisson,data=c2)
+model1 <-glm(count~NumSp*Side*Type*DifR,poisson,data=c2)
 summary(model1)
@@
 ```
-
-## Plot power of D1
-
-```{r power_PlotD1T, eval=F,echo=F,message=T,warning=T}
-
-require(ggplot2)
-pow_TD1$MeanSp <- as.numeric(pow_TD1$MeanSp)
-pow_TD1$power <- as.numeric(pow_TD1$power)
-pow_TD1$typeI <- as.numeric(pow_TD1$typeI)
-# Add number of species in the metacommunity
-pow_TD1$spMeta <- ceiling(as.numeric(pow_TD1$NumSp)*1.33)
-
-g <- ggplot(pow_TD1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
-  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
-  xlab("Metacommunity species number") +
-  scale_size_continuous(name="Type I error") +
-  scale_colour_discrete(name="")
-
-g+theme_bw()
-
-ggsave("powTD1_spMeta_Side.png", width=6,height=6,units="in",dpi=600)
-
-g <- ggplot(pow_TD1,aes(x=spMeta,y=typeI)) + geom_point(shape=19,aes(size=power)) + facet_grid(Side ~ Type)
-g+theme_bw()
-
-# Recalculate power from comp_AD
-#
-require(plyr)
-hh <-function(x) {
-  t <- nrow(x)
-  s <- nrow(x[x$p.value<0.05,])
-  data.frame(power=s/t,n=t)
-}
-
-# Calculate power in fuction of replacement rate difference
-# Falta cambiar NumSp por 
-comp_TD1$spMeta <- ceiling(as.numeric(comp_TD1$NumSp)*1.33)
-
-c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
-c1$DifR <- with(c1,abs(RplR2-RplR1))
-
-c2 <- ddply(c1,.(spMeta,Type,DifR),hh)
-
-g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
-  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
-  xlab(bquote(Delta ~"Replacement rate")) +
-  scale_size_continuous(name="Type I error") +
-  scale_colour_discrete(name="")
-
-g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
-
-ggsave("powTD1_DifReplacement.png", width=6,height=6,units="in",dpi=600)
-
-# Calculate TypeI error in fuction of replacement rate
-c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
-c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
-names(c3)[4]<-"typeI"
-g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
-g+theme_bw()
-
-rm(c1,c2,c3)
-
-```
-
-The power of D1 in combination with a T-test is relatively low with a maximun of 0.6 for
+Calculate Power using compareGrowthCurves and q=-24,24
 
@@
 {
-    powerNeutral_1T_GC(simul[i,],3,0,0,0.001)
+    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001)
 }
@@
 setwd(oldcd)
+rm(cc)
 save.image()
-```
-
-```{r power_PlotGC, eval=F,echo=F,message=T,warning=T}
-
-require(ggplot2)
-pow_GC1$MeanSp <- as.numeric(pow_GC1$MeanSp)
-pow_GC1$power <- as.numeric(pow_GC1$power)
-pow_GC1$typeI <- as.numeric(pow_GC1$typeI)
-
-# Add number of species in the metacommunity
-pow_GC1$spMeta <- ceiling(as.numeric(pow_GC1$NumSp)*1.33)
-
-g <- ggplot(pow_GC1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
-  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
-  xlab("Metacommunity species number") +
-  scale_size_continuous(name="Type I error") +
-  scale_colour_discrete(name="") 
-g+theme_bw()
-ggsave("powGC_spMeta_Side.png", width=6,height=6,units="in",dpi=600)
-
-# Recalculate power from comp_AD
-#
-require(plyr)
-hh <-function(x) {
-  t <- nrow(x)
-  s <- nrow(x[x$p.value<0.05,])
-  data.frame(power=s/t,n=t)
-}
-
-# Calculate power in fuction of replacement rate difference
-comp_GC1$spMeta <- ceiling(as.numeric(comp_GC1$NumSp)*1.33)
-
-c1 <- with(comp_GC1,comp_GC1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
-c1$DifR <- with(c1,abs(RplR2-RplR1))
-
-c2 <- ddply(c1,.(spMeta,Type,DifR),hh)
-
-g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
-  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
-  xlab(bquote(Delta ~"Replacement rate")) +
-  scale_size_continuous(name="Type I error") +
-  scale_colour_discrete(name="")
-
-g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()
-
-ggsave("powGC_DifReplacement.png", width=6,height=6,units="in",dpi=600)
-
 ```
@@
 
+#] "0.2_0.04_0.001_1_1 3 0.2_0.04_0.001_1_3 3"
+# Error: valor ausente donde TRUE/FALSE es necesario
+
 cc <- foreach(i=1:nrow(simul)) %dopar%
 {
-    powerNeutral_1T_GC(simul[i,],3,40.2,0.0,0.001,10)
+    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001,10)
 }
@@
 ```
+
+# Make plots of power! using q=[-24,24]
+
+```{r power_PlotAD, eval=F,echo=F,message=T,warning=T}
+
+require(dplyr)
+#pow_ADq24 <- with(pow_AD,pow_AD[MrtR==0.2 & DspD==0.04 & ClnR==0.001,])
+
+# Select only the subset I will use
+#
+#pow_ADq24 <- filter(pow_AD,MrtR==0.2 & DspD==0.04 & ClnR==0.001) %>%
+#  mutate(spMeta = ceiling(as.numeric(NumSp)*1.33))
+
+plotPow_MeanSp_side(pow_ADq24)
+
+ggsave("powADq24_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)
+
+require(pander)
+pandoc.table(select(pow_ADq24,Side,spMeta,MeanSp, c(5:9)),style="grid",split.tables=Inf)
+
+pow_ADq24 <- pow_ADq24 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))
+
+comp_ADq24 <- comp_AD %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
+  left_join(unique(pow_ADq24[,1:3]),by=c("Side","NumSp"))
+
+plotPow_MeanSp_difR(comp_ADq24)
+
+ggsave("powADq24_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+# Calculate TypeI error in fuction of replacement rate
+#c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
+#c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
+#names(c3)[4]<-"typeI"
+#g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
+#g+theme_bw()
+
+#rm(c1,c2,c3)
+
+```
+## Plot power of D1
+
+```{r power_PlotD1T, eval=F,echo=F,message=T,warning=T}
+
+require(dplyr)
+
+#pow_TD1$spMeta <- ceiling(as.numeric(pow_TD1$NumSp)*1.33)
+
+pow_TD1 <- pow_TD1 %>% select(-MeanSp) %>% 
+  mutate(spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% 
+  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))
+require(pander)
+pandoc.table(  select(pow_TD1,Side,spMeta,MeanSp,c(4:8)),style="grid",split.tables=Inf)
+
+plotPow_MeanSp_side(pow_TD1)
+
+ggsave("powTD1_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)
+
+# Calculate power in fuction of replacement rate difference
+# Falta cambiar NumSp por 
+#comp_TD1$spMeta <- ceiling(as.numeric(comp_TD1$NumSp)*1.33)
+
+pow_TD1 <- pow_TD1 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))
+
+comp_TD1 <- comp_TD1 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
+  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))
+
+plotPow_MeanSp_difR(comp_TD1)
+ggsave("powTD1_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+```
+
+The power of D1 in combination with a T-test is relatively low with a maximun of 0.6 for
+
+```{r power_PlotGC, eval=F,echo=F,message=T,warning=T}
+
+#pow_GC1 <-merge(pow_GC1,unique(pow_ADq10[,1:3]),by.x=c(1,2),by.y=c(1,2),all.y=F)[,c(1:2,10,4:9)]
+#names(pow_GC1)[3]<- "MeanSp"
+require(dplyr)
+
+pow_GC1 <- pow_GC1 %>% select(-MeanSp) %>% 
+  mutate(spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% 
+  left_join(unique(pow_ADq24[,1:3]),by=c("Side","NumSp")) %>%
+  select(Side,spMeta,MeanSp,c(4:8))
+
+require(pander)
+pandoc.table(pow_GC1,style="grid",split.tables=Inf)
+
+plotPow_MeanSp_side(pow_GC1)
+
+ggsave("powGC_spMeta_Side.png", width=6,height=6,units="in",dpi=600)
+
+plotPow_MeanSp_difR(comp_GC1)
+
+ggsave("powGC_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+```
+
+```{r power_PlotADq10, eval=F,echo=F,message=T,warning=T}
+
+#pow_GC1 <-merge(pow_GC1,unique(pow_ADq10[,1:3]),by.x=c(1,2),by.y=c(1,2),all.y=F)[,c(1:2,10,4:9)]
+#names(pow_GC1)[3]<- "MeanSp"
+
+plotPow_MeanSp_side(pow_ADq10)
+
+ggsave("powADq10_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)
+
+## ADD ANOTHER COLUM WITH MEANSP
+require(dplyr)
+# DONE! in .RData
+#
+#pow_ADq10 <- pow_ADq10 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))
+#
+#
+#comp_ADq10 <- comp_ADq10 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
+#  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))
+
+plotPow_MeanSp_difR(comp_ADq10)
+
+ggsave("powADq10_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+
+require(pander)
+pandoc.table( mutate(pow_ADq10 ,spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% select(Side,spMeta,MeanSp,c(5:9))
+,style="grid",split.tables=Inf,round=4)
+```

### 2014-10-28 SP_simul.Rmd
Add paper figures & tables

@@
 
-```{r simul_z1, eval=F,echo=F,message=F,warning=F}
+```{r simul_z1, eval=T,echo=F,message=F,warning=F}
 setwd("Simul")
 
-DqF <- compMethods_UniformSAD(8,256)
+DqF <- compMethods_UniformSAD(8,256)$Dq
 
-DqF <- rbind(DqF,compMethods_UniformSAD(64,256))
+DqF <- rbind(DqF,compMethods_UniformSAD(64,256)$Dq)
 
-DqF <- rbind(DqF,compMethods_UniformSAD(256,256))
+DqF <- rbind(DqF,compMethods_UniformSAD(256,256)$Dq)
 
@@
 #plotDq(Dq3,"Type")
-
+require(pander)
 pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")
@@
 
+DqF <- rbind(DqF,compMethods_UniformSAD(8,512))
+
 DqF <- rbind(DqF,compMethods_UniformSAD(64,512))
+
+DqF <- rbind(DqF,compMethods_UniformSAD(256,512))
 
@@
 Thus DqSAD works in the range 2-8 2-16 2-32 depending on the number of species
+
+For different number of species and different sides the same cualitative patterns are observed.
 
@@
 setwd(oldcd)
-rm(Dq1,Dq2,spa)
+save.image()
 
@@
 
-```{r test_SAD256, eval=T,echo=F,message=F,warning=F}
+```{r test_SAD256, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 
-```{r power_adtest, eval=T,echo=F,message=F,warning=F}
+```{r power_adtest, eval=F,echo=F,message=F,warning=F}
 # Check all simulations are present
@@
 
-```{r power_adtest, eval=T,echo=F,message=F,warning=F}
+```{r power_adtest, eval=F,echo=F,message=F,warning=F}
 
@@
 ```
+
+## Plots for publication uniform SAD
+
+```{r plots_spDq, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
+
+# Plot of the uniform and randomized spatial pattern for a uniform SAD with 64 species and side=256
+#
+
+g <- plotSAD_SpatPat(64,256,"U")
+g 
+setwd("..")
+ggsave("spat_Unif64_256.png", width=8,height=6,units="in",dpi=600)
+setwd("Simul")
+
+#
+# Plots of Dq with uniform SAD and 20 repetitions!
+#
+unique(DqT$SAD)
+#DqT$Type[DqT$Type=="SRS"] <- "DqSRS"
+#DqT$Type[DqT$Type=="rnzSRS"] <- "rnzDqSRS"
+
+rm(Dq1,Dq2,fname,fname1)
+
+g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
+g
+setwd("..")
+ggsave("Dq_Unif64_256.png", width=8,height=4,units="in",dpi=600)
+
+g <- plotDq_Side_Sp(DqT,256,0,"Uniform")
+g
+ggsave("Dq_Unif_NumSp_256.png", width=8,height=6,units="in",dpi=600)
+
+g <- plotDq_Side_Sp(DqT,512,0,"Uniform")
+g
+ggsave("Dq_Unif_NumSp_512.png", width=8,height=6,units="in",dpi=600)
+
+#
+# Plot R2 for dqSAD dqSRS
+#
+g <- plotR2Dq_Side_Sp(DqT,256,64,"Uniform")
+g
+ggsave("R2Dq_Unif_64_256.png", width=8,height=6,units="in",dpi=600)
+
+g <- plotR2Dq_Side_Sp(DqT,0,0,"Uniform")
+g
+ggsave("R2Dq_Unif_NumSp_Side.png", width=8,height=6,units="in",dpi=600)
+
+#
+# Generate Tables with R2 proportions
+#
+require(dplyr)
+hh <-function(x,c,...){
+  length(x[x>c])/length(x)
+}
+
+Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform",Side==256,NumSp==8,Type=="DqSAD")
+
+Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform") %>%
+  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Random","Regular")) %>%
+  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
+  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))
+
+write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
+
+#
+# The same for neutral simulations with logseries metacommunity 
+#
+
+Dq1 <- filter(DqT, SAD=="Neutral" | SAD=="NeuUnif") %>%
+  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Randomized","Unmodified")) %>%
+  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
+  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))
+
+names(SadT)
+Sad1 <- filter(SadT, SAD=="Neutral") %>%
+  group_by(Type,Side,NumSp,SAD,rep) %>% summarize(NumSpAct=n()) %>% summarize(meanNumSp=mean(NumSpAct),rangeSp=paste(range(NumSpAct),collapse="-"))
+
+# Merge Sad1 with Dq1 for meanNumSp
+unique(Sad1$Type)
+unique(Dq1$DqType)
+Dq1 <- inner_join(Dq1,Sad1) %>% select(SAD, meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
+pow <- distinct(select(pow_ADq24,NumSp,spMeta))
+
+Dq1 <- left_join(Dq1,pow)  %>% 
+    select(SAD, spMeta,meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
+names(Dq1)
+write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
+
+rm(Dq1,Sad1,pow)
+
+#
+# plot of the Fit of the method for Dq
+#
+
+setwd("Simul")
+
+zq <- readDq_fit(256,64,"Uniform")
+g <- plotDqFitG(zq)
+g
+setwd(oldcd)
+ggsave("DqFit_Unif_64_256.png", width=8,height=6,units="in",dpi=600)
+
+g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))
+g
+
+```
+
+## Plots for publication Logseries SAD
+
+```{r plots_logser_spDq, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
+
+# Plot of the uniform and randomized spatial pattern for a logseries SAD with 64 species and side=256
+#
+
+#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! GENERA MAL 
+# save_matrix_as_sed
+# 
+# Le falta un \n
+
+g <- plotSAD_SpatPat(64,256,"L")
+g 
+setwd("..")
+ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)
+
+unique(DqT$SAD)
+
+g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
+g
+ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)
+
+g <- plotDq_Side_Sp(DqT,256,0,"Logseries")
+g
+ggsave("Dq_Logser_NumSp_256.png", width=8,height=6,units="in",dpi=600)
+
+g <- plotDq_Side_Sp(DqT,512,0,"Logseries")
+g
+ggsave("Dq_Logser_NumSp_512.png", width=8,height=6,units="in",dpi=600)
+
+#
+# Plot R2 for dqSAD dqSRS
+#
+g <- plotR2Dq_Side_Sp(DqT,256,64,"Logseries")
+g
+ggsave("R2Dq_Logser_64_256.png", width=8,height=6,units="in",dpi=600)
+
+g <- plotR2Dq_Side_Sp(DqT,0,0,"Logseries")
+g
+
+#
+# plot of the Fit of the method for Dq
+#
+
+setwd("Simul")
+
+zq <- readDq_fit(256,64,"Logseries")
+g <-plotDqFitG(zq)
+g
+setwd(oldcd)
+ggsave("DqFit_Logser_64_256.png", width=8,height=6,units="in",dpi=600)

### 2014-10-28 R/Neutral_fun.r

@@ -586,8 +586,19 @@ compMethods_Time <- function(bName,Time,spMeta)
 #
 read_sed <- function(fname)
 {
+  d <-read.table(fname, nrows=1,header=F)
   per <-data.matrix(read.table(fname, skip=2,header=F))
+  if(d$V2!=nrow(per)) stop("Incorrect formated sed file")
+  return(per)
 }
+
+read_sed2xy <- function(fname)
+{
+  spa <- read_sed(fname)
+  z <- 1:(nrow(spa)*ncol(spa))
+  zpa <- data.frame(v=spa[z],x=trunc(z/ncol(spa)),y=1:nrow(spa))
+}
+
 
 # Function to plot Dq fit from t* files generated by mfSBA 
 # 
@@ -622,6 +633,64 @@ plotDqFit <- function(fname,qname)
 #  dev.off()    
 }
 
+# Read information of the fit of Dq (Zq) from t.file and q file
+# Return a data.frame in long format
+#
+readZq <- function(fname,qname)
+{
+  zq <- read.table(fname, sep="\t",header=T)
+  cna <- read_sed(qname)
+  q <-t(cna)
+  zq0 <- reshape(zq, timevar="q",times=q,v.names=c("logTr"),
+                 varying=list(3:length(names(zq))),
+                 direction="long")
+}
+
+# Function to plot Dq fit from t* files generated by mfSBA using ggplot2
+# 
+# zq0: data.frame with Zq, logTr 
+# fac: factor to separate the lines 
+#
+plotDqFitG <- function(zq0,fac=3)
+{
+  require(ggplot2)
+  require(dplyr)
+  
+  zq1 <- subset(zq0, q==1 | q==2 | q==3 | q==4 | q==5 | q==0 | q==-1 | q==-2 | q==-3 | q==-4 | q==-5 )
+  zq1$logTr <- zq1$logTr+zq1$q/fac
+  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), Type=ifelse(grepl("rnz",Type),"Random","Regular"))
+  
+#  g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q))) + 
+#    scale_color_discrete(name="q") + 
+  
[…]

### 2014-11-05 SP_simul.Rmd
Update abstract manuscript up to results and figure 1-2

@@
 
-## Plots for publication uniform SAD
+## Plots for publication uniform/Logseries SAD
 
@@
 
-# Plot of the uniform and randomized spatial pattern for a uniform SAD with 64 species and side=256
+# Plot of the Regular and Randomized spatial pattern for a uniform & Logseries SAD with 64 species and side=256
 #
+g <- plotSAD_SpatPat(64,256,"B")
+g
 
-g <- plotSAD_SpatPat(64,256,"U")
-g 
+#g <- plotSAD_SpatPat(64,256,"U")
+#g 
 setwd("..")
-ggsave("spat_Unif64_256.png", width=8,height=6,units="in",dpi=600)
+ggsave("spat_UniLog64_256.png", width=8,height=6,units="in",dpi=600)
 setwd("Simul")
@@
 #
-# Plots of Dq with uniform SAD and 20 repetitions!
+# Plots of Dq with uniform/Logseries SAD and 10 repetitions!
 #
 unique(DqT$SAD)
-#DqT$Type[DqT$Type=="SRS"] <- "DqSRS"
-#DqT$Type[DqT$Type=="rnzSRS"] <- "rnzDqSRS"
 
-rm(Dq1,Dq2,fname,fname1)
-
-g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
+g <- plotDq_Side_Sp(DqT,256,64,"B")
 g
 setwd("..")
-ggsave("Dq_Unif64_256.png", width=8,height=4,units="in",dpi=600)
+ggsave("Dq_UniLog64_256.png", width=8,height=6,units="in",dpi=600)
+
+g <- plotDq_Side_Sp(DqT,256,0,"B")
+g
+ggsave("Dq_UniLog_NumSp_256.png", width=8,height=6,units="in",dpi=600)
+
+#g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
+#g
 
@@
 #
-# Plot R2 for dqSAD dqSRS
+# Plot R2 for dqSAD dqSRS for uniform & Logseries
 #
+g <- plotR2Dq_Side_Sp(DqT,256,64,"B") 
+g
+ggsave("R2Dq_UniLog_64_256.png", width=8,height=6,units="in",dpi=600)
+
 g <- plotR2Dq_Side_Sp(DqT,256,64,"Uniform")
 g
-ggsave("R2Dq_Unif_64_256.png", width=8,height=6,units="in",dpi=600)
 
@@
 
-#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! GENERA MAL 
-# save_matrix_as_sed
-# 
-# Le falta un \n
+#g <- plotSAD_SpatPat(64,256,"L")
+#g 
+#setwd("..")
+#ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)
 
-g <- plotSAD_SpatPat(64,256,"L")
-g 
-setwd("..")
-ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)
+#unique(DqT$SAD)
 
-unique(DqT$SAD)
-
-g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
-g
-ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)
+#g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
+#g
+#ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)
 
@@
 #
-g <- plotR2Dq_Side_Sp(DqT,256,64,"Logseries")
-g
-ggsave("R2Dq_Logser_64_256.png", width=8,height=6,units="in",dpi=600)
+#g <- plotR2Dq_Side_Sp(DqT,256,64,"Logseries")
+#g
+#ggsave("R2Dq_Logser_64_256.png", width=8,height=6,units="in",dpi=600)
 
 g <- plotR2Dq_Side_Sp(DqT,0,0,"Logseries")
+g
+
+g <- plotR2Dq_Side_Sp(DqT,0,0,"Neutral")
 g

### 2014-11-05 R/ExtractDuplicatedSimul.r

@@ -1,0 +1,21 @@
+
+require(dplyr)
+
+Dq1 <- group_by(DqT,Type,Side,NumSp,SAD) %>% summarize(count=n())
+
+Dq1 <- filter(DqT, SAD=="Uniform",Side==256) %>% group_by(Type,Side,NumSp,SAD) %>% summarize(count=n())
+
+Dq1 <- filter(DqT, SAD=="Uniform",Side==256,NumSp==64) %>% group_by(Type,Side,NumSp,SAD,rep) %>% summarize(count=n())
+
+Dq1 <- filter(DqT, SAD=="Uniform",Side==256,NumSp==64) 
+Dq3 <- distinct(Dq1,Type,Side,NumSp,SAD,rep,q)
+
+Dq2 <- filter(DqT, !(SAD=="Uniform" & Side==256 & NumSp==64)) 
+DqT1 <-rbind(Dq2,Dq3)  
+
+Dq1 <- group_by(DqT1,Type,Side,NumSp,SAD) %>% summarize(count=n())
+
+DqT_bak <- DqT
+DqT <- DqT1
+rm(Dq1,Dq2,Dq3,DqT1)
+save.image()

### 2014-11-05 R/Neutral_fun.r

@@ -588,7 +588,7 @@ read_sed <- function(fname)
 {
   d <-read.table(fname, nrows=1,header=F)
   per <-data.matrix(read.table(fname, skip=2,header=F))
-  if(d$V2!=nrow(per)) stop("Incorrect formated sed file")
+  if(d$V2!=nrow(per)) stop(paste("Incorrect formated sed file:",fname))
   return(per)
 }
 
@@ -658,7 +658,7 @@ plotDqFitG <- function(zq0,fac=3)
   
   zq1 <- subset(zq0, q==1 | q==2 | q==3 | q==4 | q==5 | q==0 | q==-1 | q==-2 | q==-3 | q==-4 | q==-5 )
   zq1$logTr <- zq1$logTr+zq1$q/fac
-  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), Type=ifelse(grepl("rnz",Type),"Random","Regular"))
+  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), Type=ifelse(grepl("rnz",Type),"b) Randomized","a) Regular"))
   
 #  g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q))) + 
 #    scale_color_discrete(name="q") + 
@@ -679,7 +679,7 @@ plotDqFitGQ <- function(zq0,qq,fac=3)
   
   zq1 <- filter(zq0, q %in% qq  )
   zq1$logTr <- zq1$logTr+zq1$q/fac
-  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), Type=ifelse(grepl("rnz",Type),"Random","Regular"))
+  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), Type=ifelse(grepl("rnz",Type),"b) Randomized","a) Regular"))
   
   #  g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q))) + 
   #    scale_color_discrete(name="q") + 
@@ -2094,7 +2094,7 @@ plotPow_MeanSp_difR <- function(comp)
 # side: side of the image
 #
 plotSAD_SpatPat<-function(nsp,side,type="U")
-  {
+{
   require(ggplot2)
   #nsp<-64
[…]

### 2014-11-10 SP_simul.Rmd
Finsh the spatial pattern results and figures

@@
 #
-unique(DqT$SAD)
-
-g <- plotDq_Side_Sp(DqT,256,64,"B")
-g
 setwd("..")
-ggsave("Dq_UniLog64_256.png", width=8,height=6,units="in",dpi=600)
 
@@
 g
-ggsave("Dq_UniLog_NumSp_256.png", width=8,height=6,units="in",dpi=600)
+ggsave("Dq_UniLog_NumSp_256.png", width=8,height=8,units="in",dpi=600)
 
-#g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
-#g
-
-g <- plotDq_Side_Sp(DqT,256,0,"Uniform")
+g <- plotDq_Side_Sp(DqT,512,0,"B")
 g
-ggsave("Dq_Unif_NumSp_256.png", width=8,height=6,units="in",dpi=600)
-
-g <- plotDq_Side_Sp(DqT,512,0,"Uniform")
-g
-ggsave("Dq_Unif_NumSp_512.png", width=8,height=6,units="in",dpi=600)
+ggsave("Dq_UniLog_NumSp_512.png", width=8,height=8,units="in",dpi=600)
 
@@
 
-g <- plotR2Dq_Side_Sp(DqT,256,64,"Uniform")
-g
-
 g <- plotR2Dq_Side_Sp(DqT,0,0,"Uniform")
@@
 ggsave("R2Dq_Unif_NumSp_Side.png", width=8,height=6,units="in",dpi=600)
-
-#
-# Generate Tables with R2 proportions
-#
-require(dplyr)
-hh <-function(x,c,...){
-  length(x[x>c])/length(x)
-}
-
-Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform",Side==256,NumSp==8,Type=="DqSAD")
-
-Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform") %>%
-  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Random","Regular")) %>%
-  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
-  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))
-
-write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
-
-#
-# The same for neutral simulations with logseries metacommunity 
-#
-
-Dq1 <- filter(DqT, SAD=="Neutral" | SAD=="NeuUnif") %>%
-  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Randomized","Unmodified")) %>%
-  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
-  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))
-
-names(SadT)
-Sad1 <- filter(SadT, SAD=="Neutral") %>%
-  group_by(Type,Side,NumSp,SAD,rep) %>% summarize(NumSpAct=n()) %>% summarize(meanNumSp=mean(NumSpAct),rangeSp=paste(range(NumSpAct),collapse="-"))
-
-# Merge Sad1 with Dq1 for meanNumSp
-unique(Sad1$Type)
-unique(Dq1$DqType)
-Dq1 <- inner_join(Dq1,Sad1) %>% select(SAD, meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
-pow <- distinct(select(pow_ADq24,NumSp,spMeta))
-
-Dq1 <- left_join(Dq1,pow)  %>% 
-    select(SAD, spMeta,meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
-names(Dq1)
-write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
-
-rm(Dq1,Sad1,pow)
 
@@
 
+setwd("Simul")
+zq <- readDq_fit(256,8,"Uniform")
+g <- plotDqFitG(zq)
+g
+setwd(oldcd)
+ggsave("DqFit_Unif_8_256.png", width=8,height=6,units="in",dpi=600)
+
+setwd("Simul")
+zq <- readDq_fit(256,256,"Uniform")
+g <- plotDqFitG(zq)
+g
+setwd(oldcd)
+ggsave("DqFit_Unif_256_256.png", width=8,height=6,units="in",dpi=600)
+
 ```
@@
 ```{r plots_logser_spDq, eval=T,echo=F,message=F,warning=F}
-setwd("Simul")
-
-# Plot of the uniform and randomized spatial pattern for a logseries SAD with 64 species and side=256
-#
-
-#g <- plotSAD_SpatPat(64,256,"L")
-#g 
-#setwd("..")
-#ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)
-
-#unique(DqT$SAD)
-
-#g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
-#g
-#ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)
 
@@
 ggsave("DqFit_Logser_64_256.png", width=8,height=6,units="in",dpi=600)
+
+```
+
+## Generate Tables with R2 proportions
+
+```{r R2tbl_Dq, eval=F,echo=F,message=F,warning=F}
+
+#
+# Generate Tables with R2 proportions
+#
+require(dplyr)
+hh <-function(x,c,...){
+  length(x[x>c])/length(x)
+}
+
+Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform",Side==256,NumSp==8,Type=="DqSAD")
+
+Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform") %>%
+  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Random","Regular")) %>%
+  group_by(DqType,SAD,SpatialPattern,NumSp,Side) %>% 
+  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))
+
+write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
+
+#
+# The same for neutral simulations with logseries metacommunity 
+#
+
+Dq1 <- filter(DqT, SAD=="Neutral" | SAD=="NeuUnif") %>%
+  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Randomized","Unmodified")) %>%
+  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
+  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))
+
+names(SadT)
+Sad1 <- filter(SadT, SAD=="Neutral") %>%
+  group_by(Type,Side,NumSp,SAD,rep) %>% summarize(NumSpAct=n()) %>% summarize(meanNumSp=mean(NumSpAct),rangeSp=paste(range(NumSpAct),collapse="-"))
+
+# Merge Sad1 with Dq1 for meanNumSp
+unique(Sad1$Type)
+unique(Dq1$DqType)
+Dq1 <- inner_join(Dq1,Sad1) %>% select(SAD, meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
+pow <- distinct(select(pow_ADq24,NumSp,spMeta))
+
+Dq1 <- left_join(Dq1,pow)  %>% 
+    select(SAD, spMeta,meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
+names(Dq1)
+write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
+
+rm(Dq1,Sad1,pow)
+```

### 2014-11-10 R/Neutral_fun.r

@@ -658,7 +658,7 @@ plotDqFitG <- function(zq0,fac=3)
   
   zq1 <- subset(zq0, q==1 | q==2 | q==3 | q==4 | q==5 | q==0 | q==-1 | q==-2 | q==-3 | q==-4 | q==-5 )
   zq1$logTr <- zq1$logTr+zq1$q/fac
-  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), Type=ifelse(grepl("rnz",Type),"b) Randomized","a) Regular"))
+  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"DqSRS","DqSAD"), Type=ifelse(grepl("rnz",Type),"b) Randomized","a) Regular"))
   
 #  g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q))) + 
 #    scale_color_discrete(name="q") + 
@@ -2157,12 +2157,13 @@ plotSAD_SpatPat<-function(nsp,side,type="U")
 plotDq_Side_Sp <- function(Dqq,side,nsp,sad="Uniform"){
   require(dplyr)
   require(ggplot2)
+  require(grid)
   #mylabs <- list(bquote(D[q]^SRS),bquote(Rnz -~D[q]^SRS),bquote(D[q]^SAD),bquote(Rnz -~D[q]^SAD))
   mylabs <- list("Regular","Randomized")
   
   if(nsp!=0) {
     if(sad=="B"){
-        mylabs <- list("Regular Uniform","Randomized Uniform","Regular Logseries","Randomized Logseries" )
+        mylabs <- list("Regular\nUniform","Randomized\nUniform","Regular\nLogseries","Randomized\nLogseries" )
         Dq1<- filter(Dqq,Side==side,NumSp==nsp,SAD=="Uniform" | SAD=="Logseries")
     } else
         Dq1<- filter(Dqq,SAD==sad,Side==side,NumSp==nsp)
@@ -2184,23 +2185,23 @@ plotDq_Side_Sp <- function(Dqq,side,nsp,sad="Uniform"){
 
   } else {
     if(sad=="B") {
-        mylabs <- list("Regular Uniform","Randomized Uniform","Regular Logseries","Randomized Logseries" )
-        Dq1<- filter(Dqq,Side==side,SAD=="Uniform" | SAD=="Logseries")
[…]

### 2014-11-17 Neutral_simulPow.Rmd
Add figures of neutral spatpatt Dq & RAD

@@
 ```
+
+## Simulations to plot spatial patterns with differents replacement Rate
+
+```{r neutral_SpSimPlot256, eval=F,echo=F,message=T,warning=T}
+setwd("Simul")
+
+# meta = 64, side=250, time=500
+sad64 <- simul_NeutralSAD(64,256,500)
+
+# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
+#
+g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1))
+g
+
+setwd("..")
+ggsave("spat_NeuLog64_256.png", width=8,height=6,units="in",dpi=600)
+
+setwd("Simul")
+
+plotNeutral_Dq(64,256,500,"L",NULL) # Null use previous simulations
+
+setwd("..")
+ggsave("Dq_NeuLog64_256.png", width=8,height=4,units="in",dpi=600)
+
+### Plot Average SAD!
+setwd("Simul")
+den <- plotNeutral_SAD(0,256)
+
+setwd("..")
+ggsave("RAD_NeuLog_spMeta_256.png", width=8,height=6,units="in",dpi=600)
+
+# USAR dplyr en calcRankSAD_by (ver SP_simul 428)
+```

### 2014-11-17 R/Neutral_fun.r

@@ -92,7 +92,7 @@ calcRankSAD_by  <- function(den,vv,cols)
   hh <- function(x) { 
   x1 <- x[x[[vv]]>0,]
   x1$parms <- paste(unique(x[,cols]),collapse="_")
-  x1$Rank <- nrow(x1) - rank(x1[[vv]]) +1
+  x1$Rank <- nrow(x1) - rank(x1[[vv]],ties.method="min") +1
   return(x1)
   }
   ddply(den, cols,hh )
@@ -2279,4 +2279,245 @@ readDq_fit <- function(side,nsp,sad="U") {
   zq1 <- readZq(paste0("t.", fname1),"q.sed")
   zq1$Type <- "rnzDqSAD"
   zq<- rbind(zq,zq1)
+}
+
+
+# Plot of multiespecies spatial pattern generated with neutral model and logseries SAD
+#
+#
+plotNeutral_SpatPat<-function(nsp,side,time,meta="L",ReplRate=c(0,0.001,0.01,0.1,1))
+{
+  require(ggplot2)
+ 
+  spa <- data.frame()
+  for(i in 1:length(ReplRate)) {
+    if(toupper(meta)=="L") {
+      bname <- paste0("neuFish",nsp,"_",side,"R", ReplRate[i])
+    } else {
+      bname <- paste0("neuUnif",nsp,"_",side,"R", ReplRate[i])
+    }
+    
+    fname <- paste0(bname,"-",formatC(time,width=4,flag=0),".sed")
+    
+    sp1 <-read_sed2xy(fname)
+    sp1$Type <- paste("Replacement:", ReplRate[i])
+    sp1$Species <- paste("Species:",length(unique(sp1$v)))
+
+    spa <-  rbind(spa,sp1)
+  }
+  #lvl <- unique(spa$Type)
+  #spa$Type <- factor(spa$Type, levels = lvl)
+  
+  g <- ggplot(spa, aes(x, y, fill = factor(v))) + geom_raster(hjust = 0, vjust = 0) + 
+    theme_bw() + coord_equal() 
+  
+  g <- g + scale_fill_grey(guide=F) +
+    scale_x_continuous(expand=c(.01,.01)) + 
+    scale_y_continuous(expand=c(.01,.01)) +  
+    labs(x=NULL, y=NULL) 
+
+  g <- g + facet_wrap( ~ Type +Species,ncol=2) 
[…]

### 2014-11-28 Neutral_simulPow.Rmd
Finished results corrected abstract start with discussion

--- 2014-10-28 Neutral_simulPow.Rmd
@@
 
-## ADD ANOTHER COLUM WITH MEANSP
+require(plyr)
 require(dplyr)
@@
 
-plotPow_MeanSp_difR(comp_ADq10)
+p1 <- plotPow_MeanSp_difR(comp_ADq10)
+ggsave("powADq10_DifR_256.png", width=6,height=6,units="in",dpi=600)
 
-ggsave("powADq10_DifReplacement.png", width=6,height=6,units="in",dpi=600)
+p2 <- plotPow_MeanSp_difR(comp_ADq10,512)
+ggsave("powADq10_DifR_512.png", width=6,height=6,units="in",dpi=600)
+
+p1 <- rbind(p1,p2)
+p1 <- select(p1,Side,spMeta,Type:n) %>% arrange(Side,spMeta,Type,DifR) 
+write.table(format(p1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
+
+rm(p1,p2)
 
@@
 ```
+
+## Simulations to plot spatial patterns with different replacement Rate
+
+```{r neutral_SpSimPlot256, eval=F,echo=F,message=T,warning=T}
+setwd("Simul")
+
+# meta = 64, side=250, time=500
+sad64 <- simul_NeutralSAD(64,256,500)
+
+# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
+#
+g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1,1))
+g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1))
+g
+
+setwd("..")
+ggsave("spat_NeuLog64_256.png", width=8,height=6,units="in",dpi=600)
+
+# Plot Dq for simulations in txt files (NULL)
+#
+
+setwd("Simul")
+plotNeutral_Dq(64,256,500,"L",NULL) # Null use previous simulations 
+setwd("..")
+ggsave("Dq_NeuLog64_256.png", width=8,height=4,units="in",dpi=600)
+
+setwd("Simul")
+plotNeutral_Dq(8,256,500,"L",NULL) # Null use previous simulations 
+setwd("..")
+ggsave("Dq_NeuLog8_256.png", width=8,height=4,units="in",dpi=600)
+
+setwd("Simul")
+plotNeutral_Dq(256,256,500,"L",NULL) # Null use previous simulations 
+setwd("..")
+ggsave("Dq_NeuLog256_256.png", width=8,height=4,units="in",dpi=600)
+
+# Plot simulations for all metacommunities 
+#
+setwd("Simul")
+plotNeutral_Dq(0,256,500,"L",NULL) # Null use previous simulations 
+setwd("..")
+ggsave("Dq_NeuLog_NumSp_256.png", width=8,height=8,units="in",dpi=600)
+
+setwd("Simul")
+plotNeutral_Dq(0,512,500,"L",NULL) # Null use previous simulations 
+setwd("..")
+ggsave("Dq_NeuLog_NumSp_512.png", width=8,height=8,units="in",dpi=600)
+
+### Plot Average SAD!
+setwd("Simul")
+den <- plotNeutral_SAD(0,256)
+
+setwd("..")
+ggsave("RAD_NeuLog_spMeta_256.png", width=8,height=6,units="in",dpi=600)
+
+# Create table with R2 of neutral models Dq
+#
+
+setwd("Simul")
+Dqq <- R2Neutral_Dq(256)
+Dqq <- rbind(Dqq,R2Neutral_Dq(512))
+
+Dqq <- arrange(Dqq,DqType,Side,spMeta,ReplacementRate,Freq60,Freq90) %>% select(DqType,Side,spMeta,meanSp,ReplacementRate,Freq60,Freq90)
+
+setwd("..")
+
+#write.table(format(Dqq,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
+
+require(pander)
+pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)
+
+# Table with mean number of species by replacement rate
+#
+Dqq <- select(Dqq,Side,spMeta,ReplacementRate,meanSp)
+
+#write.table(format(Dqq,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
+pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)
+
+rm(Dqq,Dqq1)
+```

### 2014-11-28 R/Neutral_fun.r

@@ -2053,7 +2053,7 @@ plotPow_MeanSp_side <- function(pow){
 
 }
 
-plotPow_MeanSp_difR <- function(comp)
+plotPow_MeanSp_difR <- function(comp,side=256)
 {
   require(ggplot2)
   # Recalculate power from comp_AD
@@ -2069,23 +2069,28 @@ plotPow_MeanSp_difR <- function(comp)
   # Calculate power in fuction of replacement rate difference
   #comp$spMeta <- ceiling(as.numeric(comp$NumSp)*1.33)
 
-  c1 <- with(comp,comp[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
+  c1 <- with(comp,comp[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1 & Side==side,])
   c1$DifR <- with(c1,abs(RplR2-RplR1))
 
-  c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
+  c2 <- ddply(c1,.(Side,NumSp,Type,DifR),hh)
+  c2$spMeta <- ceiling(as.numeric(c2$NumSp)*1.33)
 
-  g <- ggplot(c2,aes(x=DifR,y=power)) + 
-    geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + 
-    facet_grid( mean_sp ~ .) +
+  g <- ggplot(c2,aes(x=as.factor(DifR),y=power)) + 
+#    geom_point(shape=19,position = position_jitter(height = .01),aes(colour=as.factor(Type))) + 
+    geom_point(aes(shape=as.factor(Type))) + 
+    facet_grid( spMeta ~ .) +
     ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
-    xlab(bquote(Delta ~"Replacement rate")) +
-    scale_size_continuous(name="Type I error") +
-    scale_colour_discrete(name="") 
+    xlab(bquote(Delta ~"Replacement")) +
+    scale_shape_manual(values=c(21,24,4,25,3,8),guide=guide_legend(title="")) 
+#    scale_size_continuous(name="Type I error") +
+#    scale_colour_discrete(name="") 
 
[…]

### 2014-12-02 Neutral_simulPow.Rmd
Finishing conclusion

@@
 #
-g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1,1))
-g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1))
+g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
+g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
 g

### 2014-12-24 Neutral_simulPow.Rmd
minor corrections sent to peerj preprints
Add color figures

@@
 # Multifractal analysis of multispecies spatial distributions - Model simulations
+
+I use here the following neutral model with exponential dispersion:
+
+<https://github.com/lsaravia/Neutral>
 
@@
 #
-g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
+#g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
 g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
@@
 setwd("Simul")
+detach("package:dplyr", unload=TRUE)
 den <- plotNeutral_SAD(0,256)

### 2014-12-24 SP_simul.Rmd
Add figures of neutral spatpatt Dq & RAD
minor corrections sent to peerj preprints
Add color figures

@@
 # Multifractal analysis of multispecies spatial distributions - Spatial patterns simulations
+
+I use mfSBA for multifractal estimation: <https://github.com/lsaravia/mfsba>
 
@@
 
+setwd("Simul")
+
+zq <- readDq_fit(256,8,"Logseries")
+g <-plotDqFitG(zq)
+g
+setwd(oldcd)
+ggsave("DqFit_Logser_8_256.png", width=8,height=6,units="in",dpi=600)
+
+setwd("Simul")
+zq <- readDq_fit(256,256,"Logseries")
+g <-plotDqFitG(zq)
+g
+setwd(oldcd)
+ggsave("DqFit_Logser_256_256.png", width=8,height=6,units="in",dpi=600)
+
 ```

### 2014-12-24 R/Neutral_fun.r

@@ -662,11 +662,14 @@ plotDqFitG <- function(zq0,fac=3)
   
 #  g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q))) + 
 #    scale_color_discrete(name="q") + 
+#    
   
-  g <- ggplot(zq1,aes(LogBox,logTr,shape=factor(q))) + geom_point(aes(shape=factor(q)),size=1) + 
-      geom_smooth(method="lm",se=F,colour="grey")  +
-      scale_shape_manual(values=c(0,1,2,3,4,5,6,8,15,16,17,21:24),name="q") +
-      ylab(expression(italic(paste("log ",  Z[q](epsilon) )))) + theme_bw() +
+#  g <- ggplot(zq1,aes(LogBox,logTr,shape=factor(q))) + geom_point(aes(shape=factor(q)),size=1) + 
+  g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q)),size=1) + 
+      geom_smooth(method="lm",se=F)  
+  g <- g + scale_shape_manual(values=c(0,1,2,3,4,5,6,8,15,16,17,21:24),name="q") 
+  g <- g + scale_colour_brewer(palette="Set1",name="q")
+  g <- g + ylab(expression(italic(paste("log ",  Z[q](epsilon) )))) + theme_bw() +
       xlab(expression(italic(paste("log ",epsilon))))+
     facet_wrap(Type ~ DqType, scales="free")
 }
@@ -2077,13 +2080,17 @@ plotPow_MeanSp_difR <- function(comp,side=256)
 
   g <- ggplot(c2,aes(x=as.factor(DifR),y=power)) + 
 #    geom_point(shape=19,position = position_jitter(height = .01),aes(colour=as.factor(Type))) + 
-    geom_point(aes(shape=as.factor(Type))) + 
+    geom_point(aes(shape=as.factor(Type),colour=factor(Type))) + 
     facet_grid( spMeta ~ .) +
     ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
     xlab(bquote(Delta ~"Replacement")) +
     scale_shape_manual(values=c(21,24,4,25,3,8),guide=guide_legend(title="")) 
 #    scale_size_continuous(name="Type I error") +
[…]

### 2015-02-23 R/Neutral_fun.r
Start MEE revision

@@ -1445,6 +1445,9 @@ calcPower_AD <- function(Dqq,Sad,nsp,side){
   return(pow)
 }
 
+# Simulations of the model with output of one time 
+#
+#
 simulNeutral_1Time<- function(nsp,side,time,meta="L",rep=10,delo=T)
 {
 

### 2015-02-23 R/Test_DqCompNew.r

@@ -1,0 +1,70 @@
+# Example for 
+# http://stackoverflow.com/questions/25085537/permute-groups-in-a-data-frame-r#
+#
+
+source("R/Test_Dq_fun.r")
+
+
+# Test with other data
+#
+setwd("Simul")
+bName <- "neuFish65_256"
+Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
+
+plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
+
+
+# Compare replacementRate = 1 and 0.1 
+#
+require(plyr)
+require(dplyr)
+
+Dqq <- filter(Dq1,MortalityRate==0.2,DispersalDistance==0.04,ColonizationRate==0.0001,
+              ReplacementRate==1 | ReplacementRate==0.1, q<11 & q>-11)
+names(Dqq)
+
+# Add repetitions
+
+simbyrep <- nrow(Dqq)/3
+
+Dqq$rep <- rep( 1:3,each=simbyrep)
+
+plotDq(Dqq,"as.factor(paste(ReplacementRate,rep))")
+
+
+adt <- pairwiseAD_Dif(Dqq,"Dq",Dqq[,c(4,10)])
+adt
+
+
+# # Compare using permutations
+# #
+# require(kSamples)
+# ks <- ad.test(list(Dqq$Dq[1:35],Dqq$Dq[36:70]),method="simulated",Nsim=10000)
+# ks
+
+require(reshape2)
+Dq2<- dcast(Dqq,ReplacementRate+rep~q,value.var="Dq")
+require(statmod)
+compareTwoGrowthCurves(Dq2$ReplacementRate,Dq2[,3:ncol(Dq2)],nsim=1000)
+
+# Compare ReplacementRate 1 and 0.01
+
+Dqq <- filter(Dq1,MortalityRate==0.2,DispersalDistance==0.04,ColonizationRate==0.0001,
+              ReplacementRate==1 | ReplacementRate==0.01, q<11 & q>-11)
+
+simbyrep <- nrow(Dqq)/3
+
+Dqq$rep <- rep( 1:3,each=simbyrep)
+
+plotDq(Dqq,"as.factor(paste(ReplacementRate,rep))")
+
+
+adt <- pairwiseAD_Dif(Dqq,"Dq",Dqq[,c(4,10)])
+adt
+
[…]

### 2015-02-25 ResponseToReviewers.md
Update reviewer 1 specific comments #1 #2 - Reviewer 2 #3 #4 #5 #6

# Reviewers comments

Associate Editor Comments to Author:

Associate Editor
Comments to the Author:
After reading the manuscript and the comments of the two reviewers I think that this approach has high potential but that the work needs some considerable improvements as well. in addition to the comments by the reviewers I suggest to take care of the following:
- In the beginning, I had some difficulties to follow which different metrics were actually tested against each other in the end and what different information they give us about the patterns and how we could interpret them in ecological terms. There is some text abut this in the beginning of the result section but this is much too late (and to me also an odd place to put this info). I would suggest that this is made clearer early on and maybe it would be good to add a table that lists the indices together with their ecological meaning.
- It should be stated early on in which situations and for which questions this method can be used and it should be highlighted somewhere what assumptions need to be tested to apply it
- Finally, please make sure that color-blind (e.g. red-green) people can understand your figures.

Reviewer(s)' Comments to Author:

Reviewer: 1

Comments to the Corresponding Author
The author proposes new macroecological metrics – species rank surface (SRS) and generalized dimensions spectrum DqSRS, which is the result of SRS multifractal analysis. New metrics are compared with the classical rank abundance distribution (RAD) and the spectrum of generalized dimensions DqSAD, which reflects the scaling of species abundance distribution (SAD). To demonstrate the possibilities of new metrics, author uses a simple toy model and a more realistic dynamic model of community. Author also has developed a procedure for statistical comparison of RAD, DqSRS and DqSAD for the latter model. This procedure is applied to detect differences between communities with varying degrees of neutrality as well as to demonstrate the differences in power between the metrics.
I highly appreciate the new method of analysis and consider it as having high potential. However, the current manuscript is not suitable for publication. The main drawbacks:
1. The author offers no meaningful interpretation of dimensions DqSRS, restricting discussion to statements that dimension for large negative q reflect the distribution of rare species, and dimensions for large positive q reflect the distribution of the dominant species. Such lack of interpretation leads to that the new metric is used rather as a "black box", which can or cannot distinguish the communities.
2. Toy examples are chosen poorly. I cannot imagine a community consisting of linear clusters of species ordered by their overall abundance.
3. Statistical procedure used for comparison of spectra is very unconventional and raises suspicions in its correctness. For comparison between a pair of two-dimensional curves author uses Anderson-Darling test, which is designed to compare the empirical distribution functions of two samples of one-dimensional random variables, samples must consist of independent observations. From the point of view of Anderson-Darling test the generalized dimensions spectrum Dq is a bimodal distribution with modes at D_-inf and D_+inf and relatively homogeneous distribution between them. Consequently, what is compared by Anderson-Darling test is just a position of the minimum and maximum of spectra. Obviously, this is not a procedure that is needed for spectra comparison. I did not encountered the procedure for the statistical comparison of the generalized dimensions spectra. If the author intends to develop such a procedure, its description and justification must be given with a stronger consideration.
4. The spectrum of generalized dimensions reflects the spatial scaling of some measure. The use of multifractal analysis implies self-similarity of the studied object, which manifests itself in the power-law form of dependence of partition function Zq on scale. Analysis of the relationship Zq (A) must precede any further analysis. If there is no power-law scaling, the object is not self-similar and its fractal analysis makes no sense. The power law looks like a linear function on a logarithmic scale. The author uses the coefficient of determination R^2 for the analysis of linearity. 
# R^2 is not a measure of linearity, it reflects only the scatter of points around the regression line. The proposed rule of thumb was not justified. 
The author shows figure with Zq(A) scaling only for toy models but not for dynamical models, whereas it is well-studied for neutral models that their species-area relations is triphasic with power law in a narrow range of scales. It is not clear whether there is power-law scaling for dynamical model in studied range of scales.
I believe that the current version of manuscript requires serious improvement and at this stage must be rejected and resubmitted.

More specific comments and suggestions:

#1. In the description of generalized dimensions spectra it is better to introduce two types (DqSRS and DqSAD) immediately to avoid confusion in formulas 2 and 5. It is better to use notation D1 in formula 3. Formula 5 must specify explicitly that Zq is an average over plots of area A.

#2. In the description of SRS details of the algorithm of assigning ranks to equally abundant species must be specified. I think that various options (random assignment of consecutive ranks or assignment of the same  average rank) will have a strong impact on the shape of DqSRS spectrum, especially for negative q. This aspect needs special consideration.

3. In the description of dynamic model (at least in Appendix) the following details must be specified: the boundary conditions, the type of lattice update (synchronous / asynchronous), the algorithm of assignment of competitive ranks in metacommunity. It is also necessary to raise the issue of the model dynamics stationarity, I propose to provide some figures of dynamics of several structural indicators (at least in the appendix).
4. D_0^SRS is not a fractal dimension of SRS (p. 9, l. 20). SRS is a rugged surface and its dimension is more than 2 but less than 3. What is really analyzed is some measure distributed over two-dimensional support. D_0^SRS is a dimension of this support.
5. The degree of difference between Dq spectra is not a direct function of Delta rho. It is not correct to analyze relation of power to Delta rho. For example, the great drop in power of DqSAD in Fig. 8 is associated exclusively with the fact that the point Delta rho = 0.9 corresponds to the comparison of simulations rho = 1 vs rho = 0.9, which has very similar spectra.
6. The power of methods based on spectra of indices is compared with power of methods based on single components of spectra. It is obvious that the latter will be less powerful. But those methods use different statistical procedures so its direct comparison is not fully correct.
7. Figures 1 and 5 lacks color scheme, making them difficult to read.
8. Figure 3 has different scales for DqSAD и DqSRS, making it difficult to compare. As A = epsilon^2 I recommend to use A in both cases.
9. RAD is a strictly nonincreasing sequence, but many curves at figure 6 lack this property.

Reviewer: 2

Comments to the Corresponding Author
Any description of biodiversity that does not explicitly include species abundance distributions (SADs) is  likely to miss important relationships on how species interact with the environment. This is one of the rarest publications in the area of SAD modelling in which author(s) performed an elegant study investigating the scaling of SAD.
The author introduces and innovative framework,  “the species rank surfaces (SRS)”, as a new way to study the scaling of SAD.
Some comments for improvement:
1)      In the Discussion the author should also highlight the limitations of their modelling process, in particular the fact that it not takes into account: a) asymmetry of the dispersal ability of species; b) the fact that trophic structure and species interactions in communities  may lead to more idiosyncratic processes of community assembly; c) the fact  that the truncated log-normal SAD was not tested.
2)      The following paper could be cited in line 7 of page 1: Triantis, K.A., Guilhaumon, F. & Whittaker, R.J. (2012). The island species–area relationship: biology and statistics. Journal of Biogeography, 39: 215-23.
#3)      In line 24 of page 1 it seems that one additional reference is missing afer Yakimove et al., 2008)
#4)      In page 14 line 23 “comparable” should be “comparable”
#5)      The author also should revise the English of the text.
#The bibliographic references are a Chaos! The same reference appears in the text in different formats (e.g. Borda-de-Água (2012) and the same correctly as Borda-de-Água et al. (2012). All the bibliographic references should be revised for consistency both in main text and List of Bibliography.
#6)      In the reference list for some strange reason all appear with "et al." in the end. I think that the author should learn to use the tools in Latex (see http://jabref.sourceforge.net/; http://en.wikibooks.org/wiki/LaTeX/Bibliography_Management
For instance the reference below is a book Chapter:
Borda-de-Água, L., Hubbell, S.P. & He, F.et al. (2007). Scaling biodiversity under neutrality. Scaling 3 biodiversity, 347–375
and should be more correctly:
Borda-de-Água, L., Hubbell, S. P., & He, F. (2007). Scaling biodiversity under neutrality. In: Storch, D., Marquet, P. A., & Brown. J. H. (eds), Scaling biodiversity. Cambridge University Press, Cambridge, 347-375

 My best regards to the author,

Paulo A. V. Borges
Azorean Biodiversity Group
University of Azores

# Response to reviewers

DqSRS is the scaling of the ranks of species in space, as the ranks have the exact position of a species in space the result is different from DqSAD.

Statistical procedure:

- I use the k-sample Anderson Darling (1987) rank test and thus it makes no parametric assumption. It test the hypothesis that k independent samples comes from a common unespecified distribution. Thus I assume that the Dq spectrum comes from an univariate distribution, is not clear which could be the parameters from such distribution but as the test is non-parametric is reasonable to use this test for Dq spectra. As the samples are discrete and there is a posibility of ties I calculate the p-values using randomization. The advantage of the AD test is that I can use the same test for SAD and Dq.

The Dq spectrum is not an univariate distribution neither, as the test is non-parametric and the significance is calculated by randomization I argue that is reasonable to use the test to compare the curves produced by Dq, I made simulations to check this assumption and the Scholz1987
- As I used the randomization test no assumptions about the nature of distributions are needed

 4. The D0SRS is the fractal dimension of the species' spatial distribution, which in our model simulations is always 2 because the lattice is always filled.

### 2015-02-25 R/Test_DqFit.r

@@ -1,0 +1,135 @@
+#
+# Testing the fit of Dq applying Liebovitch 1989 oscillations
+#
+
+source("R/Neutral_fun.r")
+
+setwd("Simul")
+
+zq <- readDq_fit(256,64,"Logseries")
+g <-plotDqFitG(zq)
+g
+
+# Calculate small sample corrected  AIC
+AICc <- function(mo)
+{
+  k <-attributes(logLik(mo))$df-1
+  n <-attributes(logLik(mo))$nobs
+  AIC(mo)+2*k*(k+1)/(n-k-1)
+}
+
+# Calculate AICc differences between linear an linear+quadratic models
+#
+linQuadAic <- function(y,x){
+  mod1 <- lm(y~x)
+  mod2 <- lm(y~x+I(x^2))
+  AICc(mod1)-AICc(mod2)
+}
+
+
+# Calculate AICc differences between linear an linear+periodic models (tiene problemas)
+#
+linPerAic <- function(y,x){
+  mod1 <- lm(y~x)
+  mod3 <- lm(y~x+I(sin(2*pi*x)),data=zq1)
+  
+  c1 <- round(coef(mod3)[1],4)
+  c2 <- round(coef(mod3)[2],4)
+  c3 <- round(coef(mod3)[3],4)
+  mod3 <- nls(y~a + b*x+ c*sin(2*pi*x/d),
+              data=zq1,
+              start=list(a=c1,b=c2,c=c3,d=1))
+
+  AICc(mod1)-AICc(mod3) # r2_l = mod1$r.squared 
+}
+
+
+# Compare linear and quadratic models using AICc
+#
+require(dplyr)
+aDif <- group_by(zq,Type,q) %>% summarize(AICDif=linQuadAic(logTr,LogBox))
+
+ggplot(aDif,aes(q,AICDif,colour=Type)) + geom_point() + geom_line()
+
+
+ggplot(aDif,aes(q,AICDif,shape=Type)) + geom_point()
+
+
+# Select 
+zq1 <- filter(zq,q==-1,Type=="DqSAD")
+
+# Test quadratic term
+#
+mod1 <- lm(logTr~LogBox,data=zq1)
+summary(mod1)
+coef(mod1)
+mod2 <- lm(logTr~LogBox+I(LogBox^2),data=zq1)
+summary(mod2)
[…]

### 2015-02-28 SP_simul.Rmd
Update reviewer 1 specific comments #3-#5 add colorblind palette

@@
 
-```{r test_neutralTime, eval=F,echo=F,message=F,warning=F}
+```{r test_neutralTime, eval=T,echo=F,message=F,warning=F}
 setwd("Simul")
 
-simul_NeutralPlotTime(8,256,T,500,"L")
-simul_NeutralPlotTime(64,256,T,500,"L")
-simul_NeutralPlotTime(256,256,T,500,"L")
+sml <- T
+simul <- data.frame()
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
 
-simul_NeutralPlotTime(8,512,T,500,"L")
-simul_NeutralPlotTime(64,512,T,500,"L")
-simul_NeutralPlotTime(256,512,T,500,"L")
+parms <-expand.grid(nsp=c(8,64,256),side=c(256,512),disp=0.04,migr=0.001,repl=c(0,0.001,0.01,0.1,1))
 
-simul_NeutralPlotTime(8,512,T,500,"U")
-simul_NeutralPlotTime(64,512,T,500,"U")
-simul_NeutralPlotTime(256,512,T,500,"U")
+simul <- foreach(i=1:nrow(parms),.combine='rbind') %dopar%
+{
+simul_NeutralPlotTime(parms$nsp[i],parms$side[i],parms$disp[i],
+                                           parms$migr[i],parms$repl[i],sml,500,3,"N","L")
+}
+
+#cbPal <- c("#edf8fb","#b3cde3","#8c96c6","#8856a7","#810f7c")
+cbPal <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+require(ggplot2)
+
+g <- ggplot(simul,aes(x=Time,y=H,colour=as.factor(nsp),shape=as.factor(Rep))) + 
+    geom_line() + geom_point(size=1)+
+    facet_grid(ReplacementRate ~ side ) +
+    ylab(bquote("Shannon index"))+ 
+    scale_colour_manual(values=cbPal,name="Metacomm sp")+
+    scale_shape_discrete(guide=F)
+
+print(g+theme_bw())
 
 setwd(oldcd)
+
+ggsave("neuTime_side_sp_H.png", width=8,height=6,units="in",dpi=600)
+
+g <- ggplot(simul,aes(x=Time,y=Richness,colour=as.factor(nsp),shape=as.factor(Rep))) + 
+    geom_line() + geom_point(size=1)+
+    facet_grid(ReplacementRate ~ side ) +
+    ylab(bquote("Richness"))+ 
+    scale_colour_manual(values=cbPal,name="Metacomm sp")+
+    scale_shape_discrete(guide=F)
+print(g+theme_bw())
+ggsave("neuTime_side_sp_Rich.png", width=8,height=6,units="in",dpi=600)
+
+save.image()
 
@@
 
-```{r power_adtest, eval=F,echo=F,message=F,warning=F}
+```{r power_adtest1, eval=F,echo=F,message=F,warning=F}
 # Check all simulations are present
@@
 
-```{r plots_spDq, eval=T,echo=F,message=F,warning=F}
+```{r plots_spDq, eval=F,echo=F,message=F,warning=F}
 setwd("Simul")
@@
 
-```{r plots_logser_spDq, eval=T,echo=F,message=F,warning=F}
+```{r plots_logser_spDq, eval=F,echo=F,message=F,warning=F}
 

### 2015-02-28 R/Neutral_fun.r

@@ -321,8 +321,14 @@ meltDensityOut_NT <- function(fname,num_sp){
 # Read simulation output and set variable names in wide format 
 #
 readWideDensityOut <- function(fname,num_sp){
+  if(!grepl("Density.txt",fname)) fname <- paste0(fname,"Density.txt")
   den <- read.delim(fname)
   names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")
+  names(den)[7] <- unlist(strsplit(names(den)[7],".",fixed=T))[1]
+  eTime <- (max(den$Time)/(den$Time[3]-den$Time[2]))+1
+  if(  eTime < nrow(den) ){
+    den$Rep <- rep( 1:(nrow(den)/eTime),each=eTime)
+  }
   return(den)
 }
 
@@ -1338,37 +1344,41 @@ comp_NeutralUniform <- function(nsp,side,simul=10) {
   }
 
 
-simul_NeutralPlotTime <- function(nsp,side,simul=T,time=1000,meta="L") {
+# Simulate a time series of the neutral/hierarchical model
+#
+# disp: dispersal parameter
+# migr: migration rate
+# repl: replacement rate
+# mortality fixed to 0.2
+#
+# simul: T=make simulations F=make plots
+# sims:  Number of repetitions
+# mf: calculate multifractal spectrum
+# meta: U= uniform metacommunity
+#       L= logseries metacommunity
+#
+simul_NeutralPlotTime <- function(nsp,side,disp,migr,repl,simul=T,time=1000,sims=10,mf="N",meta="U") {
   if(!exists("neuBin")) stop("Variable neuBin not set (neutral binary)")
-  if(!require(untb))  stop("Untb package not installed")
+
+  if(toupper(meta)=="L") {
+    prob <- genFisherSAD(nsp,side)
+    neuParm <- paste0("fishP",nsp,"_",side,"R", repl)
+    bname <- paste0("neuFish",nsp,"_",side,"R", repl)
+  } else {
+    prob <- rep(1/nsp,nsp)  
+    neuParm <- paste0("unifP",nsp,"_",side,"R", repl)
+    bname <- paste0("neuUnif",nsp,"_",side,"R", repl)
+  }
+  pname <- paste0("pomacR",repl,".lin")
 
   if(simul){
 
[…]

### 2015-03-10 Neutral_simulPow.Rmd
Update reviewer 1 specific comments #3-#5 add colorblind palette
Update reviewer 1 specific comments #7 #8

@@
 
-p1 <- plotPow_MeanSp_difR(comp_ADq10)
-ggsave("powADq10_DifR_256.png", width=6,height=6,units="in",dpi=600)
+#p1 <- plotPow_MeanSp_difR(comp_ADq10)
+#ggsave("powADq10_DifR_256.png", width=6,height=6,units="in",dpi=600)
 
-p2 <- plotPow_MeanSp_difR(comp_ADq10,512)
-ggsave("powADq10_DifR_512.png", width=6,height=6,units="in",dpi=600)
+p1 <- plotPow_MeanSp_RplR(comp_ADq10)
+ggsave("powADq10_RplR_256.png", width=8,height=8,units="in",dpi=600)
+
+p2 <- plotPow_MeanSp_RplR(comp_ADq10,512)
+ggsave("powADq10_RplR_512.png", width=6,height=6,units="in",dpi=600)
 
@@
 g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
-g
 
@@
 ggsave("spat_NeuLog64_256.png", width=8,height=6,units="in",dpi=600)
-
-# Plot Dq for simulations in txt files (NULL)
-#
-
-setwd("Simul")
-plotNeutral_Dq(64,256,500,"L",NULL) # Null use previous simulations 
-setwd("..")
-ggsave("Dq_NeuLog64_256.png", width=8,height=4,units="in",dpi=600)
-
-setwd("Simul")
-plotNeutral_Dq(8,256,500,"L",NULL) # Null use previous simulations 
-setwd("..")
-ggsave("Dq_NeuLog8_256.png", width=8,height=4,units="in",dpi=600)
-
-setwd("Simul")
-plotNeutral_Dq(256,256,500,"L",NULL) # Null use previous simulations 
-setwd("..")
-ggsave("Dq_NeuLog256_256.png", width=8,height=4,units="in",dpi=600)
 

### 2015-03-10 SP_simul.Rmd
Update reviewer 1 specific comments #7 #8

@@
 # Test if at time 500 the model is at steady state
+
+Here I generate figures 1 and 2 for the appendix
 
@@
 g <- plotSAD_SpatPat(64,256,"B")
-g
 
-#g <- plotSAD_SpatPat(64,256,"U")
-#g 
 setwd("..")
@@
 zq <- readDq_fit(256,64,"Uniform")
+
 g <- plotDqFitG(zq)
-g
+
 setwd(oldcd)
@@
 g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))
-g
 
@@
 g <- plotDqFitG(zq)
-g
+
 setwd(oldcd)

### 2015-03-10 R/Neutral_fun.r

@@ -664,20 +664,24 @@ plotDqFitG <- function(zq0,fac=3)
   
   zq1 <- subset(zq0, q==1 | q==2 | q==3 | q==4 | q==5 | q==0 | q==-1 | q==-2 | q==-3 | q==-4 | q==-5 )
   zq1$logTr <- zq1$logTr+zq1$q/fac
-  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"DqSRS","DqSAD"), Type=ifelse(grepl("rnz",Type),"b) Randomized","a) Regular"))
-  
+  zq1 <- mutate(zq1,DqType=ifelse(grepl("SRS",Type),"DqSRS","DqSAD"), Type=ifelse(grepl("rnz",Type),"b) Randomized","a) Regular"),
+                LogBox=ifelse(grepl("SRS",Type),LogBox,sqrt(LogBox)))  
 #  g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q))) + 
 #    scale_color_discrete(name="q") + 
 #    
   
 #  g <- ggplot(zq1,aes(LogBox,logTr,shape=factor(q))) + geom_point(aes(shape=factor(q)),size=1) + 
+  mc <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#666666")
+
   g <- ggplot(zq1,aes(LogBox,logTr,colour=factor(q))) + geom_point(aes(shape=factor(q)),size=1) + 
       geom_smooth(method="lm",se=F)  
   g <- g + scale_shape_manual(values=c(0,1,2,3,4,5,6,8,15,16,17,21:24),name="q") 
-  g <- g + scale_colour_brewer(palette="Set1",name="q")
+#  g <- g + scale_colour_brewer(palette="Set1",name="q")
+  g <- g + scale_colour_manual(values=mc,name="q")
   g <- g + ylab(expression(italic(paste("log ",  Z[q](epsilon) )))) + theme_bw() +
-      xlab(expression(italic(paste("log ",epsilon))))+
+    xlab(expression(italic(paste("log ",epsilon))))+ 
     facet_wrap(Type ~ DqType, scales="free")
+  print(g)
 }
 
 
@@ -699,6 +703,7 @@ plotDqFitGQ <- function(zq0,qq,fac=3)
[…]

### 2015-03-13 ResponseToReviewers.md
Update reviewer 1 specific comments #3-#5 add colorblind palette
Update reviewer 1 specific comments #7 #8
add test of AD stat with Dq -  reviewer 1 comment #3 about AD test

@@
 2. Toy examples are chosen poorly. I cannot imagine a community consisting of linear clusters of species ordered by their overall abundance.
-3.
+
+#3.
 Statistical procedure used for comparison of spectra is very unconventional and raises suspicions in its correctness.
@@
 If the author intends to develop such a procedure, its description and justification must be given with a stronger consideration.
+- I added an explanation of why this test can be used with Dq
+
 4.
@@
 # R^2 is not a measure of linearity, it reflects only the scatter of points around the regression line. The proposed rule of thumb was not justified.
+
 The author shows figure with Zq(A) scaling only for toy models but not for dynamical models, whereas it is well-studied for neutral models that their species-area relations is triphasic with power law in a narrow range of scales.
 It is not clear whether there is power-law scaling for dynamical model in studied range of scales.
+- Eliminate figure 4 with R2 add figure with fit for neutral model
+
 I believe that the current version of manuscript requires serious improvement and at this stage must be rejected and resubmitted.
@@
 Formula 5 must specify explicitly that Zq is an average over plots of area A.
+- Changed in the ms.
 
@@
 This aspect needs special consideration.
+- I added the method used to calculate ranks.
 
-3.
+#3.
 In the description of dynamic model (at least in Appendix) the following details must be specified: the boundary conditions, the type of lattice update (synchronous / asynchronous), the algorithm of assignment of competitive ranks in metacommunity.
 It is also necessary to raise the issue of the model dynamics stationarity, I propose to provide some figures of dynamics of several structural indicators (at least in the appendix).
-4.
+- More details were specified in the appendix.
+
+#4.
 D_0^SRS is not a fractal dimension of SRS (p.
@@
 D_0^SRS is a dimension of this support.
-5.
+- The D_0SRS is the fractal dimension of the species' spatial distribution, which in our model simulations is always 2 because the lattice is always filled. I changed it in the ms.
+
+#5.
 The degree of difference between Dq spectra is not a direct function of Delta rho.
@@
 8 is associated exclusively with the fact that the point Delta rho = 0.9 corresponds to the comparison of simulations rho = 1 vs rho = 0.9, which has very similar spectra.
-6.
+- Changed to a matrix of plots.
+
+#6.
 The power of methods based on spectra of indices is compared with power of methods based on single components of spectra.
@@
 But those methods use different statistical procedures so its direct comparison is not fully correct.
-7. Figures 1 and 5 lacks color scheme, making them difficult to read.
-8. Figure 3 has different scales for DqSAD и DqSRS, making it difficult to compare. As A = epsilon^2 I recommend to use A in both cases.
-9. RAD is a strictly nonincreasing sequence, but many curves at figure 6 lack this property.
+- I this case the idea is to show that single components should not be considered for community comparisons due to its high type I error and low power.
+
+#7. Figures 1 and 5 lacks color scheme, making them difficult to read.
+- I added the label and changed color palette
+
+#8. Figure 3 has different scales for DqSAD и DqSRS, making it difficult to compare. As A = epsilon^2 I recommend to use A in both cases.
+- I changed x axis to epsilon for both.
+
+#9. RAD is a strictly nonincreasing sequence, but many curves at figure 6 lack this property.
+- I corrected the calculation of ranks
 
@@
 
-- I use the k-sample Anderson Darling (1987) rank test and thus it makes no parametric assumption.
-It test the hypothesis that k independent samples comes from a common unespecified distribution.
-Thus I assume that the Dq spectrum comes from an univariate distribution, is not clear which could be the parameters from such distribution but as the test is non-parametric is reasonable to use this test for Dq spectra.
-As the samples are discrete and there is a posibility of ties I calculate the p-values using randomization.
+- As I use only two samples I don't have any information about the bivariate distribution of Dq or SAD, then I am assuming that each sample comes from an univariate unespecified distribution.
+Thus I use a permutations to calculate p-values with the k-sample Anderson Darling (1987) statistc.
 The advantage of the AD test is that I can use the same test for SAD and Dq.
@@
 - As I used the randomization test no assumptions about the nature of distributions are needed
-
- 4. The D0SRS is the fractal dimension of the species' spatial distribution, which in our model simulations is always 2 because the lattice is always filled.

### 2015-03-13 Neutral_simulPow.Rmd
add test of AD stat with Dq -  reviewer 1 comment #3 about AD test

@@
 den <- plotNeutral_SAD(0,256)
-
 setwd("..")

### 2015-03-13 R/Neutral_fun.r

@@ -92,7 +92,7 @@ calcRankSAD_by  <- function(den,vv,cols)
   hh <- function(x) { 
   x1 <- x[x[[vv]]>0,]
   x1$parms <- paste(unique(x[,cols]),collapse="_")
-  x1$Rank <- nrow(x1) - rank(x1[[vv]],ties.method="min") +1
+  x1$Rank <- nrow(x1) - rank(x1[[vv]],ties.method="first") +1
   return(x1)
   }
   ddply(den, cols,hh )
@@ -708,10 +708,12 @@ plotDqFitGQ <- function(zq0,qq,fac=3)
 
 # Calculates theoretic Dq from pmodel
 #
-calcDqTeor <- function(q,p1) {
+calcDqTeor <- function(q,p1,p2=0,p3=0,p4=0) {
   if( q==1)
     q <- q+1e-10
-  p2 <- p3 <- p4 <- (1-p1)/3
+  if(p2==0 & p3==0 & p4==0 ) {
+      p2 <- p3 <- p4 <- (1-p1)/3
+  }
   f1 <- p1/(p1+p2+p3+p4)
   f2 <- p2/(p1+p2+p3+p4)
   f3 <- p3/(p1+p2+p3+p4)
@@ -2241,14 +2243,11 @@ plotSAD_SpatPat<-function(nsp,side,type="U")
     spa <- rbind(spa,sp1)
   }
 
-  #g <- ggplot(spa, aes(x, y, fill = factor(v))) + geom_raster(hjust = 0, vjust = 0) + 
-  #  theme_bw() + coord_equal() 
-  # g <- g + scale_fill_grey(guide=F) +
   g <- ggplot(spa, aes(x, y, fill = v)) + geom_raster(hjust = 0, vjust = 0) + 
     theme_bw() + coord_equal() 
-  mc <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+  mc <- c("#b35806","#e08214","#fdb863","#fee0b6","#f7f7f7","#d8daeb","#b2abd2","#8073ac","#542788")
   
-  g <- g + scale_fill_gradientn(colours=mc[1:4],guide="colourbar",name="Species no.") + #guide=F
+  g <- g + scale_fill_gradientn(colours=mc,guide="colourbar",name="Species no.") + #guide=F
[…]

### 2015-03-19 ResponseToReviewers.md
correct all comments of reviewer 1 and editor

@@
 in addition to the comments by the reviewers I suggest to take care of the following:
-- In the beginning, I had some difficulties to follow which different metrics were actually tested against each other in the end and what different information they give us about the patterns and how we could interpret them in ecological terms.
+#- In the beginning, I had some difficulties to follow which different metrics were actually tested against each other in the end and what different information they give us about the patterns and how we could interpret them in ecological terms.
 There is some text abut this in the beginning of the result section but this is much too late (and to me also an odd place to put this info).
 I would suggest that this is made clearer early on and maybe it would be good to add a table that lists the indices together with their ecological meaning.
-- It should be stated early on in which situations and for which questions this method can be used and it should be highlighted somewhere what assumptions need to be tested to apply it
-- Finally, please make sure that color-blind (e.g. red-green) people can understand your figures.
+
+- I moved the paragraph about interpretation to the methods section, and added more explanations, but as I didn't know in advance how Dq will be, I present most interpretations as a discussion.
+I added a table with the methods used.
+
+# -It should be stated early on in which situations and for which questions this method can be used and it should be highlighted somewhere what assumptions need to be tested to apply it
+- The assumptions are stated in methods and I am testing here the power of the test to compare communities, but another possible applications are suggested for Dq to characterize rare species.
+
+#- Finally, please make sure that color-blind (e.g. red-green) people can understand your figures.
+
+- All figures have now a color-blind-safe palettes.
 
@@
 I highly appreciate the new method of analysis and consider it as having high potential. However, the current manuscript is not suitable for publication. The main drawbacks:
-1.
+
+#1.
 The author offers no meaningful interpretation of dimensions DqSRS, restricting discussion to statements that dimension for large negative q reflect the distribution of rare species, and dimensions for large positive q reflect the distribution of the dominant species.
 Such lack of interpretation leads to that the new metric is used rather as a "black box", which can or cannot distinguish the communities.
-2. Toy examples are chosen poorly. I cannot imagine a community consisting of linear clusters of species ordered by their overall abundance.
+- I added a some more interpretations, and about wath we know and what we don't know about Dq.
+This is why I added the simple toy models to understand more about how D_q is related to SAD and spatial patterns.
+
+#2. Toy examples are chosen poorly. I cannot imagine a community consisting of linear clusters of species ordered by their overall abundance.
+- these are examples of very simple species gradients and don't intend to be realistic, and mimic in a primitive way an enviromental gradient.
 
@@
 
-4.
+#4.
 The spectrum of generalized dimensions reflects the spatial scaling of some measure.
@@
 The author uses the coefficient of determination R^2 for the analysis of linearity.
-# R^2 is not a measure of linearity, it reflects only the scatter of points around the regression line. The proposed rule of thumb was not justified.
+R^2 is not a measure of linearity, it reflects only the scatter of points around the regression line.
+The proposed rule of thumb was not justified.
+- I added an explanation about R^2
 
-The author shows figure with Zq(A) scaling only for toy models but not for dynamical models, whereas it is well-studied for neutral models that their species-area relations is triphasic with power law in a narrow range of scales.
+#The author shows figure with Zq(A) scaling only for toy models but not for dynamical models, whereas it is well-studied for neutral models that their species-area relations is triphasic with power law in a narrow range of scales.
 It is not clear whether there is power-law scaling for dynamical model in studied range of scales.
-- Eliminate figure 4 with R2 add figure with fit for neutral model
+- Eliminate figure 4 with R2 add figure with fit for neutral model, and several figures in the appendix.
 
@@
 But those methods use different statistical procedures so its direct comparison is not fully correct.
-- I this case the idea is to show that single components should not be considered for community comparisons due to its high type I error and low power.
+- I added an explanation on why I calculate power for 1 dimension, the idea is to show that single components should not be considered for community comparisons due to its high type I error and low power.
+When you have different methods to do a test of hypothesis you allway prefer the one with more power, so it is commoon to compare power of different methods.
 
@@
 1)      In the Discussion the author should also highlight the limitations of their modelling process, in particular the fact that it not takes into account: a) asymmetry of the dispersal ability of species; b) the fact that trophic structure and species interactions in communities  may lead to more idiosyncratic processes of community assembly; c) the fact  that the truncated log-normal SAD was not tested.
-2)      The following paper could be cited in line 7 of page 1: Triantis, K.A., Guilhaumon, F.
+
+#2)      The following paper could be cited in line 7 of page 1: Triantis, K.A., Guilhaumon, F.
 & Whittaker, R.J.
@@
 
+- the references were corrected and the english
+
  My best regards to the author,
@@
 University of Azores
-
-# Response to reviewers
-
-DqSRS is the scaling of the ranks of species in space, as the ranks have the exact position of a species in space the result is different from DqSAD.
-
-Statistical procedure:
-
-- As I use only two samples I don't have any information about the bivariate distribution of Dq or SAD, then I am assuming that each sample comes from an univariate unespecified distribution.
-Thus I use a permutations to calculate p-values with the k-sample Anderson Darling (1987) statistc.
-The advantage of the AD test is that I can use the same test for SAD and Dq.
-
-The Dq spectrum is not an univariate distribution neither, as the test is non-parametric and the significance is calculated by randomization I argue that is reasonable to use the test to compare the curves produced by Dq, I made simulations to check this assumption and the Scholz1987
-- As I used the randomization test no assumptions about the nature of distributions are needed

### 2015-03-19 Neutral_simulPow.Rmd
correct all comments of reviewer 1 and editor

@@
 options("scipen"=100, "digits"=4)
+```
+# Test if at time 500 the model is at steady state
+
+Here I generate figures 1 and 2 for the appendix
+
+```{r test_neutralTime, eval=T,echo=F,message=F,warning=F}
+setwd("Simul")
+
+sml <- T
+simul <- data.frame()
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+parms <-expand.grid(nsp=c(8,64,256),side=c(256,512),disp=0.04,migr=0.001,repl=c(0,0.001,0.01,0.1,1))
+
+simul <- foreach(i=1:nrow(parms),.combine='rbind') %dopar%
+{
+simul_NeutralPlotTime(parms$nsp[i],parms$side[i],parms$disp[i],
+                                           parms$migr[i],parms$repl[i],sml,500,3,"N","L")
+}
+
+#cbPal <- c("#edf8fb","#b3cde3","#8c96c6","#8856a7","#810f7c")
+cbPal <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+require(ggplot2)
+
+g <- ggplot(simul,aes(x=Time,y=H,colour=as.factor(nsp),shape=as.factor(Rep))) + 
+    geom_line() + geom_point(size=1)+
+    facet_grid(ReplacementRate ~ side ) +
+    ylab(bquote("Shannon index"))+ 
+    scale_colour_manual(values=cbPal,name="Metacomm sp")+
+    scale_shape_discrete(guide=F)
+
+print(g+theme_bw())
+
+setwd(oldcd)
+
+ggsave("neuTime_side_sp_H.png", width=8,height=6,units="in",dpi=600)
+
+g <- ggplot(simul,aes(x=Time,y=Richness,colour=as.factor(nsp),shape=as.factor(Rep))) + 
+    geom_line() + geom_point(size=1)+
+    facet_grid(ReplacementRate ~ side ) +
+    ylab(bquote("Richness"))+ 
+    scale_colour_manual(values=cbPal,name="Metacomm sp")+
+    scale_shape_discrete(guide=F)
+print(g+theme_bw())
+ggsave("neuTime_side_sp_Rich.png", width=8,height=6,units="in",dpi=600)
+
+save.image()
+
 ```
@@
 
-```{r power_GCq10test, eval=T,echo=F,message=T,warning=T}
+```{r power_GCq10test, eval=F,echo=F,message=T,warning=T}
 setwd("Simul")
@@
 
-```{r neutral_SpSimPlot256, eval=F,echo=F,message=T,warning=T}
+```{r neutral_SpSimPlot256, eval=T,echo=F,message=T,warning=T}
+
 setwd("Simul")
 
-# meta = 64, side=250, time=500
-sad64 <- simul_NeutralSAD(64,256,500)
+ps <- data.frame(nsp=c(8,64,256),si=rep(c(256,512),each=3))
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+
+sad64 <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
+{
+  simul_NeutralSAD(ps$nsp[i],ps$si[i],500)
+}
+setwd(oldcd)
+
+```
+
+## Plots for publication
+
+```{r neutral_pubPlots, eval=F,echo=F,message=T,warning=T}
 
@@
 
+### Plot Neutral Dq Fit
+#
+setwd("Simul")
+zq <-readNeutral_Dq_fit(64,256,500,"L")
+plotDqFitG(zq)
+setwd(oldcd)
+ggsave("DqFit_NeuLog64_256.png", width=8,height=8,units="in",dpi=600)
+
+setwd("Simul")
+zq <-readNeutral_Dq_fit(8,256,500,"L")
+plotDqFitG(zq)
+setwd(oldcd)
+ggsave("DqFit_NeuLog8_256.png", width=8,height=8,units="in",dpi=600)
+
+setwd("Simul")
+zq <-readNeutral_Dq_fit(256,256,500,"L")
+plotDqFitG(zq)
+setwd(oldcd)
+ggsave("DqFit_NeuLog256_256.png", width=8,height=8,units="in",dpi=600)
+
+setwd("Simul")
+zq <-readNeutral_Dq_fit(8,512,500,"L")
+plotDqFitG(zq)
+setwd(oldcd)
+ggsave("DqFit_NeuLog8_512.png", width=8,height=8,units="in",dpi=600)
+
+setwd("Simul")
+zq <-readNeutral_Dq_fit(64,512,500,"L")
+plotDqFitG(zq)
+setwd(oldcd)
+ggsave("DqFit_NeuLog64_512.png", width=8,height=8,units="in",dpi=600)
+
+setwd("Simul")
+zq <-readNeutral_Dq_fit(256,512,500,"L")
+plotDqFitG(zq)
+setwd(oldcd)
+ggsave("DqFit_NeuLog256_512.png", width=8,height=8,units="in",dpi=600)
+
 # Create table with R2 of neutral models Dq

### 2015-03-19 SP_simul.Rmd
add test of AD stat with Dq -  reviewer 1 comment #3 about AD test
correct all comments of reviewer 1 and editor

@@
-# Multifractal analysis of multispecies spatial distributions - Spatial patterns simulations
+# Multifractal analysis of multispecies spatial distributions - Simple spatial patterns simulations
 
@@
 #plotDq(Dq3,"Type")
-require(pander)
-pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")
+#require(pander)
+#pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")
+
+simul <- 9
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
+
+ps <- expand.grid(nsp=c(8,64,256),side=c(256),simul=1:9)
+
+cc <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
+{
+  compMethods_UniformSAD(ps$nsp[i],256,F)
+}
+
+for(i in 1:nrow(ps)) {
+  DqF <- rbind(DqF, cc[[i]]$Dq)
+  }
+
 setwd(oldcd)
@@
 
-# Banded pattern 64 species 512 side
+# Banded pattern uniform SAD 8,64,256 species 512 side
 
@@
 
-# Now simulate an image with logseries SAD with 8, 64 & 256 species
-
-# Test logseries SAD side = 256
+# Now simulate 10 times simple spatial pattern with logseries SAD with 8, 64 & 256 species,side = 256
 
@@
 
-DqF <- rbind(DqF,compMethods_FisherSAD(8,256))
+require(doParallel)
+cn <-detectCores()
+cl <- makeCluster(cn)
+registerDoParallel(cl)
+require(foreach)
 
-DqF <- rbind(DqF,compMethods_FisherSAD(64,256))
+ps <- expand.grid(nsp=c(8,64,256),side=c(256),simul=1:10)
 
-DqF <- rbind(DqF,compMethods_FisherSAD(256,256))
+cc <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
+{
+  compMethods_FisherSAD(ps$nsp[i],256,F)
+}
+
+for(i in 1:nrow(ps)) {
+  DqF <- rbind(DqF, cc[[i]]$Dq)
+  }
 
 setwd(oldcd)
+save.image()
 
@@
 save.image()
-
-```
-
-# Simulate with logseries and the neutral model
-
-```{r simul_neu_256, eval=F,echo=F,message=F,warning=F}
-setwd("Simul")
-
-DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T)$Dq)
-
-DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T)$Dq)
-
-DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T)$Dq)
-setwd(oldcd)
-rm(nsp,side,spa)
-
-save.image()
-```
-
-# Test if at time 500 the model is at steady state
-
-Here I generate figures 1 and 2 for the appendix
-
-```{r test_neutralTime, eval=T,echo=F,message=F,warning=F}
-setwd("Simul")
-
-sml <- T
-simul <- data.frame()
-require(doParallel)
-cn <-detectCores()
-cl <- makeCluster(cn)
-registerDoParallel(cl)
-
-parms <-expand.grid(nsp=c(8,64,256),side=c(256,512),disp=0.04,migr=0.001,repl=c(0,0.001,0.01,0.1,1))
-
-simul <- foreach(i=1:nrow(parms),.combine='rbind') %dopar%
-{
-simul_NeutralPlotTime(parms$nsp[i],parms$side[i],parms$disp[i],
-                                           parms$migr[i],parms$repl[i],sml,500,3,"N","L")
-}
-
-#cbPal <- c("#edf8fb","#b3cde3","#8c96c6","#8856a7","#810f7c")
-cbPal <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-require(ggplot2)
-
-g <- ggplot(simul,aes(x=Time,y=H,colour=as.factor(nsp),shape=as.factor(Rep))) + 
-    geom_line() + geom_point(size=1)+
-    facet_grid(ReplacementRate ~ side ) +
-    ylab(bquote("Shannon index"))+ 
-    scale_colour_manual(values=cbPal,name="Metacomm sp")+
-    scale_shape_discrete(guide=F)
-
-print(g+theme_bw())
-
-setwd(oldcd)
-
-ggsave("neuTime_side_sp_H.png", width=8,height=6,units="in",dpi=600)
-
-g <- ggplot(simul,aes(x=Time,y=Richness,colour=as.factor(nsp),shape=as.factor(Rep))) + 
-    geom_line() + geom_point(size=1)+
-    facet_grid(ReplacementRate ~ side ) +
-    ylab(bquote("Richness"))+ 
-    scale_colour_manual(values=cbPal,name="Metacomm sp")+
-    scale_shape_discrete(guide=F)
-print(g+theme_bw())
-ggsave("neuTime_side_sp_Rich.png", width=8,height=6,units="in",dpi=600)
-
-save.image()
-
-```
-
-Perform Neutral with metaccomunity uniform and Uniform, 10 simulations with side 256 and 512
-
-```{r test_SAD256U, eval=F,echo=F,message=F,warning=F}
-setwd("Simul")
-
-cc <- comp_NeutralUniform(8,256)
-DqUN   <-cc$Dq
-SadUN  <-cc$SAD
-
-cc <- comp_NeutralUniform(64,256)
-DqUN   <-rbind(DqUN  ,cc$Dq)
-SadUN  <-rbind(SadUN ,cc$SAD)
-
-cc <- comp_NeutralUniform(256,256)
-DqUN   <-rbind(DqUN  ,cc$Dq)
-SadUN  <-rbind(SadUN ,cc$SAD)
-
-cc <- comp_NeutralUniform(8,512)
-DqUN   <-rbind(DqUN  ,cc$Dq)
-SadUN  <-rbind(SadUN ,cc$SAD)
-
-cc <- comp_NeutralUniform(64,512)
-DqUN   <-rbind(DqUN  ,cc$Dq)
-SadUN  <-rbind(SadUN ,cc$SAD)
-
-cc <- comp_NeutralUniform(256,512)
-DqUN   <-rbind(DqUN  ,cc$Dq)
-SadUN  <-rbind(SadUN ,cc$SAD)
-
-rm(cc)
-
-# merge SAD
-SadT <- rbind(SadGC,SadUN)
-rm(SadGC,SadUN)
-
-# merge Dq
-
-DqT <- rbind(DqGC,DqUN)
-rm(DqGC,DqUN)
-
-setwd(oldcd)
-save.image()
-
-#compT <- rbind(compT,compUN)
-#SadT <- rbind(SadT,SadUN)
-#DqT  <- rbind(DqT,DqUN)
-
-```
-
-Perform Neutral with metacommunity logseries and Logseries, 10 simulations with side =256/512
-
-```{r test_SAD256, eval=F,echo=F,message=F,warning=F}
-setwd("Simul")
-
-cc <- comp_NeutralLogseries(8,256)
-DqT   <-rbind(DqT,cc$Dq)
-SadT  <-rbind(SadT ,cc$SAD)
-
-cc <- comp_NeutralLogseries(64,256)
-DqT   <-rbind(DqT  ,cc$Dq)
-SadT  <-rbind(SadT ,cc$SAD)
-
-cc <- comp_NeutralLogseries(256,256)
-DqT   <-rbind(DqT  ,cc$Dq)
-SadT  <-rbind(SadT ,cc$SAD)
-
-cc <- comp_NeutralLogseries(8,512)
-DqT   <-rbind(DqT  ,cc$Dq)
-SadT  <-rbind(SadT ,cc$SAD)
-
-cc <- comp_NeutralLogseries(64,512)
-DqT   <-rbind(DqT  ,cc$Dq)
-SadT  <-rbind(SadT ,cc$SAD)
-
-cc <- comp_NeutralLogseries(256,512)
-DqT   <-rbind(DqT  ,cc$Dq)
-SadT  <-rbind(SadT ,cc$SAD)
-
-# Simulations with side=512 not done
-#
-#compSP <- rbind(compSP,compKS_NeutralLogseries(8,512))
-#compSP <- rbind(compSP,compKS_NeutralLogseries(64,512))
-#compSP <- rbind(compSP,compKS_NeutralLogseries(256,512))
-rm(cc)
-
-setwd(oldcd)
-save.image()
-```
-
-Now check if all simulations are done a make power calculations
-
-```{r power_adtest1, eval=F,echo=F,message=F,warning=F}
-# Check all simulations are present
-require(plyr)
-ddply(SadT,3:6,summarize, max(rep))
-ddply(DqT,5:8,summarize, max(rep),min(rep))
-powad <- data.frame()
-
-powad <- rbind(powad,calcPower_AD(DqT,SadT,8,256))
-powad <- rbind(powad,calcPower_AD(DqT,SadT,64,256))
-powad <- rbind(powad,calcPower_AD(DqT,SadT,256,256))
-
-powad <- rbind(powad,calcPower_AD(DqT,SadT,8,512))
-powad <- rbind(powad,calcPower_AD(DqT,SadT,64,512))
-powad <- rbind(powad,calcPower_AD(DqT,SadT,256,512))
-
-save.image()
-```
-
-Make plots of power and type I error
-
-```{r power_adtest, eval=F,echo=F,message=F,warning=F}
-
-plot_DqPowerTypeI <- function(pp,tit){
-  require(ggplot2)
-  pp$Type2[pp$Type2=="SRS"] <- "DqSRS" 
-  pp$Type2[grepl("rnz",pp$Type2)] <- "Power"
-  pp$Type2[grepl("Dq",pp$Type2)] <- "Type I"
-
-  g <-ggplot(pp, aes(factor(NumSp), power, colour = as.factor(Side))) +
-    geom_point(aes(shape=as.factor(Side)),size=4) + ggtitle(tit) + theme_bw() +
-    facet_grid(Type1~Type2) + scale_colour_discrete(name="Size") +
-    scale_shape_discrete(name="Size") + scale_x_discrete(name="Number of Species")
-  print(g)
-}
-#powad <- power
-p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Uniform" ,])
-plot_DqPowerTypeI(p1,"Uniform")
-
-p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="NeuUnif" ,])
-plot_DqPowerTypeI(p1,"NeuUnif")
-
-p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Logseries" ,])
-plot_DqPowerTypeI(p1,"Logseries")
-
-p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Neutral" ,])
-plot_DqPowerTypeI(p1,"Neutral")
 
@@
 zq <- readDq_fit(256,64,"Uniform")
-
-g <- plotDqFitG(zq)
+plotDqFitG(zq)
 
@@
 
-g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))
+## another version of the plot
+#g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))
 
@@
 zq <- readDq_fit(256,8,"Uniform")
-g <- plotDqFitG(zq)
+plotDqFitG(zq)
 
@@
 zq <- readDq_fit(256,256,"Uniform")
-g <- plotDqFitG(zq)
+plotDqFitG(zq)
 
@@
 #
-#g <- plotR2Dq_Side_Sp(DqT,256,64,"Logseries")
-#g
-#ggsave("R2Dq_Logser_64_256.png", width=8,height=6,units="in",dpi=600)
 
@@
 zq <- readDq_fit(256,64,"Logseries")
-g <-plotDqFitG(zq)
-g
+plotDqFitG(zq)
+
 setwd(oldcd)
@@
 zq <- readDq_fit(256,8,"Logseries")
-g <-plotDqFitG(zq)
-g
+plotDqFitG(zq)
+
 setwd(oldcd)
@@
 zq <- readDq_fit(256,256,"Logseries")
-g <-plotDqFitG(zq)
-g
+plotDqFitG(zq)
 setwd(oldcd)

### 2015-03-19 R/Neutral_fun.r

@@ -606,38 +606,6 @@ read_sed2xy <- function(fname)
 }
 
 
-# Function to plot Dq fit from t* files generated by mfSBA 
-# 
-# fname: file name of the t.inputFile
-# qname: file name of the q sed file used
-#
-plotDqFit <- function(fname,qname)
-{
-  zq <- read.table(fname, sep="\t",header=T)
-  cna <- read_sed(qname)
-  q <-t(cna)
-  zq0 <- reshape(zq, timevar="q",times=q,v.names=c("logTr"),
-                 varying=list(3:length(names(zq))),
-                 direction="long")
-  library(lattice)
-  zq1 <- subset(zq0, q==1 | q==2 | q==3 | q==4 | q==5 | q==0 | q==-1 | q==-2 | q==-3 | q==-4 | q==-5 )
-
-#  oname <- paste("lsaravia_figS_W",sem,"_",wnro,".tif",sep="")
-#  tiff(oname, width=4.86,height=4.86,units="in",res=600,compression=c("lzw"))
-  
-  trellis.par.set(superpose.symbol=list(pch=c(0,1,2,3,4,5,6,8,15,16,17)))
-  trellis.par.set(superpose.symbol=list(cex=c(rep(0.6,11))))
-  trellis.par.set(superpose.line=list(lty=3))
-  
-  #show.settings()
-  if(names(zq1)[2]=="LogBox") names(zq1)[2]<-"Log.Box"
-  print(xyplot(logTr~Log.Box , data =zq1, groups=q, type=c("r","p"), scales=list(tck=-1), 
-               #main=list(wtitle,cex=0.9),
-               auto.key=list(space = "right",title=expression(italic("q")),cex.title=.7, points=TRUE,cex=.7),
-               ylab=expression(italic(paste("log ",  Z[q](epsilon) ))) , xlab=expression(italic(paste("log ",epsilon)))  
-  ))
-#  dev.off()    
-}
 
 # Read information of the fit of Dq (Zq) from t.file and q file
 # Return a data.frame in long format
[…]

### 2015-03-19 R/test_ADwithDq.r

@@ -1,0 +1,193 @@
+# Multifractal analysis of multispecies spatial distributions - Anderson-Darling test
+
+#I use Dq from the simple spatial patterns with uniform and logseries SAD (DqT)
+
+
+load(".RData")
+
+simul  <- F # variable to perform or not the simulations
+
+oldcd <-getwd()
+source("R/Neutral_fun.r")
+
+# Set the location of the binary 
+#
+mfBin <- "~/Dropbox/cpp/SpatialAnalysis/mfsba" # /mfSBA /multiSpeciesSBA
+
+require(pander)
+panderOptions('table.split.table',Inf)
+panderOptions("table.style", "multiline") 
+options("scipen"=100, "digits"=4)
+knitr::opts_chunk$set(comment = NA)
+
+# Define the function
+
+
+# test the permutation with Anderson-Darling statistic for Dq
+# using the global variable DqT
+#
+test_ADPerm <-function(type="DqSRS",nsp=8,nsp1=64,maxq=24){
+
+  require(ggplot2)
+  require(kSamples)
+  require(plyr)
+  require(dplyr)
+
+  # select 1 set for comparison
+  # 
+  Dq1<- filter(DqT,Side==256,NumSp==nsp,SAD=="Logseries",Type==type,abs(q)<=maxq) %>%
+        group_by(SAD,Type,q) %>% summarize(SD.Dq=sd(Dq),Dq=mean(Dq),count=n(),Curve=paste(type,nsp))%>%
+        select(Curve,Dq,SD.Dq,q)
+        
+  # Change location add a constant
+
+  Dq2 <- mutate(Dq1,Dq=Dq+mean(Dq)*0.01,Curve=paste(type,nsp,"+ 0.1"))
+
+
+  g <- ggplot(rbind(Dq1,Dq2),aes(x=q,y=Dq,colour=Curve)) + theme_bw()+ geom_point() +  ggtitle("Add a constant")
+  print(g)  
+  g <- ggplot(rbind(Dq1,Dq2),aes(x=Dq,colour=Curve))+theme_bw()+stat_ecdf()
[…]

### 2015-03-20 ResponseToReviewers.md
Add pdf and updated Rmd files

@@
 Some comments for improvement:
-1)      In the Discussion the author should also highlight the limitations of their modelling process, in particular the fact that it not takes into account: a) asymmetry of the dispersal ability of species; b) the fact that trophic structure and species interactions in communities  may lead to more idiosyncratic processes of community assembly; c) the fact  that the truncated log-normal SAD was not tested.
+#1)      In the Discussion the author should also highlight the limitations of their modelling process, in particular the fact that it not takes into account: a) asymmetry of the dispersal ability of species; b) the fact that trophic structure and species interactions in communities  may lead to more idiosyncratic processes of community assembly; c) the fact  that the truncated log-normal SAD was not tested.
+
+- This paper is about a methodology to compare communities the models was choosen to generate a gradient with similar and different communities, but not to study the models or the limitation of the models, that would be another paper...
 
@@
 I think that the author should learn to use the tools in Latex (see http://jabref.sourceforge.net/; http://en.wikibooks.org/wiki/LaTeX/Bibliography_Management
-For instance the reference below is a book Chapter:
-Borda-de-Água, L., Hubbell, S.P. & He, F.et al. (2007). Scaling biodiversity under neutrality. Scaling 3 biodiversity, 347–375
-and should be more correctly:
-Borda-de-Água, L., Hubbell, S.
+#For instance the reference below is a book Chapter:
+#Borda-de-Água, L., Hubbell, S.P. & He, F.et al. (2007). Scaling biodiversity under neutrality. Scaling 3 biodiversity, 347–375
+#and should be more correctly:
+#Borda-de-Água, L., Hubbell, S.
 P., & He, F.
@@
 Scaling biodiversity under neutrality.
-In: Storch, D., Marquet, P.
+#In: Storch, D., Marquet, P.
 A., & Brown.
@@
 
-- the references were corrected and the english
+- the references were corrected and the ms was read by a native
 

### 2015-03-20 Neutral_simulPow.Rmd
Add pdf and updated Rmd files

@@
 
-# HAVE TO USE BINOMIAL !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!1
-
 ```
 
-# Use the information dimension t-test
+# Power of the information dimension t-test
 
@@
 ```
-Calculate Power using compareGrowthCurves and q=-24,24
+
+# (not used) Calculate Power using compareGrowthCurves and q=-24,24
 
@@
 
-More simulations to do comparisons with GC
+# More simulations to do comparisons with GC
 
@@
 
-Compare using the GC with q<=10
+## Power using growthcurves with q<=10
 
@@
 
-Lets try with ANderson-Darling test!
+## Power using Anderson-Darling test and q<=10
 
@@
 require(dplyr)
-#pow_ADq24 <- with(pow_AD,pow_AD[MrtR==0.2 & DspD==0.04 & ClnR==0.001,])
-
-# Select only the subset I will use
-#
-#pow_ADq24 <- filter(pow_AD,MrtR==0.2 & DspD==0.04 & ClnR==0.001) %>%
-#  mutate(spMeta = ceiling(as.numeric(NumSp)*1.33))
 
@@
 require(pander)
-pandoc.table(select(pow_ADq24,Side,spMeta,MeanSp, c(5:9)),style="grid",split.tables=Inf)
+pandoc.table(select(pow_ADq24,Side,spMeta,MeanSp, c(5:9)),style="multiline",split.tables=Inf)
 
@@
 
-# Calculate TypeI error in fuction of replacement rate
-#c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
-#c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
-#names(c3)[4]<-"typeI"
-#g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
-#g+theme_bw()
+```
 
-#rm(c1,c2,c3)
-
-```
 ## Plot power of D1
@@
 require(pander)
-pandoc.table(  select(pow_TD1,Side,spMeta,MeanSp,c(4:8)),style="grid",split.tables=Inf)
+pandoc.table(  select(pow_TD1,Side,spMeta,MeanSp,c(4:8)),style="multiline",split.tables=Inf)
 
@@
 
+## (Not used) Plot power of compareGrowthCurves method
+
 ```{r power_PlotGC, eval=F,echo=F,message=T,warning=T}
@@
 require(pander)
-pandoc.table(pow_GC1,style="grid",split.tables=Inf)
+pandoc.table(pow_GC1,style="multiline",split.tables=Inf)
 
@@
 
+## Plot power of Anderson-Darling test for q<=10
+
 ```{r power_PlotADq10, eval=F,echo=F,message=T,warning=T}
-
-#pow_GC1 <-merge(pow_GC1,unique(pow_ADq10[,1:3]),by.x=c(1,2),by.y=c(1,2),all.y=F)[,c(1:2,10,4:9)]
-#names(pow_GC1)[3]<- "MeanSp"
 
@@
 
-ggsave("powADq10_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)
+#ggsave("powADq10_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)
 
@@
 p1 <- plotPow_MeanSp_RplR(comp_ADq10)
-ggsave("powADq10_RplR_256.png", width=8,height=8,units="in",dpi=600)
+#ggsave("powADq10_RplR_256.png", width=8,height=8,units="in",dpi=600)
 
 p2 <- plotPow_MeanSp_RplR(comp_ADq10,512)
-ggsave("powADq10_RplR_512.png", width=6,height=6,units="in",dpi=600)
+#ggsave("powADq10_RplR_512.png", width=6,height=6,units="in",dpi=600)
 
@@
 pandoc.table( mutate(pow_ADq10 ,spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% select(Side,spMeta,MeanSp,c(5:9))
-,style="grid",split.tables=Inf,round=4)
+,style="multiline",split.tables=Inf,round=4)
 ```
 
-## Simulations to plot spatial patterns with different replacement Rate
+## Aditional simulations to plot spatial patterns with different replacement Rate $\rho$
 
@@
 
-setwd("..")
+setwd(oldcd)
 
@@
 require(pander)
-pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)
+pandoc.table(format(Dqq,digits=2),style="multiline",split.tables=Inf)
 
@@
 #write.table(format(Dqq,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
-pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)
+pandoc.table(format(Dqq,digits=2),style="multiline",split.tables=Inf)
 

### 2015-03-20 ResponseToReviewers.md
correct/add Dq interpretation in methods

@@
 # -It should be stated early on in which situations and for which questions this method can be used and it should be highlighted somewhere what assumptions need to be tested to apply it
-- The assumptions are stated in methods and I am testing here the power of the test to compare communities, but another possible applications are suggested for Dq to characterize rare species.
+- The assumptions are stated in methods and I am testing here the power of the test to compare communities, but other possible applications are suggested for Dq to characterize rare species.
 

### 2015-04-02 ResponseToReviewers.md
Resubmitted version to MEE

@@
 
-- I moved the paragraph about interpretation to the methods section, and added more explanations, but as I didn't know in advance how Dq will be, I present most interpretations as a discussion.
+* I moved the paragraph about interpretation to the methods section, and added more explanations, but as I didn't know in advance how Dq will be, I present most interpretations as a discussion.
 I added a table with the methods used.
@@
 # -It should be stated early on in which situations and for which questions this method can be used and it should be highlighted somewhere what assumptions need to be tested to apply it
-- The assumptions are stated in methods and I am testing here the power of the test to compare communities, but other possible applications are suggested for Dq to characterize rare species.
+* The assumptions are stated in methods and I am testing here the power of the test to compare communities, but other possible applications are suggested for Dq to characterize rare species.
 
@@
 
-- All figures have now a color-blind-safe palettes.
+* All figures have now a color-blind-safe palettes.
 
@@
 Such lack of interpretation leads to that the new metric is used rather as a "black box", which can or cannot distinguish the communities.
-- I added a some more interpretations, and about wath we know and what we don't know about Dq.
+* I added a some more interpretations, and about wath we know and what we don't know about Dq.
 This is why I added the simple toy models to understand more about how D_q is related to SAD and spatial patterns.
+pag 7:6_28
 
 #2. Toy examples are chosen poorly. I cannot imagine a community consisting of linear clusters of species ordered by their overall abundance.
-- these are examples of very simple species gradients and don't intend to be realistic, and mimic in a primitive way an enviromental gradient.
+* these are examples of very simple species gradients and don't intend to be realistic, and mimic in a basic way an enviromental gradient.
 
@@
 If the author intends to develop such a procedure, its description and justification must be given with a stronger consideration.
-- I added an explanation of why this test can be used with Dq
+* I added an explanation of why this test can be used with D_q pag 9:10-24
 
@@
 The proposed rule of thumb was not justified.
-- I added an explanation about R^2
+* I added an explanation about why I use R^2 and delete the rule of thumb. Pag 6:29- Pag 7:1-5
 
@@
 It is not clear whether there is power-law scaling for dynamical model in studied range of scales.
-- Eliminate figure 4 with R2 add figure with fit for neutral model, and several figures in the appendix.
+
+* I Eliminated figure 4 with R^2 and add figure 6 with fit for neutral model, and also figures 9-13 in the appendix.
 
@@
 Formula 5 must specify explicitly that Zq is an average over plots of area A.
-- Changed in the ms.
+
+* I changed that in the ms. pag 4:25-29 pag 6:1
 
@@
 This aspect needs special consideration.
-- I added the method used to calculate ranks.
+
+* I added the method used to calculate ranks. pag 6:23-24
 
@@
 It is also necessary to raise the issue of the model dynamics stationarity, I propose to provide some figures of dynamics of several structural indicators (at least in the appendix).
-- More details were specified in the appendix.
+
+* More details and figures 1-2 were added in the appendix.
 
@@
 D_0^SRS is a dimension of this support.
-- The D_0SRS is the fractal dimension of the species' spatial distribution, which in our model simulations is always 2 because the lattice is always filled. I changed it in the ms.
+
+* D_0^SRS is the fractal dimension of the species' spatial distribution, which in our model simulations is always 2 because the lattice is always filled. I changed it in the ms. pag 10:23-25
 
@@
 8 is associated exclusively with the fact that the point Delta rho = 0.9 corresponds to the comparison of simulations rho = 1 vs rho = 0.9, which has very similar spectra.
-- Changed to a matrix of plots.
+
+* I changed figure 8 to a matrix of plots.
 
@@
 But those methods use different statistical procedures so its direct comparison is not fully correct.
-- I added an explanation on why I calculate power for 1 dimension, the idea is to show that single components should not be considered for community comparisons due to its high type I error and low power.
-When you have different methods to do a test of hypothesis you allway prefer the one with more power, so it is commoon to compare power of different methods.
+
+* I added an explanation on why I calculate power for 1 dimension, the idea is to show that single components should not be considered for community comparisons due to its high type I error and low power.
+When you have different methods to perform a test of a hypothesis you allways prefer the one with more power, so it is commoon to compare power of different methods.
+pag 10:1-5
 
 #7. Figures 1 and 5 lacks color scheme, making them difficult to read.
-- I added the label and changed color palette
+* I added the labels and changed color palette
 
 #8. Figure 3 has different scales for DqSAD и DqSRS, making it difficult to compare. As A = epsilon^2 I recommend to use A in both cases.
-- I changed x axis to epsilon for both.
+* I changed x axis to epsilon for both.
 
 #9. RAD is a strictly nonincreasing sequence, but many curves at figure 6 lack this property.
-- I corrected the calculation of ranks
+* That was a mistake in calculating averages, I corrected the calculation of ranks.
 
@@
 Some comments for improvement:
+
 #1)      In the Discussion the author should also highlight the limitations of their modelling process, in particular the fact that it not takes into account: a) asymmetry of the dispersal ability of species; b) the fact that trophic structure and species interactions in communities  may lead to more idiosyncratic processes of community assembly; c) the fact  that the truncated log-normal SAD was not tested.
 
-- This paper is about a methodology to compare communities the models was choosen to generate a gradient with similar and different communities, but not to study the models or the limitation of the models, that would be another paper...
+* This manuscript is about a methodology to compare communities the model was chosen to generate a gradient from  similar and different communities, the comments of the reviewer are very interesting but for a paper about community assembly, that would be another paper...
 
@@
 Journal of Biogeography, 39: 215-23.
+
 #3)      In line 24 of page 1 it seems that one additional reference is missing afer Yakimove et al., 2008)
@@
 
-- the references were corrected and the ms was read by a native
+* the references were corrected and the ms was read by a native.
 

### 2015-05-06 ResponseToReviewers2.md
2nd review changes

# Reviewers comments resubmited manuscript

Associate Editor Comments to Author:

Associate Editor  
Comments to the Author:
I agree with the two reviewers that the manuscript has greatly improved. Please look at their responses for the few remaining issues concerning the content.
In addition, there are still many language issues and careless mistakes in the manuscript. This needs to be improved and I suggest to find (again) a native speaker for careful proofreading. I mention a few but did not check in detail.
p.4, l.2-3: check grammar
# 4, 26: change to 'first'
# 5, 13: 'graph'
# 6, 29: missing free space
# 7, 9: 'expresses'
# 7, 31: 'took'
# 11, 13: double 'with'
# 15, 21: did not 'make'
# 16, 1: What means: 'low species communities'? 
* communities with low richness

# 16, 2: What means: 'when species are around 100'?
* the number of species is around 100

# 16, 7: 'sizes'

Reviewer(s)' Comments to Author:

Reviewer: 1

Comments to the Corresponding Author

The author has improved the manuscript substantially from the previous version. All my concerns were addressed. The most crucial points are widened discussion of spectra interpretation and clarification of the use of Anderson-Darling criterion for spectra comparison. I believe that AD test is not an ideal solution (for example it cannot distinguish between spectra shifted along each other) but I’m now sure that there will be no inflated type 1 error.

# I think the work now is very close to be accepted but I found several places to be corrected. The most important are plots with scaling of log Zq vs log epsilon in the case of DqSAD (Fig. 3  and 6, left panels). Zq for q < 1 must increase wi th scale and Zq for q > 1 must decrease. Specifically Z0 is just a species richness and so the plot of its scaling is a usual SAR. But on the figures this pattern is reversed. I suspect there was some technical error. Otherwise description of algorithms must be reconsidered.

* For DqSAD equations 4 & 5, we have Zq(A) = Zq(e*e) is the sum of densities of species raised to q in a subplot with side e if q>0 when the area is bigger A'>A the sum Zq(A')>=Zq(A), for q<0 we have Zq(A')<=Zq(A) and this is what we can observe for DqSAD (and also DqSRS) in figures 3 and 6. 
For example if we take only the upper left square to calculate Zq(A):

1 1 2 1
2 1 2 3
2 1 2 3   
1 2 2 1

q=2 e=2  Zq(e*e)= 3*3 + 1
q=2 e=3  Zq(e*e)= 4*4 + 5*5
q=2 e=4  Zq(e*e)= 7*7 + 7*7 + 2*2

Thus Zq is increasing (the exact term is non-decreasing) when q>0

Other minor corrections:

# p. 3, l. 12: change “scaling of Renyi entropies” to “scaling exponents of Renyi entropies”
# p. 3, l. 25: Yakimov et al., 2014 and change reference accordingly
# p. 5, formula 3: I think it is better to specify that this is D1 explicitly (change Dq to D1)
# p. 5, l. 25: change “the abundance” to “the relative abundance”
# p. 6, l. 18: insert “relations” after “species-abundance-area”
# p. 11, l. 5: Fig. 3 shows not an example of fitted Dq but scaling of Zq fitted by linear regressions (and so the figure captions must be corrected)
* I corrected the captions of figures 3 and 6

# p. 14, l. 4: alfa = 0.05 obviously
# p. 14, l. 7: Table 3

Reviewer: 2

Comments to the Corresponding Author
I find the manuscript much improved, the writing more clear and the methods and results much easier to follow. I appreciate the effort the author has made to incorporate the referees criticisms. I make only some minor corrections.
.
Some comments for improvement:
# 1)      Page 12 – line 13 – “with with” should be replaced with “with”
# 2)      Page 6 – line 29 – “(Liebovitch 1998)and” should be replaced with “(Liebovitch 1998) and”
# 3)      the reference below is a book Chapter:
#Borda-de-Água, L., Hubbell, S.P. & He, F.et al. (2007). Scaling biodiversity under neutrality. Scaling 3 biodiversity, 347–375
#and should be more correctly:
#Borda-de-Água, L., Hubbell, S. P., & He, F. (2007). Scaling biodiversity under neutrality, Scaling biodiversity (eds. D. Storch, P.A. Marquet & J.H. Brown) pp. 347-375. Cambridge University Press, Cambridge.

#4)      Dal Bello, M., Maggi, E., Rindi, L., Capocchi, A., Fontanini, D., Sanz-Lazaro, C. & Benedetti-Cecchi, L. 27 (2014). Multifractal spatial distribution of epilithic microphytobenthos on a Mediterranean rocky shore. 28 Oikos, n/a—–n/a
#SHOULD BE:
#Dal Bello, M., Maggi, E., Rindi, L., Capocchi, A., Fontanini, D., Sanz-Lazaro, C. & Benedetti-Cecchi, L. 27 (2014). Multifractal spatial distribution of epilithic microphytobenthos on a Mediterranean rocky shore. Oikos, 124, 477–485.
#5)      In page 21 “Trends in ecology & evolution”, should be “Trends in Ecology & Evolution”
#6)      The reference
#Yakimov, B.N., Iudin, D.I., Solntsev, L.A. & Gelashvili, D.B. (2013). Multifractal analysis of neutral  community spatial structure. Journal of Theoretical Biology.

#Should be
#Yakimov, B.N., Iudin, D.I., Solntsev, L.A. & Gelashvili, D.B. (2013). Multifractal analysis of neutral  community spatial structure. Journal of Theoretical Biology, 343, 44–53.

My best regards to the author,

Paulo A. V. Borges

Azorean Biodiversity Group

cE3c - Centre for Ecology, Evolution and Environmental Changes
University of Azores

Associate Editor Comments to Author:

Associate Editor
Comments to the Author:
After reading the manuscript and the comments of the two reviewers I think that this approach has high potential but that the work needs some considerable improvements as well. in addition to the comments by the reviewers I suggest to take care of the following:
#- In the beginning, I had some difficulties to follow which different metrics were actually tested against each other in the end and what different information they give us about the patterns and how we could interpret them in ecological terms. There is some text abut this in the beginning of the result section but this is much too late (and to me also an odd place to put this info). I would suggest that this is made clearer early on and maybe it would be good to add a table that lists the indices together with their ecological meaning.

* I moved the paragraph about interpretation to the methods section, and added more explanations, but as I didn't know in advance how Dq will be, I present most interpretations as a discussion. I added a table with the methods used.

### 2015-05-06 R/Neutral_fun.r

@@ -810,7 +810,8 @@ genFisherSAD_image <- function(nsp,side)
 
 
 # Generate Logseries SAD with nsp*f species and side = side
-#  The factor f is to compensate losses for use as a metacommunity
+#  The factor f is to compensate losses for use as a metacommunity 
+#  previously set to f=1.33 now set to 1
 # Requires untb package
 #
 #

### 2015-05-10 ResponseToReviewers2.md
correct inverted slopes in Zq vs e

@@
 
-* For DqSAD equations 4 & 5, we have Zq(A) = Zq(e*e) is the sum of densities of species raised to q in a subplot with side e if q>0 when the area is bigger A'>A the sum Zq(A')>=Zq(A), for q<0 we have Zq(A')<=Zq(A) and this is what we can observe for DqSAD (and also DqSRS) in figures 3 and 6.
-For example if we take only the upper left square to calculate Zq(A):
-
-1 1 2 1
-2 1 2 3
-2 1 2 3   
-1 2 2 1
-
-q=2 e=2  Zq(e*e)= 3*3 + 1
-q=2 e=3  Zq(e*e)= 4*4 + 5*5
-q=2 e=4  Zq(e*e)= 7*7 + 7*7 + 2*2
-
-Thus Zq is increasing (the exact term is non-decreasing) when q>0
+* I corrected this. The error was produced because I calculated DqSAD=-Tau/(q-1) which is equivalent to DqSAD=Tau/(1-q), thus the slopes were inverted.
 
@@
 Azorean Biodiversity Group
-
-cE3c - Centre for Ecology, Evolution and Environmental Changes
-University of Azores
-
-Associate Editor Comments to Author:
-
-Associate Editor
-Comments to the Author:
-After reading the manuscript and the comments of the two reviewers I think that this approach has high potential but that the work needs some considerable improvements as well.
-in addition to the comments by the reviewers I suggest to take care of the following:
-#- In the beginning, I had some difficulties to follow which different metrics were actually tested against each other in the end and what different information they give us about the patterns and how we could interpret them in ecological terms.
-There is some text abut this in the beginning of the result section but this is much too late (and to me also an odd place to put this info).
-I would suggest that this is made clearer early on and maybe it would be good to add a table that lists the indices together with their ecological meaning.
-
-* I moved the paragraph about interpretation to the methods section, and added more explanations, but as I didn't know in advance how Dq will be, I present most interpretations as a discussion.
-I added a table with the methods used.

### 2015-05-10 Neutral_simulPow.Rmd
correct inverted slopes in Zq vs e

@@
 zq <-readNeutral_Dq_fit(64,256,500,"L")
-plotDqFitG(zq)
+plotDqFitG(zq,0)
 setwd(oldcd)
@@
 zq <-readNeutral_Dq_fit(8,256,500,"L")
-plotDqFitG(zq)
+plotDqFitG(zq,0)
 setwd(oldcd)
@@
 zq <-readNeutral_Dq_fit(256,256,500,"L")
-plotDqFitG(zq)
+plotDqFitG(zq,0)
 setwd(oldcd)
@@
 zq <-readNeutral_Dq_fit(8,512,500,"L")
-plotDqFitG(zq)
+plotDqFitG(zq,0)
 setwd(oldcd)
@@
 zq <-readNeutral_Dq_fit(64,512,500,"L")
-plotDqFitG(zq)
+plotDqFitG(zq,0)
 setwd(oldcd)
@@
 zq <-readNeutral_Dq_fit(256,512,500,"L")
-plotDqFitG(zq)
+plotDqFitG(zq,0)
 setwd(oldcd)

### 2015-05-10 R/Neutral_fun.r

@@ -625,13 +625,13 @@ readZq <- function(fname,qname)
 # zq0: data.frame with Zq, logTr 
 # fac: factor to separate the lines 
 # repRate: replacement to plot (rho)
-plotDqFitG <- function(zq0,fac=3,replRate=c(0,0.01,1))
+plotDqFitG <- function(zq0,fac=1/3,replRate=c(0,0.01,1))
 {
   require(ggplot2)
   require(dplyr)
   
   zq1 <- subset(zq0, q==1 | q==2 | q==3 | q==4 | q==5 | q==0 | q==-1 | q==-2 | q==-3 | q==-4 | q==-5 )
-  zq1$logTr <- zq1$logTr+zq1$q/fac
+  zq1$logTr <- zq1$logTr+zq1$q*fac
   if( "RplRt" %in% names(zq1))
   {
     zq1 <- filter(zq1,RplRt %in% replRate) %>% mutate(DqType=ifelse(grepl("SRS",Type),"DqSRS","DqSAD"), Type=paste("Rho:",RplRt),
@@ -2252,7 +2252,7 @@ plotR2Dq_Side_Sp <- function(Dqq,side,nsp,sad="Uniform")
 # Read sed files generated with simple spatial models and calculate Dq and return Fit of Dq 
 #
 readDq_fit <- function(side,nsp,sad="Uniform") {
-  
+  require(dplyr)
   if(sad=="Uniform") {                                  # SAD Uniform
     fname <- paste0("unif",nsp,"_",side,".sed")
     fname1 <- paste0("unif",nsp,"_",side,"rnz.sed") 
@@ -2272,11 +2272,13 @@ readDq_fit <- function(side,nsp,sad="Uniform") {
   Dq1<- calcDq_multiSBA(fname,"q.sed 2 1024 20 E",mfBin,T)
   zq1 <- readZq(paste0("t.", fname),"q.sed")
   zq1$Type <- "DqSAD"
+  zq1 <- mutate(zq1,logTr=-logTr)
   zq<- rbind(zq,zq1)
 
   Dq1<- calcDq_multiSBA(fname1,"q.sed 2 1024 20 E",mfBin,T)
   zq1 <- readZq(paste0("t.", fname1),"q.sed")
   zq1$Type <- "rnzDqSAD"
+  zq1 <- mutate(zq1,logTr=-logTr)
   zq<- rbind(zq,zq1)
   return(zq)
 }
[…]

### 2015-05-14 ResponseToReviewers2.md
Submited 2nd revision of the manuscript

@@
 I agree with the two reviewers that the manuscript has greatly improved. Please look at their responses for the few remaining issues concerning the content.
-In addition, there are still many language issues and careless mistakes in the manuscript.
+#In addition, there are still many language issues and careless mistakes in the manuscript.
 This needs to be improved and I suggest to find (again) a native speaker for careful proofreading.
 I mention a few but did not check in detail.
-p.4, l.2-3: check grammar
+# p.4, l.2-3: check grammar
 # 4, 26: change to 'first'
@@
 # 16, 1: What means: 'low species communities'? 
-* communities with low richness
+* I corrected as: communities with low richness
 
 # 16, 2: What means: 'when species are around 100'?
-* the number of species is around 100
+* I corrected as: the number of species is around 100
 
 # 16, 7: 'sizes'
+
+Following the review of a native speaker I reworded the paragraph at page 6 line 29.
+Additionally I deleted a paragraph in the disccussion (page 16 between lines 14-15) because it is a repetition of the same ideas and seems to be out of place.
 
@@
 
-* I corrected this. The error was produced because I calculated DqSAD=-Tau/(q-1) which is equivalent to DqSAD=Tau/(1-q), thus the slopes were inverted.
+* I corrected this.
+The error was produced because I use the following to calculate DqSAD: DqSAD=-Tau/(q-1) which is equivalent to DqSAD=Tau/(1-q) that is equation 5, as Tau=log(Zq)/log(e) the slopes were inverted.
+I updated figures 3, 6, and the appendix.
 
-Other minor corrections:
+# Other minor corrections:
 
